### 2022-06-22 latex/paper.tex
update

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%% preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[
%a4paper,       % letterpaper, a4paper, a5paper
%10pt,              % 10pt, 11pt, 12pt
reprint,           % journal's actual layout
%preprint,          % 12pt, single-column
superscriptaddress,% authors with affiliations via superscripts
amsmath,           % add AMS-Latex features
amssymb,           % add extra AMS symbols, including amsfonts
aps,               % aps or aip
prd,               % prl, pra, prb, prc, prd, pre, prstab
%showpacs,          % make PACS codes appear
notitlepage,       % control appearance of title page
longbibliography,  % show  article titles in the bibliography
floatfix,          % process floats as early as possible
showkeys,          % option to make keywords appear
%titlepage,         %
%eqsecnum,          % number equations by section
]{revtex4-1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% load packages %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{tensor}     % manipulate tensors
\usepackage{graphicx}   % include figures
\usepackage[
colorlinks=true,        % color link
citecolor=blue,         % cite color
linkcolor=blue,         % link color
urlcolor=blue           % url color
]{hyperref}             % create hyperlinks
\usepackage{bm}         % \bm{<text>} Bold math symbols
\usepackage{xcolor}     % textcolor
%\usepackage{dcolumn}    % Align table columns on decimal point
%\usepackage{array}      % dcolumn depends on array
\usepackage{tabulary}
\usepackage{color}      % \textcolor{declared-color}{text}
%\usepackage{longtable}  % large table\
%\usepackage{fontspec} % accented characters for .bib file using XeLaTex
\usepackage[section]{placeins} % figures processing
%\renewcommand{\arraystretch}{1.25}
%\arraycolsep 10pt

% User-defined commands
\renewcommand{\vec}[1]{\boldsymbol{#1}} % Uncomment for BOLD vectors.
\def\Bs{{\overline{B}}_s}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% new commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\nc}{\newcommand*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% alphabet %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\nc{\al}{\alpha}
\nc{\s}{\sigma}
\nc{\dt}{\delta}
\nc{\Dt}{\Delta}
\nc{\Ld}{\Lambda}
\nc{\p}{\partial}
\nc{\om}{\omega}
\nc{\Om}{\Omega}
\nc{\rd}{\mathrm{d}}
\nc{\Od}[1]{\mathcal{O}(#1)} % order operator
\nc{\kp}{\kappa}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% equations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\({\left(}
\def\){\right)}
\def\[{\left[}
\def\]{\right]}
\def\e{\begin{equation}}
\def\q{\end{equation}}
\def\m{\begin{eqnarray}}
\def\n{\end{eqnarray}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% citations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\nc{\Eq}[1]{Eq.~\eqref{#1}}     % equation
\nc{\Fig}[1]{Fig.~\ref{#1}}     % figure
\nc{\Table}[1]{Table~\ref{#1}}  % table
\nc{\Sec}[1]{Sec.~\ref{#1}}     % section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% gravitational waves %%%%%%%%%%%%%%%%%%%%%%%%%%%
\nc{\Msun}{M_\odot}             % solar mass
\nc{\fpbh}{f_{\mathrm{pbh}}}    % f_pbh
\nc{\fpbhn}{f_{\mathrm{pbh0}}}    % f_pbh
\nc{\mR}{\mathcal{R}} % merger rate density
\nc{\seq}{\sigma_{\mathrm{eq}}}
\nc{\ogw}{\Omega_{\mathrm{GW}}}
\nc{\gpcyr}{\mathrm{Gpc}^{-3}\,\mathrm{yr}^{-1}}
\nc{\lvc}{LIGO/Virgo} % LIGO-VIRGO collaboration
\nc{\SNR}{\mathrm{SNR}} % signal to noise ratio
\nc{\mmin}{{m_{\mathrm{min}}}}
\nc{\mmax}{{m_{\mathrm{max}}}}
\nc{\Mmin}{{M_{\mathrm{min}}}}
\nc{\fmin}{{f_{\mathrm{min}}}}
\nc{\VT}{\mathrm{VT}}
\nc{\rhoGW}{\rho_{\mathrm{GW}}}
\nc{\vth}{\vec{\theta}}
\nc{\vd}{\vec{d}}
\nc{\vla}{\vec{\lambda}}
\nc{\Nobs}{N_{\mathrm{obs}}}
\nc{\av}[1]{\langle #1 \rangle} % average bracket
\nc{\km}{\mathrm{km}}
\nc{\Mpc}{\mathrm{Mpc}}
\nc{\Tobs}{T_{\mathrm{obs}}}
\nc{\Ntemp}{N_{\mathrm{temp}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% other %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\nc{\addref}{[\textcolor{red}{add ref}] } % placeholder of references
\nc{\eg}{\textit{e.g.~}}
\nc{\app}{\approx}
\nc{\hf}{\frac{1}{2}}
\nc{\discuss}{\textcolor{red}{Add discussion here!}}
\nc{\red}[1]{\textcolor{red}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%% only used in this paper %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\nc{\mH}{\mathcal{H}}
\nc{\cs}{c_s^2}
\nc{\Sij}[1]{S_{ij}^{(#1)}}
\nc{\vi}[1]{v_i^{(#1)}}
\nc{\no}{\nonumber}
\def\<{\left\langle}
\def\>{\right\rangle}
\def\ap{\alpha}
\def\half{{1\over 2}}
\nc{\bk}{\bm{k}}
\nc{\bq}{\bm{q}}
\nc{\bp}{\bm{p}}
\nc{\bl}{\bm{l}}
\nc{\bx}{\bm{x}}
\nc{\be}{\mathbf{e}}
\nc{\mS}{\mathcal{S}}
\nc{\te}{\tilde{\eta}}
\nc{\tp}{\tilde{p}}
\nc{\tk}{\tilde{k}}
\nc{\tx}{\tilde{x}}
\nc{\tF}{\tilde{F}}
\nc{\tA}{\tilde{A}}
\nc{\mkpq}{|\bk-\bp-\bq|}
\nc{\mpq}{|\bp-\bq|}
\nc{\mkp}{|\bk-\bp|}
\nc{\mSi}[1]{\mS^{(#1)}({\bk, \eta})}
\nc{\vk}{\vec{k}}
\nc{\kstar}{k_*}
\nc{\xstar}{x_*}
\nc{\mpbh}{m_{\rm{pbh}}}
\nc{\cR}{\mathcal{R}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% main text %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
\title{The merger history of primordial-black-hole binaries implied by GWTC-3}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\author{Zu-Cheng~Chen}
%\email{zucheng.chen@bnu.edu.cn}
%\affiliation{Department of Astronomy, Beijing Normal University, Beijing 100875, China}
%\affiliation{Advanced Institute of Natural Sciences, Beijing Normal University, Zhuhai 519087, China}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\author{You~Wu}
%\email{Corresponding author: youwuphy@gmail.com}
%\affiliation{College of Mathematics and Physics, Hunan University of Arts and Science, Changde, 415000, China}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\date{\today}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Primordial black holes (PBHs), as dark matter candidates, have attracted 
more and more attentions as they could be possible progenitors of 
the heavy binary black holes (BBHs) observed by \lvc.
Accurately estimating the merger rate of PBH binaries will be crucial to
reconstruct the mass distribution of PBHs.
%However there exists some uncertainties in estimating the merger rate.
It was pointed out the merger history of PBHs may shift the merger rate distribution depending on the mass function of PBHs.
In this paper, we use BBH events from \lvc\ GWTC-3 data release to
constrain the merger rate distribution of PBHs by taking into account the effect of merger history.
It is found that the second merger process makes subdominant contribution to the 
total merger rate, and hence the merger history effect can be safely neglected.	
We also confirm that the main components of dark matter should not be made of stellar 
mass PBHs.

%\keywords{primordial black holes, merger rate, merger history}
\end{abstract}

\pacs{???}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
The direct detection of gravitational wave (GW) from a binary black hole (BBH)
coalescence \cite{Abbott:2016blz} has opened a new window into the universe.
Over the past few years, ten BBH mergers have been reported by \lvc\ during 
the O1 and O2 observing runs \cite{Abbott:2016blz,Abbott:2016nmj,%
TheLIGOScientific:2016pea,Abbott:2017vtc,%
Abbott:2017gyy,Abbott:2017oio,LIGOScientific:2018mvr}.
The progenitors of these BBHs are still unknown and under intensively investigation (see \eg \cite{Bird:2016dcv,Sasaki:2016jop,Chen:2018czv,%
Fishbach:2017dwv,Clesse:2016vqa,Antonini:2016gqe,%
Inayoshi:2017mrs,Ali-Haimoud:2017rtz,Perna:2019axr,Kavanagh:2018ggo,%
Rodriguez:2015oxa,Rodriguez:2016kxx,Park:2017zgj,%
Belczynski:2014iua,Belczynski:2016obo,Woosley:2016nnw,%
Rodriguez:2018rmd,Choksi:2018jnq,2010AIPC.1314..291D,deMink:2016vkw}).
These \lvc\ BBHs present a much heavier mass distribution (in particular the 
source-frame primary mass of GW170729 event can be as heavy as
$50.2^{+16.2}_{-10.2} \Msun$ \cite{LIGOScientific:2018mvr}) than that 
inferred from X-ray observations
\cite{Wiktorowicz:2013dua,Casares:2013tpa,Corral-Santana:2013uua,%
Corral-Santana:2015fud},
which would challenge the formation and evolution mechanisms of astrophysical
black holes. 
One possible explanation for \lvc\ BBHs is the primordial black holes (PBHs)
\cite{Bird:2016dcv,Sasaki:2016jop,Chen:2018czv}
formed through the gravitational collapse of the primordial density
fluctuations \cite{Hawking:1971ei,Carr:1974nx}, 
which may accompany the induced GWs
\cite{Yuan:2019udt,Yuan:2019wwo,Chen:2019xse,Yuan:2019fwv,Cai:2019bmk,Cai:2018dig,Cai:2019elf,DeLuca:2019ufz,Bartolo:2018rku,Bartolo:2018evs}.
On the other hand, PBHs can also be a candidate of cold dark matter (CDM),
and the abundance of PBHs in CDM has been constrained by various experiments
\cite{Carr:2009jm,Barnacka:2012bm,Graham:2015apa,Niikura:2017zjd,%
Griest:2013esa,Niikura:2019kqi,Tisserand:2006zx,Brandt:2016aco,Gaggero:2016dpq,%
Ali-Haimoud:2016mbv,Blum:2016cjs,Horowitz:2016lib,Chen:2016pud,%
Wang:2016ana,Abbott:2018oah,Magee:2018opb,Wang:2019kaf,Chen:2018rzo,Chen:2019irf,%
Yuan:2019udt,Chen:2019xse,Montero-Camacho:2019jte,Laha:2019ssq,Dasgupta:2019cae,Gow:2019pok}.

In order to account for the \lvc\ BBHs, the merger rate of PBH binaries has
been estimated to be $17 \sim 288~\gpcyr$ \cite{Chen:2018rzo}.
One should notice that theoretically there exist some uncertainties in
estimating the merger rate distribution of PBH binaries, and the accuracy of 
the estimation has been continuously improved.
The merger rate of PBH binaries with monochromatic mass function has already
been given in \cite{Nakamura:1997sm,Sasaki:2016jop} for the case where two 
neighboring PBHs having sufficiently small separation can form a binary in
the early Universe due to the torque from the third nearest PBH.
These binaries would then evolve and coalesce within the age of the Universe 
and finally explain the merger events observed by \lvc\
\cite{Sasaki:2016jop}.
Later, the merger rate estimation is improved in \cite{Ali-Haimoud:2017rtz} 
by taking into account the torques exerted by all CDM (including all the PBHs
and linear density perturbations), but it is also assumed that all PBHs have
the same mass.
It is also pointed out in \cite{Ali-Haimoud:2017rtz} that the effects such as
encountering with other PBHs, tidal field from the smooth halo, and
the baryon accretion are subdominant and can be neglected when estimating
the merger rate.

Various attempts have been made to estimate the merger rate distribution
of PBH binaries when PBHs have an extended mass function 
\cite{Chen:2018czv,Chen:2018rzo,Raidal:2018bbj,Raidal:2017mfl,Liu:2018ess,Liu:2020cds,Vaskonen:2019jpv}.
In particular, a formalism to estimate the effect of merger history of PBHs
on merger rate distribution has been developed in \cite{Liu:2019rnx},
and it is argued that the multiple-merger effect may not be ignored if
PBHs have a power-law or a log-normal mass function by choosing some specific
parameter values of the mass function.
An accurate estimation of the merger rate will be crucial to infer the event
rate of \lvc\ BBHs and constrain the abundance of PBHs in CDM either through
null detection of sub-solar mass PBH binaries or the null detection
of stochastic GW background (SGWB) from PBH binaries.

In this paper, we will use the publicly available GW data from \lvc\ O1 and O2 
observations to estimate the merger rate distribution of PBH binaries with a
general mass function assuming all of \lvc\ BBHs are of primordial origin.
We find that the merger history effect makes no significant contribution to
the merger rate of PBHs and can be safely ignored.
The rest of this paper is organized as follows.
In \Sec{merger}, we review the calculation of merger rate distribution 
accounting for the merger history effect.
In \Sec{method}, we elaborate the data analysis method used to infer the
PBH populations from \lvc\ data.
In \Sec{result}, we present the results for PBHs with a power-law and 
a log-normal mass function respectively.
Finally, we summarize and discuss our results in \Sec{conclusion}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{merger}Merger rate distribution of PBHs}
In this section, we will briefly review the calculation of merger rate density
by closely following \cite{Liu:2019rnx}.
We denote the probability distribution function (PDF) of PBH masses by $P(m)$
which satisfies the following normalization condition
\e\label{norm}
    \int_{0}^{\infty} P(m)\, \rd m = 1.
\q 
Consequently the abundance of PBHs in the mass interval $(m, m+\rd m)$ is given 
by \cite{Chen:2018rzo}
\e 
    0.85 \fpbh\, P(m)\, \rd m,
\q 
where $\fpbh$ is the fraction of PBHs in CDM, and the coefficient $0.85$ is roughly the fraction of CDM in non-relativistic matter.
Similar to \cite{Liu:2019rnx}, one may define a quantity $\mpbh$ as
\e\label{mpbh}
    \frac{1}{\mpbh} = \int \frac{P(m)}{m} \rd m.
\q 
Furthermore, the present average number density of PBHs with mass $m$ in the 
present total average number density of PBHs, $F(m)$, can be obtained by
\cite{Liu:2019rnx}
\e\label{Fm} 
    F(m) = P(m) \frac{\mpbh}{m}.
\q

With the above definitions at hand, one can go directly to estimate the merger rate densities of PBH binaries contributed from different merger processes. We assume that PBHs are randomly distributed in the early Universe when they decouple from the cosmic background evolution \cite{Nakamura:1997sm,Sasaki:2016jop,Ali-Haimoud:2017rtz}. Due to gravitational interactions, two nearest PBHs would attract each other and form a bound system if they get the angular momentum from the torque of the third closest PBH. Because of gravitational radiations, PBH binaries would eventually merge and may be detected by \lvc. Let us consider the first-merger process now. Assuming PBHs posses a random distribution in the early Universe, the differential distribution, for three PBHs with masses $(m_i, m_i+dm_i)$, $(m_j, m_j+dm_j)$ and  $(m_l, m_l+dm_l)$, is given by \cite{Liu:2019rnx}
\e\label{dP1}
\begin{split} 
    dP_1 =& 16\pi^2 n_T^2 x^2 y^2 F(m_i) F(m_j) F(m_l) \\
            &\times e^{-4\pi y^3 n_T/3} \rd m_i \rd m_j \rd m_l \rd x \rd y \Theta(y-x),
\end{split}
\q 
where $\Theta$ is the Heaviside step function, and $x$ is the comoving distance between two closest PBHs with masses $m_i$ and $m_j$. Note that these two nearest PBHs will form a binary due to the torque of third PBH with mass $m_l$. In \Eq{dP1}, $y$ is the comoving distance from the binary to the third PBH, and $n_T$ is the average number density of PBHs defined by
\e 
    n_T = \frac{\fpbh \rho_{\mathrm{CDM}}}{\mpbh},
\q  
where $\rho_{\mathrm{CDM}}$ is the energy density of CDM.
Notice that the $e$-factor in \Eq{dP1} guarantees that there are no other PBHs within the distance $y$. It is now straightforward to obtain the fraction of PBHs that have merged before cosmic time $t$ \cite{Liu:2019rnx}
\e 
    G_1(t) = \int \rd x \rd y \rd m_l \frac{\rd P_1}{\rd x \rd y \rd m_i \rd m_j \rd m_l} \Theta(t-\tau),
\q 
where $\tau$ is the cosmic time at which the PBH binary with masses of $m_i$ and $m_j$ merges. Therefore the merger rate density of first-merger process, $\cR_1(t, m_i, m_j)$, is given by \cite{Liu:2019rnx}
\e 
\cR_1(t, m_i, m_j) = \hf n_T \frac{\rd G_1(t, m_i, m_j)}{\rd t}
            = \int \hat{\cR}_1 \rd m_l,
\q 
where the factor $1/2$ accounts for the symmetry of $m_i$ and $m_j$, and
\e 
\begin{split}
    &\hat{\cR}_1(t, m_i, m_j, m_l)
    =1.32 \times 10^6 \times \(\frac{t}{t_0}\)^{-\frac{34}{37}}\(\frac{\fpbh}{\mpbh}\)^\frac{53}{37} \\ 
    &\times m_l^{-\frac{21}{37}} (m_i m_j)^\frac{3}{37} (m_i + m_j)^\frac{36}{37} F(m_i) F(m_j) F(m_l).     
\end{split}
\q
After the first-merger process, the mass of the remnant BH will approximately be $m_i + m_j$ if the two initial PBHs have masses of $m_i$ and $m_j$.
A second-merger process would happen if this remnant BH and the nearest PBH with mass $m_k$ form a new binary by the torque from another PBH with mass $m_l$. Similarly, the merger rate density of second-merger process, $\cR_2(t, m_i, m_j)$, is given by \cite{Liu:2019rnx}
\e 
\begin{split}
    \cR_2(t, m_i, m_j) &= \hf \int \hat{\cR}_2(t, m_i-m_e, m_e, m_j, m_l)\ \rd m_l \rd m_e\\
    &+ \hf \int \hat{\cR}_2(t, m_j-m_e, m_e, m_i, m_l)\ \rd m_l \rd m_e,
\end{split}
\q 
where
\e 
\begin{split}
    &\hat{\cR}_2(t, m_i, m_j,m_k, m_l)
    =1.59 \times 10^4 \times \(\frac{t}{t_0}\)^{-\frac{31}{37}} \(\frac{\fpbh}{\mpbh}\)^\frac{69}{37}\\ 
    &\qquad\times m_k^{\frac{6}{37}} m_l^{-\frac{42}{37}} (m_i+ m_j)^\frac{6}{37} (m_i + m_j + m_k)^\frac{72}{37}\\
    &\qquad\times F(m_i) F(m_j) F(m_k) F(m_l).     
\end{split}
\q
Following the same spirit, in principle one can derive the merger rate density $\cR_n(t, m_i, m_j)$ contributed from the $n$-th merger process.
Therefore the total merger rate density, $\cR(t, m_i, m_j)$, 
of PBHs at cosmic time $t$ with masses $m_i$ and $m_j$ is
\e\label{cR}
    \cR(t, m_i, m_j) = \sum_{n=1} \cR_n(t, m_i, m_j),
\q 
and the total merger rate can be directly obtained by
\e\label{Rt}
    R(t) = \int \cR(t, m_i, m_j) \rd m_i \rd m_j = \sum_{n=1} R_n(t),
\q 
where
\e 
 R_n(t) = \int \cR_n(t, m_i, m_j) \rd m_i \rd m_j.
\q 
As demonstrated in \cite{Liu:2019rnx}, $\cR_{n+1}(t, m_i, m_j)$ is not 
necessarily be smaller than $\cR_n(t, m_i, m_j)$ (see Fig.~7 and Fig.~8 in 
\cite{Liu:2019rnx}).
However, $R_{n+1}(t)$ should be smaller than $R_n(t)$ as expected
\cite{Liu:2019rnx}.
Here, we only consider the merger history up to second-merger process.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{method}Inference on PBH mass distribution from GW data}
Given a general mass function of PBHs $P(m|\vth)$ which satisfy the normalization
condition of \Eq{norm}, the time (or redshift) dependent merger rate can be
obtained by \Eq{Rt}, namely
\e\label{Rt2}
R(t|\vth) = \int \mR(t, \vla|\vth)\ \rd \vla,
\q 
where $\vla \equiv \{m_1, m_2\}$, and $\vth$ are the parameters that 
characterize the mass function and will be inferred from GW data. 
For instance, $\vth=\{\alpha, M\}$ for the power-law PDF (see \Eq{power}) 
and $\vth=\{m_c, \s\}$ for the log-normal PDF (see \Eq{log}).
The local merger rate density distribution then reads \cite{Chen:2018rzo}
\e\label{Rt0} 
\mR(t_0, \vla|\vth) = R_0\, p(\vla|\vth),
\q 
where $R_0 \equiv R(t_0|\vth)$ is the local merger rate, and $p(m_1,m_2|\vth)$ 
is the population distribution of BBH mergers.
Note that \Eq{Rt0} guarantees $p(m_1,m_2|\vth)$ is normalized, namely
\e 
    \int p(\vla|\vth)\, \rd \vla = 1.
\q

Given the GW data, $\vd = (d_1, \dots, d_N)$, which consist of $N$ BBH merger
events, we aim to extract the population parameters $\{\vth, R_0\}$ from $\vd$.
In order to do that, it is necessary to perform the hierarchical Bayesian inference
on the BBHs' mass distribution 
\cite{Abbott:2016nhf,Abbott:2016drs,TheLIGOScientific:2016pea,
    Wysocki:2018mpo,Fishbach:2018edt,Mandel:2018mve,Thrane:2018qnx}.
In this work, we will use the data of ten BBHs
\cite{TheLIGOScientific:2016pea,LIGOScientific:2018mvr} 
reported by \lvc\ O1 and O2 observations, and hence $N=10$. 
The posterior samples of these BBHs are publicly available from \footnote{\url{https://www.gw-openscience.org/}}. 
Because the standard priors on masses for each event in \lvc\ analysis are 
taken to be uniform \cite{TheLIGOScientific:2016pea,LIGOScientific:2018mvr},
the likelihood of an individual event $p(d_i|\vla)$ is
proportional to the posterior of that event $p(\vla|d_i)$.
The total likelihood for an inhomogeneous Poisson process can be evaluated as
\cite{Wysocki:2018mpo,Fishbach:2018edt,Mandel:2018mve,Thrane:2018qnx}
\e\label{likelihood}
p(\vd|\vth, R_0) \propto R_0^{N} e^{-R_0\, \beta(\vth)} \prod_i^N 
\int \rd\vla\ p(d_i|\vla)\ p(\vla|\vth),
\q 
where $\beta(\vth)$ is defined as
\e 
\beta(\vth) \equiv \int \rd\vla\ VT(\vla)\ p(\vla|\vth),
\q 
in which $VT(\vla)$ is the sensitive spacetime volume \cite{Abbott:2016nhf,Abbott:2016drs} of LIGO.
We adopt the semi-analytical approximation from 
\cite{Abbott:2016nhf,Abbott:2016drs} to estimate $VT$, 
where we use the ``IMRPhenomPv2" waveform to simulate the BBH templates
and neglect the effect of spins for BHs.
Furthermore, the threshold signal-to-noise ratio (SNR) of detection for a 
single-detector is set to $8$,
which corresponds to a network SNR threshold of around $12$.

Assuming the prior distributions $p(\vth, R_0)$ are uniform for $\vth$ parameters
and log-uniform for local merger rate $R_0$
\cite{Abbott:2016nhf,Abbott:2017vtc}, namely
\e 
p(\vth, R_0) \propto \frac{1}{R_0},
\q 
the posterior probability distribution $p(\vth, R_0|\vd)$ 
can be directly calculated by
\e\label{post} 
p(\vth, R_0|\vd) \propto p(\vd |\vth, R_0)\ p(\vth, R_0).
\q
The marginalized posterior $p(\vth|\vd)$ can then be readily obtained by
integrating over $R_0$ in \Eq{post}, namely
\e\label{post_vth} 
p(\vth|\vd) \propto \[\beta(\vth)\]^{-N} 
\prod_i^N \int \rd\vla\ p(d_i|\vla)\ p(\vla|\vth).
\q 
This marginalized posterior has been widely used in previous 
population inferences 
\cite{Abbott:2016nhf,Abbott:2017vtc,TheLIGOScientific:2016pea,
    Abbott:2016drs,Fishbach:2017zga,Chen:2018rzo}.
In the following section, we will utilize the posterior \eqref{post} to infer
the population parameters $\{\vth, R_0\}$ by considering two concrete mass
distributions, a power-law PDF and a log-normal PDF, respectively.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{result}results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Log-normal mass function}
We now consider a log-normal mass function of PBHs as \cite{Dolgov:1992pu}
\e\label{log}
P(m) = \frac{1}{\sqrt{2\pi} \s m} \exp \(-\frac{\ln^2\(m/m_c\)}{2\s^2}\),
\q
where $m_c$ presents the peak mass of $m P(m)$, and $\s$ denotes the width of 
the mass spectrum.
The log-normal mass function is a good approximation to a large class of extended mass distributions if PBHs are formed from smooth symmetric peaks in the inflationary power spectrum \cite{Carr:2017jsz}, as demonstrated in \cite{Green:2016xgy,Kannike:2017bxn}.
Note that $\vth=\{m_c, \s\}$, and the free parameters are 
$\{\vth, R_0\} = \{m_c, \s, R_0\}$ in this case. 
Using \Eq{mpbh} and \Eq{Fm}, it is easily to get
\e
\mpbh = m_c \exp \(-\frac{\s^2}{2}\),
\q
\e 
F(m) = \frac{m_c}{\sqrt{2\pi} \s m^2} \exp \(-\frac{\s^2}{2}-\frac{\ln^2\(m/m_c\)}{2\s^2}\).
\q

Using data of $10$ BBHs observed by \lvc\ O1 and O2 observations and performing
the hierarchical Bayesian inference, we obtain $m_c =8.9^{+7.8}_{-7.3} \Msun$,
$\s = 0.91^{+0.50}_{-0.42}$, and $R_0 = 55^{+42}_{-27} \gpcyr$.
It is then easy to infer the abundance of PBHs in CDM to be 
$\fpbh = 2.6^{+6.8}_{-1.4} \times 10^{-3}$ from the posterior distribution of 
local merger rate $R_0$.
The results of local merger rate and abundance of PBHs are consistent with
the previous estimations, confirming that the main components of CDM should
not be made of stellar mass PBHs.
The posteriors of parameters $\{\vth, R_0\} = \{m_c, \s, R_0\}$ are shown 
in \Fig{posterior-log}.
\begin{figure}[htbp!]
	\centering
	\includegraphics[width = 0.48\textwidth]{posterior-log.pdf}
	\caption{\label{posterior-log}
		The marginalized one- and two-dimensional posterior distributions for 
		parameters $\{\vth, R_0\} = \{m_c, \s, R_0\}$ in the log-normal mass function of PBHs, by using $10$ BBH events from \lvc\ O1 and O2 observing runs.
		The contours are at the $68\%$ and $95\%$ credible levels, respectively. 
	}
\end{figure}

\begin{figure}[htbp!]
	\centering
	\includegraphics[width = 0.45\textwidth]{ratio-log.pdf}
	\caption{\label{ratio-log}
		The ratio of merger rate density from second-merger history
		to that from first-merger history,
		$\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$. Note that the parameters $\{m_c, \sigma\}$ in \Eq{log} are fixed to their best-fit values.
	}
\end{figure}

\Fig{ratio-log} shows the ratio of merger rate density from second-merger history
to the one from first-merger history, namely 
$\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing $\{\vth, R_0\}$ to their best-fit values.
The correction to total merger rate density from 
second-merger history is larger as component masses are heavier.
However, the ratio of merger rate from 
second-merger history to the one from first-merger history is negligible, namely
$R_2(t_0)/R_1(t_0) = 3.0\%$.
This is because the major contribution to the merger rate comes from the binaries with masses less than $50\Msun$.
Therefore the merger history effect can be safely ignored
when estimating the merger rate of PBHs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Power-law mass function}
We now consider a power-law mass function of PBHs as \cite{Carr:1975qj}
\e\label{power} 
    P(m) = \frac{\al-1}{M} \(\frac{m}{M}\)^{-\al},
\q
where $m>M$, and $\al>1$ is the power-law index. The power-law form is a commonly used mass function as it naturally arises if PBHs are formed from primordial energy density fluctuations due to a scale-invariant primordial power spectrum \cite{Carr:2016drx,Carr:2017jsz}.
Note that $\vth=\{\al, M\}$ and the free parameters are 
$\{\vth, R_0\} = \{\al, M, R_0\}$ in this case. 
Using \Eq{mpbh} and \Eq{Fm}, it is easily to get
\e
    \mpbh = M \frac{\al}{\al-1},
\q
\e 
    F(m) = \frac{\al}{m} \(\frac{m}{M}\)^{-\al}.
\q

Using data of $10$ BBHs observed by \lvc\ O1 and O2 observations and performing
the hierarchical Bayesian inference, we obtain $\al = 2.41^{+1.00}_{-0.87}$,
$M = 7.4^{+1.4}_{-3.3} \Msun$, and $R_0 = 48^{+37}_{-24} \gpcyr$.
It is then easy to infer the abundance of PBHs in CDM to be 
$\fpbh = 2.8^{+1.8}_{-1.2} \times 10^{-3}$ from the posterior distribution of local merger rate $R_0$.
The results of local merger rate and abundance of PBHs are consistent with
the previous estimations, confirming that the main components of CDM should
not be made of stellar mass PBHs.
The posteriors of parameters $\{\vth, R_0\} = \{\al, M, R_0\}$ are shown 
in \Fig{posterior-power}.

\begin{figure}[htbp!]
	\centering
	\includegraphics[width = 0.48\textwidth]{posterior-power.pdf}
	\caption{\label{posterior-power}
		The marginalized one- and two-dimensional posterior distributions for 
    parameters $\{\vth, R_0\} = \{\al, M, R_0\}$ in the power-law mass function 
    of PBHs, by using $10$ BBH events from \lvc\ O1 and O2 observing runs.
    The contours are at the $68\%$ and $95\%$ credible levels, respectively. 
	}
\end{figure}

\begin{figure}[htbp!]
	\centering
	\includegraphics[width = 0.45\textwidth]{ratio-power.pdf}
	\caption{\label{ratio-power}
		The ratio of merger rate density from second-merger history
        to that from first-merger history,
        $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$. Note that the parameters $\{\al, M\}$ in \Eq{power} are fixed to their best-fit values.
	}
\end{figure}

\Fig{ratio-power} shows the ratio of merger rate density from second-merger history
to the one from first-merger history, namely 
$\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing $\{\vth, R_0\}$ to their best-fit values.
It is clearly that the correction of total merger rate density from 
second-merger history is less than $10\%$.
It is then readily to calculate the ratio of merger rate from 
second-merger history to the one from first-merger history, 
$R_2(t_0)/R_1(t_0) = 0.5\%$.
We therefore conclude that the merger history effect can be safely ignored
when estimating the merger rate (density) of PBHs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{conclusion}Conclusion}

In this paper, we use the publicly available GW data of $10$ BBH events from 
\lvc\ O1 and O2 observing runs to constrain the merger rate distribution 
of PBHs by taking into account the effect of merger history.
Considering two concrete mass functions of PBHs, a power-law PDF and 
a log-normal one, we demonstrate that the contribution of merger rate (density)
from second-merger history to total merger rate (density) is 
subdominant, and hence the second-merger history effect can be safely ignored.
As third-merger (and later merger) history will make even less contribution to 
the total merger rate (density), we conclude that the effect of merger history
is subdominant and can be neglected when evaluating the merger rate of PBH
binaries.

Furthermore, the results of local merger rate and abundance of PBHs inferred from the updated
analysis are consistent with the previous estimations, 
confirming that the main components of CDM should not be made of stellar 
mass PBHs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% acknowledgments %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgments}
We thank the anonymous referee for providing constructive comments and suggestions to improve the quality of this paper. 
We would also like to thank Zu-Cheng Chen and Lang Liu for useful conversations.
This work is supported by grants from National Natural Science Foundation of China (grant No.11847107). 
This research has made use of data, software and/or web tools obtained 
from the Gravitational Wave Open Science Center \cite{Vallisneri:2014vxa}
(\url{https://www.gw-openscience.org}), a service of LIGO Laboratory, 
the LIGO Scientific Collaboration and the Virgo Collaboration. 
LIGO is funded by the U.S. National Science Foundation. 
Virgo is funded by the French Centre National de Recherche Scientifique (CNRS),
the Italian Istituto Nazionale della Fisica Nucleare (INFN) and the Dutch Nikhef,
with contributions by Polish and Hungarian institutes. 
\end{acknowledgments}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %%% references %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{./ref}

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-06-22 code/events.jl

@@ -17,6 +17,24 @@ GWTC2_events = [
     "190915_235702", "190924_021846", "190929_012149", "190930_133541"
 ];
 
+GWTC3_events = [
+    "150914", "151012", "151226", "170104", "170608",
+    "170729", "170809", "170814", "170818", "170823",
+    "190408_181802", "190412", "190413_134308", "190421_213856", "190425", 
+    "190503_185404", "190512_180714", "190513_205428", "190517_055101", "190519_153544",
+    "190521", "190521_074359", "190527_092055", "190602_175927", "190620_030421", 
+    "190630_185205", "190701_203306", "190706_222641", "190707_093326", "190708_232457",
+    "190720_000836", "190727_060333", "190728_064510", "190803_022701", "190814", 
+    "190828_063405", "190828_065509", "190910_112807", "190915_235702", "190924_021846", 
+    "190925_232845", "190929_012149", "190930_133541", "191105_143521", "191109_010717", 
+    "191127_050227", "191129_134029", "191204_171526", "191215_223052", "191216_213338", 
+    "191222_033537", "191230_180458", "200105_162426", "200112_155838", "200115_042309", 
+    "200128_022011", "200129_065458", "200202_154313", "200208_130117", "200209_085452", 
+    "200219_094415", "200224_222234", "200225_060421", "200302_015811", "200311_115853", 
+    "200316_215756", "190413_052954", "190426_152155", "190719_215514", "190725_174728",
+    "190731_140936", "190805_211137", "190917_114630", "191103_012549", "200216_220804"
+];
+
 # hight false alarm rate events
 high_FAR_event = [
     "190426_152155", "190719_215514", "190909_114149"
@@ -26,18 +44,28 @@ high_FAR_event = [
 high_spin_events = [
     "151226", "170729", 
     "190412", "190425", "190517_055101", "190519_153544", "190620_030421", 
-    "190706_222641", "190719_215514", "190720_000836", "190728_064510", "190828_063405"        
+    "190719_215514", "190720_000836", "190728_064510", "190828_063405",
+    "191204_171526", "191216_213338", "200316_215756", "190719_215514", "191103_012549"
 ]
 
 # events with secondary mass smaller than 3 solar masses
 light_mass_events = [
-    "190425", "190426_152155", "190814"
[…]

### 2022-09-25 latex/reply.tex
update

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[
%a4paper,       % letterpaper, a4paper, a5paper
%10pt,              % 10pt, 11pt, 12pt
%reprint,           % journal's actual layout
preprint,          % 12pt, single-column
superscriptaddress,% authors with affiliations via superscripts
amsmath,           % add AMS-Latex features
amssymb,           % add extra AMS symbols, including amsfonts
aps,               % aps or aip
prl,               % prl, pra, prb, prc, prd, pre, prstab
%showpacs,          % make PACS codes appear
notitlepage,       % control appearance of title page
longbibliography,  % show  article titles in the bibliography
floatfix,          % process floats as early as possible
%showkeys,          % option to make keywords appear
%titlepage,         %
%eqsecnum,          % number equations by section
nofootinbib,
onecolumn,
]{revtex4-1}

\usepackage{amsmath}
\usepackage{graphicx}   % include figures
\usepackage[
colorlinks=true,        % color link
citecolor=blue,         % cite color
linkcolor=blue,         % link color
urlcolor=blue           % url color
]{hyperref}             % create hyperlinks

\begin{document}

Dear Editor and Referee, \\

We thank the referee for careful reading of our manuscript and for his/her insightful suggestions and comments. 
We enclose our reply to comments in the following part of our reply. 
\begin{enumerate}
	\item The power-law and log-normal mass functions are commonly used in literature and are worthwhile to investigate because they are well motivated by the formation mechanisms of primordial black holes (PBHs). The mass function of PBHs is closely related to shape of primordial power spectrum when PBHs are formed. It is believed that power-law and log-normal mass functions can be representatives of quite a large class of mass distributions. We added corresponding explanations after Eq.(23) and Eq.(26), respectively, to address the motivations of using these two mass functions.

    \item The text after Eq.~(4) to the end of Section 2 was completely rewritten as suggested by the referee. We added some necessary intermediate steps and explanations to make the derivations much more readable.

    \item We added units to the labels of figures and enlarge labels' font size. Furthermore, more explanations were added to the captions.

    \item We corrected the grammatical errors as pointed out by the referee.

\end{enumerate}

Please reconsider our paper for publication in PRD. \\

Best wishes,

You Wu

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

### 2022-09-25 code/GWTC2_lognormal_heavy_mass.jl

@@ -1,0 +1,167 @@
+# modify model
+model = "GWTC2_lognormal_heavy_mass"
+
+include("utils.jl")
+
+# modify post_events
+posts = [get_post_func(event) for event in GWTC2_events_heavy_mass];
+save("backup/posts_$(model).jld2", Dict("posts" => posts))
+posts = load("backup/posts_$(model).jld2", "posts");
+
+f = 0.0025693801260000975 # fpbh
+log_fpbh = 1e-3
+mc = 8.896735628637506
+σc = 0.9108320383237213
+i = 10
+j = 30
+
+function mergerRateDensity1st(i, j, mc, σc, f)
+    210084.52488130186/(i^2 * j^2 * σc^2) * exp(-(743*σc^4 + 1369*log(i/mc)^2 + 1369*log(j/mc)^2)/(2738*σc^2)) * (i*j)^(3/37) * (i+j)^(36/37) * ((exp(σc^2/2)*f)/mc)^(53/37) * mc^(53/37)
+end
+
+function mergerRateDensity2nd1(i, j, mc, σc, f)
+    tmp1 = 1009.5488113544313 * f^(69/37) * i^(6/37) * (i+j)^(72/37) / j^(68/37) / σc^3 
+    tmp2 = exp(-(-3318*σc^4 + 1369*log(j/mc)^2)/(2738*σc^2))
+    
+    int0(e) = exp(-(1369*log(e/mc)^2 + 1369*log((-e+i)/mc)^2)/(2738*σc^2)) / (e^2 * (-e + i)^2)
+    int(e) = i * int0(i*e)
+    function integrand(x, f)
+        f[1] = int(x[1])
+    end
+    result, err = cuhre(integrand, rtol=1e-1)
+    tmp1 * tmp2 * result[1]
+end
+
+mergerRateDensity2nd(i, j, mc, σc, f) = 0.5 * (mergerRateDensity2nd1(i, j, mc, σc, f) + mergerRateDensity2nd1(j, i, mc, σc, f))
+
+# function mergerRateDensity(i, j, mc, σc, f)
+#     if i >= j
+#         mergerRateDensity1st(i, j, mc, σc, f) + mergerRateDensity2nd(i, j, mc, σc, f)
+#     else
+#         mergerRateDensity(j, i, mc, σc, f)
+#     end
+# end
+
[…]

### 2022-09-25 code/cosmology.jl

@@ -1,0 +1,95 @@
+const yr = 365.25 * 24 * 3600 # seconds
+
+abstract type Cosmology end
+struct LCDM <: Cosmology
+    h::Float64 # hubble const
+    H0::Float64
+    t0::Float64
+
+    ΩM::Float64
+    ΩΛ::Float64
+
+    HH::Function
+    ϕt::Function
+    ϕr::Function
+    ϕV::Function
+    zt::Function
+    tz::Function
+    rz::Function
+    DLz::Function # luminosity distance
+
+
+    function LCDM(h, ΩM)
+        ΩΛ = 1 - ΩM
+        H0 = 100h / 3.08567758128e19 # https://www.unitconverters.net/length/megaparsec-to-kilometer.htm
+
+        # eq.(A2) of arxiv:1712.01168
+        HH(z) = sqrt(ΩΛ + ΩM * (1 + z)^3)
+
+        # eq.(A5) of arxiv:1712.01168
+        function ϕt0(z)
+            int0(z) = 1 / HH(z) / (1 + z)
+            int(y) = int0(z + y / (1 - y)) / (1 - y)^2
+            # int(y) = 1/ (1-y) / (1+(1-y)*z) / HH(y/(1-y) + z)
+            function integrand(x, f)
+                f[1] = int(x[1])
+            end
+            result, err = cuhre(integrand, rtol=1e-3)
+            result[1]
+        end
+
+        # eq.(A6) of arxiv:1712.01168
+        function ϕr0(z)
+            int0(z) = 1 / HH(z)
+            int(y) = z * int0(z * y)
+            # int(y) = z / HH(z*y)
+            function integrand(x, f)
+                f[1] = int(x[1])
+            end
+            result, err = cuhre(integrand, rtol=1e-3, minevals=10^5)
+            result[1]
+        end
+
+        logzs = -10:0.01:2
+        logϕts = log10.(ϕt0.(10 .^ logzs))
+        logts = logϕts .- log10(H0) # eq.(A5) of arxiv:1712.01168
+        logϕrs = log10.(ϕr0.(10 .^ logzs))
+
+        writedlm("logzs_logϕts.txt", zip(logzs, logϕts))
+        log_log_ϕt_inter = interpolate((logzs,), logϕts, Gridded(Linear()))
[…]

### 2022-09-25 code/merger_rate.jl

@@ -1,0 +1,266 @@
+using Trapz, MathLink, SpecialFunctions
+
+const m_min = 1e-1
+const m_max = 1e3
+
+# # using beta function from mathematica
+# beta0 = W"Beta"(W"z", W"a", W"b")
+# beta(z, a, b) = weval(beta0; z=z, a=a, b=b)
+
+
+# log-normal mass function 
+function mergerRateDensity1st0_log(mc, σc, log_fpbh, i, j)
+    fpbh = 10^log_fpbh
+    210084.52488130186 / (i^2 * j^2 * σc^2) * exp(-(743 * σc^4 + 1369 * log(i / mc)^2 + 1369 * log(j / mc)^2) / (2738 * σc^2)) * (i * j)^(3 / 37) * (i + j)^(36 / 37) * ((exp(σc^2 / 2) * fpbh) / mc)^(53 / 37) * mc^(53 / 37)
+end
+
+function mergerRateDensity2nd00_log(mc, σc, log_fpbh, i, j)
+    fpbh = 10^log_fpbh
+    tmp1 = 1009.5488113544313 * fpbh^(69 / 37) * i^(6 / 37) * (i + j)^(72 / 37) / j^(68 / 37) / σc^3
+    tmp2 = exp(-(-3318 * σc^4 + 1369 * log(j / mc)^2) / (2738 * σc^2))
+
+    int0(e) = exp(-(1369 * log(e / mc)^2 + 1369 * log((-e + i) / mc)^2) / (2738 * σc^2)) / (e^2 * (-e + i)^2)
+
+    vx = range(1e-1, i - 1e-1, length=20)
+    M = [int0(e) for e = vx]
+    # @show M
+    result = trapz((vx), M)
+
+    # int(e) = i * int0(i * e)
+    # function integrand(x, f)
+    #     f[1] = int(x[1])
+    # end
+    # result, err = cuhre(integrand, rtol=1e-1)
+    tmp1 * tmp2 * result[1]
+end
+
+function mergerRateDensity2nd0_log(mc, σc, log_fpbh, i, j)
+    0.5 * (mergerRateDensity2nd00_log(mc, σc, log_fpbh, i, j) + mergerRateDensity2nd00_log(mc, σc, log_fpbh, j, i))
+end
+
[…]

### 2022-09-25 code/utils.jl

@@ -1,82 +1,308 @@
-using Cuba
-include("events.jl")
-using Revise
-using Cuba
-using HypergeometricFunctions
-using SpecialFunctions
-# using GSL
-using BenchmarkTools
-using Interpolations
-using Distributions
-using KernelDensity
-using DelimitedFiles
-using Memoize
-using StatsPlots
-using NestedSamplers
-using StatsBase: sample
-using Random
-# using MCMCChains
-using FileIO
 using BAT
-using IntervalSets
+using BenchmarkTools
+using Cuba
+using DelimitedFiles
 using FileIO
-using LaTeXStrings
-using Roots
-# using GWSC
+using Interpolations
 using IntervalSets
-using AbstractMCMC
-# AbstractMCMC.setprogress!(false)
-Random.seed!(8452);
+using LaTeXStrings
+using Memoize
+using Revise
+using StatsPlots
+using Trapz
 
-const m_min = 3
-const m_max = 130
-const δm = m_max - m_min
+const yr = 365.25 * 24 * 3600 # seconds
+const Mpc_to_km = 3.08567758128e19 # https://www.unitconverters.net/length/megaparsec-to-kilometer.htm
+const lc = 2.99792458e8; # speed of light in m/s
+const Gpc_in_m = 1e6 * Mpc_to_km;
 
-# function beta_func(x, y, a, b)
-#     result = sf_beta_inc(a, b, y) - sf_beta_inc(a, b, x)
-#     result * sf_beta(a, b)
-# end
+abstract type Cosmology end
+struct LCDM <: Cosmology
+    h::Float64 # hubble const
+    t0::Float64
+    ΩM::Float64
+    ΩΛ::Float64
 
-@memoize function beta_func2(x, y, a, b)
-    δ = y - x
-    int0(t) = t^(a-1) * (1-t)^(b-1)
-    int(t) = δ * int0(x + δ*t)
-    function integrand(x, f)
-        f[1] = int(x[1])
+    t_at_z::Function
+    z_at_DL::Function # luminosity distance
+    dDL_over_dz::Function
+    dVC_over_dz::Function
+
+    function LCDM(h, ΩM)
+        ΩΛ = 1 - ΩM
+        H0 = 100h / Mpc_to_km # 1/second
+
+        # eq.(A2) of arxiv:1712.01168
[…]

### 2022-09-26 code/cosmology.jl
Updates from Overleaf

@@ -1,95 +1,0 @@
-const yr = 365.25 * 24 * 3600 # seconds
-
-abstract type Cosmology end
-struct LCDM <: Cosmology
-    h::Float64 # hubble const
-    H0::Float64
-    t0::Float64
-
-    ΩM::Float64
-    ΩΛ::Float64
-
-    HH::Function
-    ϕt::Function
-    ϕr::Function
-    ϕV::Function
-    zt::Function
-    tz::Function
-    rz::Function
-    DLz::Function # luminosity distance
-
-
-    function LCDM(h, ΩM)
-        ΩΛ = 1 - ΩM
-        H0 = 100h / 3.08567758128e19 # https://www.unitconverters.net/length/megaparsec-to-kilometer.htm
-
-        # eq.(A2) of arxiv:1712.01168
-        HH(z) = sqrt(ΩΛ + ΩM * (1 + z)^3)
-
-        # eq.(A5) of arxiv:1712.01168
-        function ϕt0(z)
-            int0(z) = 1 / HH(z) / (1 + z)
-            int(y) = int0(z + y / (1 - y)) / (1 - y)^2
-            # int(y) = 1/ (1-y) / (1+(1-y)*z) / HH(y/(1-y) + z)
-            function integrand(x, f)
-                f[1] = int(x[1])
-            end
-            result, err = cuhre(integrand, rtol=1e-3)
-            result[1]
-        end
-
-        # eq.(A6) of arxiv:1712.01168
-        function ϕr0(z)
-            int0(z) = 1 / HH(z)
-            int(y) = z * int0(z * y)
-            # int(y) = z / HH(z*y)
-            function integrand(x, f)
-                f[1] = int(x[1])
-            end
-            result, err = cuhre(integrand, rtol=1e-3, minevals=10^5)
-            result[1]
-        end
-
-        logzs = -10:0.01:2
-        logϕts = log10.(ϕt0.(10 .^ logzs))
-        logts = logϕts .- log10(H0) # eq.(A5) of arxiv:1712.01168
-        logϕrs = log10.(ϕr0.(10 .^ logzs))
-
-        writedlm("logzs_logϕts.txt", zip(logzs, logϕts))
-        log_log_ϕt_inter = interpolate((logzs,), logϕts, Gridded(Linear()))
[…]

### 2022-09-26 code/merger_rate.jl

@@ -1,266 +1,0 @@
-using Trapz, MathLink, SpecialFunctions
-
-const m_min = 1e-1
-const m_max = 1e3
-
-# # using beta function from mathematica
-# beta0 = W"Beta"(W"z", W"a", W"b")
-# beta(z, a, b) = weval(beta0; z=z, a=a, b=b)
-
-
-# log-normal mass function 
-function mergerRateDensity1st0_log(mc, σc, log_fpbh, i, j)
-    fpbh = 10^log_fpbh
-    210084.52488130186 / (i^2 * j^2 * σc^2) * exp(-(743 * σc^4 + 1369 * log(i / mc)^2 + 1369 * log(j / mc)^2) / (2738 * σc^2)) * (i * j)^(3 / 37) * (i + j)^(36 / 37) * ((exp(σc^2 / 2) * fpbh) / mc)^(53 / 37) * mc^(53 / 37)
-end
-
-function mergerRateDensity2nd00_log(mc, σc, log_fpbh, i, j)
-    fpbh = 10^log_fpbh
-    tmp1 = 1009.5488113544313 * fpbh^(69 / 37) * i^(6 / 37) * (i + j)^(72 / 37) / j^(68 / 37) / σc^3
-    tmp2 = exp(-(-3318 * σc^4 + 1369 * log(j / mc)^2) / (2738 * σc^2))
-
-    int0(e) = exp(-(1369 * log(e / mc)^2 + 1369 * log((-e + i) / mc)^2) / (2738 * σc^2)) / (e^2 * (-e + i)^2)
-
-    vx = range(1e-1, i - 1e-1, length=20)
-    M = [int0(e) for e = vx]
-    # @show M
-    result = trapz((vx), M)
-
-    # int(e) = i * int0(i * e)
-    # function integrand(x, f)
-    #     f[1] = int(x[1])
-    # end
-    # result, err = cuhre(integrand, rtol=1e-1)
-    tmp1 * tmp2 * result[1]
-end
-
-function mergerRateDensity2nd0_log(mc, σc, log_fpbh, i, j)
-    0.5 * (mergerRateDensity2nd00_log(mc, σc, log_fpbh, i, j) + mergerRateDensity2nd00_log(mc, σc, log_fpbh, j, i))
-end
-
[…]

### 2022-09-26 code/utils.jl

@@ -1,308 +1,82 @@
-using BAT
-using BenchmarkTools
 using Cuba
-using DelimitedFiles
-using FileIO
-using Interpolations
-using IntervalSets
-using LaTeXStrings
-using Memoize
+include("events.jl")
 using Revise
+using Cuba
+using HypergeometricFunctions
+using SpecialFunctions
+# using GSL
+using BenchmarkTools
+using Interpolations
+using Distributions
+using KernelDensity
+using DelimitedFiles
+using Memoize
 using StatsPlots
-using Trapz
+using NestedSamplers
+using StatsBase: sample
+using Random
+# using MCMCChains
+using FileIO
+using BAT
+using IntervalSets
+using FileIO
+using LaTeXStrings
+using Roots
+# using GWSC
+using IntervalSets
+using AbstractMCMC
+# AbstractMCMC.setprogress!(false)
+Random.seed!(8452);
 
-const yr = 365.25 * 24 * 3600 # seconds
-const Mpc_to_km = 3.08567758128e19 # https://www.unitconverters.net/length/megaparsec-to-kilometer.htm
-const lc = 2.99792458e8; # speed of light in m/s
-const Gpc_in_m = 1e6 * Mpc_to_km;
+const m_min = 3
+const m_max = 130
+const δm = m_max - m_min
 
-abstract type Cosmology end
-struct LCDM <: Cosmology
-    h::Float64 # hubble const
-    t0::Float64
-    ΩM::Float64
-    ΩΛ::Float64
+# function beta_func(x, y, a, b)
+#     result = sf_beta_inc(a, b, y) - sf_beta_inc(a, b, x)
+#     result * sf_beta(a, b)
+# end
 
-    t_at_z::Function
-    z_at_DL::Function # luminosity distance
-    dDL_over_dz::Function
-    dVC_over_dz::Function
-
-    function LCDM(h, ΩM)
-        ΩΛ = 1 - ΩM
-        H0 = 100h / Mpc_to_km # 1/second
-
-        # eq.(A2) of arxiv:1712.01168
-        Ez(z) = sqrt(ΩΛ + ΩM * (1 + z)^3)
-
-        # eq.(A5) of arxiv:1712.01168
-        function ϕt0(z)
-            int0(z) = 1 / Ez(z) / (1 + z)
-            int(y) = int0(z + y / (1 - y)) / (1 - y)^2
[…]

### 2022-09-26 latex/paper.tex
Updates from Overleaf

@@
 \begin{acknowledgments}
-We thank the anonymous referee for providing constructive comments and suggestions to improve the quality of this paper. 
-We would also like to thank Zu-Cheng Chen and Lang Liu for useful conversations.
+% We thank the referee for providing constructive comments and suggestions to improve the quality of this paper. 
+We would also like to thank Xingjiang Zhu, Shen-Shi Du for useful conversations.
 This work is supported by grants from National Natural Science Foundation of China (grant No.11847107). 

### 2022-09-26 latex/paper.tex
update

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
-\title{The merger history of primordial-black-hole binaries implied by GWTC-3}
+\title{The merger history of primordial-black-hole binaries inferred from GWTC-3}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\author{Zu-Cheng~Chen}
-%\email{zucheng.chen@bnu.edu.cn}
-%\affiliation{Department of Astronomy, Beijing Normal University, Beijing 100875, China}
-%\affiliation{Advanced Institute of Natural Sciences, Beijing Normal University, Zhuhai 519087, China}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\author{You~Wu}
-%\email{Corresponding author: youwuphy@gmail.com}
-%\affiliation{College of Mathematics and Physics, Hunan University of Arts and Science, Changde, 415000, China}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\author{Zu-Cheng~Chen}
+\email{zucheng.chen@bnu.edu.cn}
+\affiliation{Department of Astronomy, Beijing Normal University, Beijing 100875, China}
+\affiliation{Advanced Institute of Natural Sciences, Beijing Normal University, Zhuhai 519087, China}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\author{Zhi-Qiang~You}
+\email{zhiqiang.you@bnu.edu.cn}
+\affiliation{Department of Astronomy, Beijing Normal University, Beijing 100875, China}
+\affiliation{Advanced Institute of Natural Sciences, Beijing Normal University, Zhuhai 519087, China}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\author{You~Wu}
+\email{youwuphy@gmail.com}
+\affiliation{College of Mathematics and Physics, Hunan University of Arts and Science, Changde, 415000, China}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\author{Lang~Liu}
+\email{Corresponding author: liulang@bnu.edu.cn}
+\affiliation{Department of Astronomy, Beijing Normal University, Beijing 100875, China}
+\affiliation{Advanced Institute of Natural Sciences, Beijing Normal University, Zhuhai 519087, China}
 
@@
 	\centering
-	\includegraphics[width = 0.48\textwidth]{posterior-log.pdf}
+	\includegraphics[width = 0.48\textwidth]{post-log.pdf}
 	\caption{\label{posterior-log}
@@
 	\centering
-	\includegraphics[width = 0.48\textwidth]{posterior-power.pdf}
+	\includegraphics[width = 0.48\textwidth]{post-power.pdf}
 	\caption{\label{posterior-power}

### 2022-09-26 latex/paper.tex
Updates from Overleaf
update

@@
 	\centering
-	\includegraphics[width = 0.48\textwidth]{post-log.pdf}
+	\includegraphics[width=0.5\textwidth]{post-log.pdf}
 	\caption{\label{posterior-log}
@@
 	\centering
-	\includegraphics[width = 0.45\textwidth]{ratio-log.pdf}
+	\includegraphics[width=0.5\textwidth]{ratio-log.pdf}
 	\caption{\label{ratio-log}
@@
 	\centering
-	\includegraphics[width = 0.48\textwidth]{post-power.pdf}
+	\includegraphics[width=0.5\textwidth]{post-power.pdf}
 	\caption{\label{posterior-power}
@@
 	\centering
-	\includegraphics[width = 0.45\textwidth]{ratio-power.pdf}
+	\includegraphics[width=0.5\textwidth]{ratio-power.pdf}
 	\caption{\label{ratio-power}
@@
 
+\subsection{Broken Power-law mass function}
+We now consider a power-law mass function of PBHs as \cite{Carr:1975qj}
+\e\label{bpower} 
+P(m) = \frac{\al-1}{M} \(\frac{m}{M}\)^{-\al},
+\q
+where $m>M$, and $\al>1$ is the power-law index.
+The power-law form is a commonly used mass function as it naturally arises if PBHs are formed from primordial energy density fluctuations due to a scale-invariant primordial power spectrum \cite{Carr:2016drx,Carr:2017jsz}.
+Note that $\vth=\{\al, M\}$ and the free parameters are 
+$\{\vth, R_0\} = \{\al, M, R_0\}$ in this case. 
+Using \Eq{mpbh} and \Eq{Fm}, it is easily to get
+\e
+\mpbh = M \frac{\al}{\al-1},
+\q
+\e 
+F(m) = \frac{\al}{m} \(\frac{m}{M}\)^{-\al}.
+\q
+
+Using data of $10$ BBHs observed by \lvc\ O1 and O2 observations and performing
+the hierarchical Bayesian inference, we obtain $\al = 2.41^{+1.00}_{-0.87}$,
+$M = 7.4^{+1.4}_{-3.3} \Msun$, and $R_0 = 48^{+37}_{-24} \gpcyr$.
+It is then easy to infer the abundance of PBHs in CDM to be 
+$\fpbh = 2.8^{+1.8}_{-1.2} \times 10^{-3}$ from the posterior distribution of local merger rate $R_0$.
+The results of local merger rate and abundance of PBHs are consistent with
+the previous estimations, confirming that the main components of CDM should
+not be made of stellar mass PBHs.
+The posteriors of parameters $\{\vth, R_0\} = \{\al, M, R_0\}$ are shown 
+in \Fig{posterior-power}.
+
+\begin{figure}[htbp!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{post-bpower.pdf}
+	\caption{\label{posterior-bpower}
+		The marginalized one- and two-dimensional posterior distributions for 
+		parameters $\{\vth, R_0\} = \{\al, M, R_0\}$ in the power-law mass function 
+		of PBHs, by using $10$ BBH events from \lvc\ O1 and O2 observing runs.
+		The contours are at the $68\%$ and $95\%$ credible levels, respectively. 
+	}
+\end{figure}
+
+\begin{figure}[htbp!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{ratio-bpower.pdf}
+	\caption{\label{ratio-bpower}
+		The ratio of merger rate density from second-merger history
+		to that from first-merger history,
+		$\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$. Note that the parameters $\{\al, M\}$ in \Eq{power} are fixed to their best-fit values.
+	}
+\end{figure}
+
+\Fig{ratio-power} shows the ratio of merger rate density from second-merger history
+to the one from first-merger history, namely 
+$\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing $\{\vth, R_0\}$ to their best-fit values.
+It is clearly that the correction of total merger rate density from 
+second-merger history is less than $10\%$.
+It is then readily to calculate the ratio of merger rate from 
+second-merger history to the one from first-merger history, 
+$R_2(t_0)/R_1(t_0) = 0.5\%$.
+We therefore conclude that the merger history effect can be safely ignored
+when estimating the merger rate (density) of PBHs.
+
+\subsection{CC mass function}
+We now consider a power-law mass function of PBHs as \cite{Carr:1975qj}
+\e\label{CC} 
+P(m) = \frac{\al-1}{M} \(\frac{m}{M}\)^{-\al},
+\q
+where $m>M$, and $\al>1$ is the power-law index.
+The power-law form is a commonly used mass function as it naturally arises if PBHs are formed from primordial energy density fluctuations due to a scale-invariant primordial power spectrum \cite{Carr:2016drx,Carr:2017jsz}.
+Note that $\vth=\{\al, M\}$ and the free parameters are 
+$\{\vth, R_0\} = \{\al, M, R_0\}$ in this case. 
+Using \Eq{mpbh} and \Eq{Fm}, it is easily to get
+\e
+\mpbh = M \frac{\al}{\al-1},
+\q
+\e 
+F(m) = \frac{\al}{m} \(\frac{m}{M}\)^{-\al}.
+\q
+
+Using data of $10$ BBHs observed by \lvc\ O1 and O2 observations and performing
+the hierarchical Bayesian inference, we obtain $\al = 2.41^{+1.00}_{-0.87}$,
+$M = 7.4^{+1.4}_{-3.3} \Msun$, and $R_0 = 48^{+37}_{-24} \gpcyr$.
+It is then easy to infer the abundance of PBHs in CDM to be 
+$\fpbh = 2.8^{+1.8}_{-1.2} \times 10^{-3}$ from the posterior distribution of local merger rate $R_0$.
+The results of local merger rate and abundance of PBHs are consistent with
+the previous estimations, confirming that the main components of CDM should
+not be made of stellar mass PBHs.
+The posteriors of parameters $\{\vth, R_0\} = \{\al, M, R_0\}$ are shown 
+in \Fig{posterior-power}.
+
+\begin{figure}[htbp!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{post-CC.pdf}
+	\caption{\label{post-CC}
+		The marginalized one- and two-dimensional posterior distributions for 
+		parameters $\{\vth, R_0\} = \{\al, M, R_0\}$ in the power-law mass function 
+		of PBHs, by using $10$ BBH events from \lvc\ O1 and O2 observing runs.
+		The contours are at the $68\%$ and $95\%$ credible levels, respectively. 
+	}
+\end{figure}
+
+\begin{figure}[htbp!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{ratio-CC.pdf}
+	\caption{\label{ratio-CC}
+		The ratio of merger rate density from second-merger history
+		to that from first-merger history,
+		$\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$. Note that the parameters $\{\al, M\}$ in \Eq{power} are fixed to their best-fit values.
+	}
+\end{figure}
+
+\Fig{ratio-power} shows the ratio of merger rate density from second-merger history
+to the one from first-merger history, namely 
+$\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing $\{\vth, R_0\}$ to their best-fit values.
+It is clearly that the correction of total merger rate density from 
+second-merger history is less than $10\%$.
+It is then readily to calculate the ratio of merger rate from 
+second-merger history to the one from first-merger history, 
+$R_2(t_0)/R_1(t_0) = 0.5\%$.
+We therefore conclude that the merger history effect can be safely ignored
+when estimating the merger rate (density) of PBHs.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % We thank the referee for providing constructive comments and suggestions to improve the quality of this paper. 
-We would also like to thank Xingjiang Zhu, Shen-Shi Du for useful conversations.
+We would also like to thank Xingjiang Zhu, Xiao-Jin Liu, Shen-Shi Du, and Zhu Yi for useful discussions.
 This work is supported by grants from National Natural Science Foundation of China (grant No.11847107). 

### 2022-09-26 latex/paper.tex
update

@@
 \nc{\cR}{\mathcal{R}}
+\nc{\mU}{{\mathcal{U}}}
+\nc{\Mc}{{M_\mathrm{c}}}
+\nc{\Mf}{{M_\mathrm{f}}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We now consider a power-law mass function of PBHs as \cite{Carr:1975qj}
-\e\label{bpower} 
-P(m) = \frac{\al-1}{M} \(\frac{m}{M}\)^{-\al},
-\q
+\begin{equation}
+	P(m)= \left(\frac{m_*}{\alpha_1+1}-\frac{m_*}{\alpha_2-1}\right)^{-1} \begin{cases}\left(m / m_*\right)^{\alpha_1}, & m<m_* \\ \left(m / m_*\right)^{-\alpha_2}, & m>m_*\end{cases}
+\end{equation}
 where $m>M$, and $\al>1$ is the power-law index.
@@
 \subsection{CC mass function}
-We now consider a power-law mass function of PBHs as \cite{Carr:1975qj}
-\e\label{CC} 
-P(m) = \frac{\al-1}{M} \(\frac{m}{M}\)^{-\al},
+We now consider the critical collapse mass function taking the form of \cite{Niemeyer:1997mt,Yokoyama:1998xd,Carr:2016hva,Gow:2020cou}
+\e
+P(m, \alpha, M_{\mathrm{f}})=\frac{\alpha^2\,  m^\alpha}{M_{\mathrm{f}}^{1+\alpha}\, \Gamma(1 / \alpha)} \exp \left(-(m/M_{\mathrm{f}})^{\alpha}\right),
 \q
-where $m>M$, and $\al>1$ is the power-law index.
-The power-law form is a commonly used mass function as it naturally arises if PBHs are formed from primordial energy density fluctuations due to a scale-invariant primordial power spectrum \cite{Carr:2016drx,Carr:2017jsz}.
+where $\alpha$ is a universal exponent which is related to the critical collapse of radiation, and $M_{\mathrm{f}}$ is a mass scale at the order of horizon mass at the collapse epoch \cite{Carr:2016hva}.
+This mass function is supposed to be closely associated with a monochromatic power spectrum of the density fluctuations.
+In this case, there is an exponential upper cut-off at a mass scale of $M_{\mathrm{f}}$, but no lower mass cut-off.
+Here and after, we dub it as CC mass function.
 Note that $\vth=\{\al, M\}$ and the free parameters are 
@@
 when estimating the merger rate (density) of PBHs.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[htbp!]
+	\centering
+	%	\scriptsize
+	\begin{tabular}{lll}
+		\hline\hline
+		\textbf{Parameter\quad} & \textbf{Description} & \textbf{Prior} \\
+		\hline
+		\multicolumn{3}{c}{Lognormal PBH mass function} \\[1pt]
+		$\Mc$ & Peak mass in $\Msun$. & $\mU(5, 50)$\\
+		$\sigma_\mathrm{c}$ & Mass width. & $\mU(0.1, 2)$\\
+		\hline
+		\multicolumn{3}{c}{Power-law PBH mass function} \\[1pt]
+		$\Mmin$ & Lower mass cut-off in $\Msun$. & $\mU(3, 10)$\\
+		$\al$ & power-law index & $\mU(1.05, 4)$\\
+		\hline
+		\multicolumn{3}{c}{Broken Power-law PBH mass function} \\[1pt]
+%		$\M_{*}$ & to be filled & $\mU(3, 15)$\\
+		$\al_1$ & power-law index & $\mU(0, 15)$\\
+		$\al_2$ & power-law index & $\mU(1, 3)$\\
+		\hline
+		\multicolumn{3}{c}{Critical collapse (CC) PBH mass function} \\[1pt]
+		$\Mf$ & Horizon mass scale in $\Msun$. & $\mU(1, 50)$\\
+		$\al$ & Universal exponent. & $\mU(0, 5)$\\
+		\hline
+	\end{tabular}
+	\label{tab:priors}
+	\caption{Parameters and their prior distributions used in the Bayesian parameter estimations.}
+\end{table}
+
+\begin{table}[tbp!]
+	\centering
+	\begin{tabular}{l|c|c|c|c}
+		\hline\hline
+		& lognormal & power-law & broken power-law & CC \\
+		\hline
+		$\mathrm{BF}^{\mathrm{2nd}}_{\mathrm{1st}}$ & $0.9$ & $0.4$ & $0.69$ & $1.2$ \\
+		$\mathrm{BF}_{\mathrm{PL}}$ & $166$ & $1$ & $2$ & $139$ \\
+		$R_2/R_1$ & $0.011$ & $0.0095$ & $0.0098$ & $0.033$ \\
+		$\fpbh$ & $0.0020$ & $0.0026$ & $0.0026$ & $0.0016$ \\
+		\hline
+	\end{tabular}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %%% references %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{./ref}
+\bibliography{ref}
 

### 2022-09-26 latex/paper.tex
update

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%% preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[
-%a4paper,       % letterpaper, a4paper, a5paper
-%10pt,              % 10pt, 11pt, 12pt
-reprint,           % journal's actual layout
-%preprint,          % 12pt, single-column
-superscriptaddress,% authors with affiliations via superscripts
-amsmath,           % add AMS-Latex features
-amssymb,           % add extra AMS symbols, including amsfonts
-aps,               % aps or aip
-prd,               % prl, pra, prb, prc, prd, pre, prstab
-%showpacs,          % make PACS codes appear
-notitlepage,       % control appearance of title page
-longbibliography,  % show  article titles in the bibliography
-floatfix,          % process floats as early as possible
-showkeys,          % option to make keywords appear
-%titlepage,         %
-%eqsecnum,          % number equations by section
-]{revtex4-1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%% load packages %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[twocolumn]{aastex631}
+%\documentclass[twocolumn,linenumbers]{aastex631}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% load packages %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage{ulem}
+\hypersetup{linkcolor=red,citecolor=blue,filecolor=cyan,urlcolor=magenta}
+\usepackage{amsmath}
+%\usepackage{subfigure}
+\usepackage{float}
 \usepackage{tensor}     % manipulate tensors
 \usepackage{graphicx}   % include figures
-\usepackage[
-colorlinks=true,        % color link
-citecolor=blue,         % cite color
-linkcolor=blue,         % link color
-urlcolor=blue           % url color
-]{hyperref}             % create hyperlinks
 \usepackage{bm}         % \bm{<text>} Bold math symbols
 \usepackage{xcolor}     % textcolor
-%\usepackage{dcolumn}    % Align table columns on decimal point
-%\usepackage{array}      % dcolumn depends on array
-\usepackage{tabulary}
 \usepackage{color}      % \textcolor{declared-color}{text}
@@
 \usepackage[section]{placeins} % figures processing
-%\renewcommand{\arraystretch}{1.25}
-%\arraycolsep 10pt
+\usepackage[utf8]{inputenc} % bibtex formatting
 
-% User-defined commands
-\renewcommand{\vec}[1]{\boldsymbol{#1}} % Uncomment for BOLD vectors.
-\def\Bs{{\overline{B}}_s}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Reintroduced the \received and \accepted commands from AASTeX v5.2
+%\received{}
+%\revised{}
+%\accepted{}
+%\published{}
+%% Command to document which AAS Journal the manuscript was submitted to.
+%% Adds "Submitted to " the arguement.
+%\submitjournal{ApJ}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author{Zu-Cheng~Chen}
+\author[0000-0001-7016-9934]{Zu-Cheng~Chen}
 \email{zucheng.chen@bnu.edu.cn}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author{Zhi-Qiang~You}
+\author[0000-0002-3309-415X]{Zhi-Qiang~You}
 \email{zhiqiang.you@bnu.edu.cn}
@@
 
-\pacs{???}
-
-\maketitle
+%\maketitle
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{\label{merger}Merger rate distribution of PBHs}
-In this section, we will briefly review the calculation of merger rate density
-by closely following \cite{Liu:2019rnx}.
+\section{\label{merger}Merger rate density distribution of PBH binaries}
+
+In this section, we will outline the calculation of merger rate density when taking into account the PBH merger history effect. We refer to \cite{Liu:2019rnx} for more details.
+
 We denote the probability distribution function (PDF) of PBH masses by $P(m)$
@@
 		\multicolumn{3}{c}{Broken Power-law PBH mass function} \\[1pt]
-%		$\M_{*}$ & to be filled & $\mU(3, 15)$\\
+		$M_*$ & to be filled & $\mU(3, 15)$\\
 		$\al_1$ & power-law index & $\mU(0, 15)$\\

### 2022-09-29 latex/paper.tex
update

@@
 
-We denote the probability distribution function (PDF) of PBH masses by $P(m)$
-which satisfies the following normalization condition
+The BBHs observed by LVK suggest that BHs should have a broad mass distribution, and hence we consider an extended mass function for PBHs.
+Here, we denote the probability distribution function (PDF) of PBH masses by $P(m)$ and demand the PDF to be normalized such that
 \e\label{norm}
@@
 \q 
-Consequently the abundance of PBHs in the mass interval $(m, m+\rd m)$ is given 
-by \cite{Chen:2018rzo}
+Assuming the fraction of PBHs in CDM is $\fpbh$, we can estimate the abundance of PBHs in the mass interval $(m, m+\rd m)$ as \citep{Chen:2018rzo}
 \e 
@@
 \q 
-where $\fpbh$ is the fraction of PBHs in CDM, and the coefficient $0.85$ is roughly the fraction of CDM in non-relativistic matter.
-Similar to \cite{Liu:2019rnx}, one may define a quantity $\mpbh$ as
+where the coefficient $0.85$ is roughly the fraction of CDM in non-relativistic matter including both CDM and baryons.
+Following \cite{Liu:2019rnx}, we may also define the ``averaged" PBH mass, $\mpbh$, as
 \e\label{mpbh}
@@
 \q 
-Furthermore, the present average number density of PBHs with mass $m$ in the 
-present total average number density of PBHs, $F(m)$, can be obtained by
-\cite{Liu:2019rnx}
+Then, we can obtain the average number density of PBHs with mass $m$ in the 
+total number density of PBHs, $F(m)$, by \citep{Liu:2019rnx}
 \e\label{Fm} 
@@
 
-With the above definitions at hand, one can go directly to estimate the merger rate densities of PBH binaries contributed from different merger processes.
+We can now proceed to estimate the merger rate densities of PBH binaries by considering the merger history effect.
+
 We assume that PBHs are randomly distributed in the early Universe when they decouple from the cosmic background evolution \cite{Nakamura:1997sm,Sasaki:2016jop,Ali-Haimoud:2017rtz}.

### 2022-09-29 code/merger_rate.jl
update

@@ -1,0 +1,152 @@
+using Trapz, MathLink, SpecialFunctions
+
+const m_min = 1e-1
+const m_max = 1e3
+
+# # using beta function from mathematica
+# beta0 = W"Beta"(W"z", W"a", W"b")
+# beta(z, a, b) = weval(beta0; z=z, a=a, b=b)
+
+
+# log-normal mass function 
+function mergerRateDensity1st0_log(mc, σc, log_fpbh, i, j)
+    fpbh = 10^log_fpbh
+    210084.52488130186 / (i^2 * j^2 * σc^2) * exp(-(743 * σc^4 + 1369 * log(i / mc)^2 + 1369 * log(j / mc)^2) / (2738 * σc^2)) * (i * j)^(3 / 37) * (i + j)^(36 / 37) * ((exp(σc^2 / 2) * fpbh) / mc)^(53 / 37) * mc^(53 / 37)
+end
+
+function mergerRateDensity2nd00_log(mc, σc, log_fpbh, i, j)
+    fpbh = 10^log_fpbh
+    tmp1 = 1009.5488113544313 * fpbh^(69 / 37) * i^(6 / 37) * (i + j)^(72 / 37) / j^(68 / 37) / σc^3
+    tmp2 = exp(-(-3318 * σc^4 + 1369 * log(j / mc)^2) / (2738 * σc^2))
+
+    int0(e) = exp(-(1369 * log(e / mc)^2 + 1369 * log((-e + i) / mc)^2) / (2738 * σc^2)) / (e^2 * (-e + i)^2)
+
+    vx = range(1e-1, i - 1e-1, length=20)
+    M = [int0(e) for e = vx]
+    # @show M
+    result = trapz((vx), M)
+
+    # int(e) = i * int0(i * e)
+    # function integrand(x, f)
+    #     f[1] = int(x[1])
+    # end
+    # result, err = cuhre(integrand, rtol=1e-1)
+    tmp1 * tmp2 * result[1]
+end
+
+function mergerRateDensity2nd0_log(mc, σc, log_fpbh, i, j)
+    0.5 * (mergerRateDensity2nd00_log(mc, σc, log_fpbh, i, j) + mergerRateDensity2nd00_log(mc, σc, log_fpbh, j, i))
+end
+
[…]

### 2022-10-26 latex/paper.tex
update

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% load packages %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{ulem}
-\hypersetup{linkcolor=red,citecolor=blue,filecolor=cyan,urlcolor=magenta}
+%\usepackage{ulem}
+%\hypersetup{linkcolor=red,citecolor=blue,filecolor=cyan,urlcolor=magenta}
 \usepackage{amsmath}
 %\usepackage{subfigure}
-\usepackage{float}
-\usepackage{tensor}     % manipulate tensors
-\usepackage{graphicx}   % include figures
-\usepackage{bm}         % \bm{<text>} Bold math symbols
-\usepackage{xcolor}     % textcolor
-\usepackage{color}      % \textcolor{declared-color}{text}
+%\usepackage{float}
+%\usepackage{tensor}     % manipulate tensors
+%\usepackage{graphicx}   % include figures
+%\usepackage{bm}         % \bm{<text>} Bold math symbols
+%\usepackage{xcolor}     % textcolor
+%\usepackage{color}      % \textcolor{declared-color}{text}
 %\usepackage{longtable}  % large table\
 %\usepackage{fontspec} % accented characters for .bib file using XeLaTex
-\usepackage[section]{placeins} % figures processing
-\usepackage[utf8]{inputenc} % bibtex formatting
+%\usepackage[section]{placeins} % figures processing
+%\usepackage[utf8]{inputenc} % bibtex formatting
 
@@
 \def\n{\end{eqnarray}}
+\def\permille{\ensuremath{{}^\text{o}\mkern-5mu/\mkern-3mu_\text{oo}}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
-\title{The merger history of primordial-black-hole binaries inferred from GWTC-3}
+\title{Constrain the Merger History of Primordial-Black-Hole Binaries from GWTC-3}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author[0000-0001-7016-9934]{Zu-Cheng~Chen}
-\email{zucheng.chen@bnu.edu.cn}
+\author[0000-0002-0297-9633]{Lang~Liu}
+\email{liulang@bnu.edu.cn}
 \affiliation{Department of Astronomy, Beijing Normal University, Beijing 100875, China}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author{You~Wu}
+\author[0000-0002-9610-2284]{You~Wu}
 \email{youwuphy@gmail.com}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author{Lang~Liu}
-\email{Corresponding author: liulang@bnu.edu.cn}
+\author[0000-0001-7016-9934]{Zu-Cheng~Chen}
+\email{Corresponding author: zucheng.chen@bnu.edu.cn}
 \affiliation{Department of Astronomy, Beijing Normal University, Beijing 100875, China}
 \affiliation{Advanced Institute of Natural Sciences, Beijing Normal University, Zhuhai 519087, China}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-In this paper, we will use the publicly available GW data from \lvc\ O1 and O2 
-observations to estimate the merger rate distribution of PBH binaries with a
-general mass function assuming all of \lvc\ BBHs are of primordial origin.
-We find that the merger history effect makes no significant contribution to
-the merger rate of PBHs and can be safely ignored.
-The rest of this paper is organized as follows.
-In \Sec{merger}, we review the calculation of merger rate distribution 
-accounting for the merger history effect.
-In \Sec{method}, we elaborate the data analysis method used to infer the
-PBH populations from \lvc\ data.
-In \Sec{result}, we present the results for PBHs with a power-law and 
-a log-normal mass function respectively.
-Finally, we summarize and discuss our results in \Sec{conclusion}.
+In this paper, we will use the LVK recent released GWTC-3 data to constrain the effect of merger history on the merger rate of PBH binaries assuming all of LVK BBHs are of primordial origin.
+We organize the rest paper as follows.
+In \Sec{merger}, we give a brief review on calculation of merger rate of PBH binaries by accounting for the merger history effect.
+In \Sec{method}, we describe the hierarchical Bayesian framework used to infer the PBH population parameters from GW data.
+In \Sec{result}, we consider four commonly used PBH mass functions and present the results.
+Finally, we give conclusions in \Sec{conclusion}.
 
@@
 
-The BBHs observed by LVK suggest that BHs should have a broad mass distribution, and hence we consider an extended mass function for PBHs.
-Here, we denote the probability distribution function (PDF) of PBH masses by $P(m)$ and demand the PDF to be normalized such that
+The BBHs observed by LVK suggest that BHs should have a broad mass distribution, so we consider an extended mass function for PBHs.
+Here, we demand the probability distribution function of PBH mass, $P(m)$, be normalized such that
 \e\label{norm}
@@
 \q 
-where the coefficient $0.85$ is roughly the fraction of CDM in non-relativistic matter including both CDM and baryons.
-Following \cite{Liu:2019rnx}, we may also define the ``averaged" PBH mass, $\mpbh$, as
+where the coefficient $0.85$ is roughly the fraction of CDM in non-relativistic matter including both CDM and baryons. Following \cite{Liu:2019rnx}, we may define an average PBH mass, $\mpbh$, as
 \e\label{mpbh}
@@
 We can now proceed to estimate the merger rate densities of PBH binaries by considering the merger history effect.
+We assume that PBHs are randomly distributed in the early Universe when they decouple from the cosmic background evolution \citep{Nakamura:1997sm,Sasaki:2016jop,Ali-Haimoud:2017rtz}.
+Two nearest PBHs would attract each other because of the gravitational interactions.
+These two PBHs would obtain the angular momentum from the torque of other PBHs and form a PBH binary.
+The binary would emit gravitational radiations and eventually merge.
 
-We assume that PBHs are randomly distributed in the early Universe when they decouple from the cosmic background evolution \cite{Nakamura:1997sm,Sasaki:2016jop,Ali-Haimoud:2017rtz}.
-Due to gravitational interactions, two nearest PBHs would attract each other and form a bound system if they get the angular momentum from the torque of the third closest PBH.
-Because of gravitational radiations, PBH binaries would eventually merge and may be detected by \lvc.
-Let us consider the first-merger process now.
-Assuming PBHs posses a random distribution in the early Universe, the differential distribution, for three PBHs with masses $(m_i, m_i+dm_i)$, $(m_j, m_j+dm_j)$ and  $(m_l, m_l+dm_l)$, is given by \cite{Liu:2019rnx}
-\e\label{dP1}
-\begin{split} 
-    dP_1 =& 16\pi^2 n_T^2 x^2 y^2 F(m_i) F(m_j) F(m_l) \\
-            &\times e^{-4\pi y^3 n_T/3} \rd m_i \rd m_j \rd m_l \rd x \rd y \Theta(y-x),
-\end{split}
+We do not intend to give a detailed derivation, but quote the results from \cite{Liu:2019rnx} here.
+The merger rate density from first-merger process, $\cR_1(t, m_i, m_j)$, is given by \citep{Liu:2019rnx}
+\e 
+\cR_1(t, m_i, m_j) = \int \hat{\cR}_1 \rd m_l,
 \q 
-where $\Theta$ is the Heaviside step function, and $x$ is the comoving distance between two closest PBHs with masses $m_i$ and $m_j$.
-Note that these two nearest PBHs will form a binary due to the torque of third PBH with mass $m_l$.
-In \Eq{dP1}, $y$ is the comoving distance from the binary to the third PBH, and $n_T$ is the average number density of PBHs defined by
-\e 
-    n_T = \frac{\fpbh \rho_{\mathrm{CDM}}}{\mpbh},
-\q  
-where $\rho_{\mathrm{CDM}}$ is the energy density of CDM.
-Notice that the $e$-factor in \Eq{dP1} guarantees that there are no other PBHs within the distance $y$.
-It is now straightforward to obtain the fraction of PBHs that have merged before cosmic time $t$ \cite{Liu:2019rnx}
-\e 
-    G_1(t) = \int \rd x \rd y \rd m_l \frac{\rd P_1}{\rd x \rd y \rd m_i \rd m_j \rd m_l} \Theta(t-\tau),
-\q 
-where $\tau$ is the cosmic time at which the PBH binary with masses of $m_i$ and $m_j$ merges.
-Therefore the merger rate density of first-merger process, $\cR_1(t, m_i, m_j)$, is given by \cite{Liu:2019rnx}
-\e 
-\cR_1(t, m_i, m_j) = \hf n_T \frac{\rd G_1(t, m_i, m_j)}{\rd t}
-            = \int \hat{\cR}_1 \rd m_l,
-\q 
-where the factor $1/2$ accounts for the symmetry of $m_i$ and $m_j$, and
+where
 \e 
@@
     &\hat{\cR}_1(t, m_i, m_j, m_l)
-    =1.32 \times 10^6 \times \(\frac{t}{t_0}\)^{-\frac{34}{37}}\(\frac{\fpbh}{\mpbh}\)^\frac{53}{37} \\ 
+    \equiv 1.32 \times 10^6 \times \(\frac{t}{t_0}\)^{-\frac{34}{37}}\(\frac{\fpbh}{\mpbh}\)^\frac{53}{37} \\ 
     &\times m_l^{-\frac{21}{37}} (m_i m_j)^\frac{3}{37} (m_i + m_j)^\frac{36}{37} F(m_i) F(m_j) F(m_l).     
@@
 \q
-After the first-merger process, the mass of the remnant BH will approximately be $m_i + m_j$ if the two initial PBHs have masses of $m_i$ and $m_j$.
-A second-merger process would happen if this remnant BH and the nearest PBH with mass $m_k$ form a new binary by the torque from another PBH with mass $m_l$.
-Similarly, the merger rate density of second-merger process, $\cR_2(t, m_i, m_j)$, is given by \cite{Liu:2019rnx}
+Similarly, the merger rate density from second-merger process, $\cR_2(t, m_i, m_j)$, is given by \citep{Liu:2019rnx}
 \e 
@@
 \q
-Following the same spirit, in principle one can derive the merger rate density $\cR_n(t, m_i, m_j)$ contributed from the $n$-th merger process.
-Therefore the total merger rate density, $\cR(t, m_i, m_j)$, 
-of PBHs at cosmic time $t$ with masses $m_i$ and $m_j$ is
+We only consider the effect of merger history up to second-merger process.
+Therefore the total merger rate density, $\cR(t, m_i, m_j)$, of PBH binaries at cosmic time $t$ with masses $m_i$ and $m_j$ is
 \e\label{cR}
-    \cR(t, m_i, m_j) = \sum_{n=1} \cR_n(t, m_i, m_j),
+    \cR(t, m_i, m_j) =  \sum_{n=1,2} \cR_n(t, m_i, m_j),
 \q 
-and the total merger rate can be directly obtained by
+and the total merger rate is
 \e\label{Rt}
-    R(t) = \int \cR(t, m_i, m_j) \rd m_i \rd m_j = \sum_{n=1} R_n(t),
+    R(t) = \int \cR(t, m_i, m_j) \rd m_i \rd m_j = \sum_{n=1,2} R_n(t),
 \q 
@@
 \q 
-As demonstrated in \cite{Liu:2019rnx}, $\cR_{n+1}(t, m_i, m_j)$ is not 
-necessarily be smaller than $\cR_n(t, m_i, m_j)$ (see Fig.~7 and Fig.~8 in 
-\cite{Liu:2019rnx}).
-However, $R_{n+1}(t)$ should be smaller than $R_n(t)$ as expected
-\cite{Liu:2019rnx}.
-Here, we only consider the merger history up to second-merger process.
+All the above mentioned merger rate (density) is measured at source frame.
+We should emphasize that although $R_2(t)$ should be smaller than $R_1(t)$ as expected, $\cR_2(t, m_i, m_j)$ is not necessarily be smaller than $\cR_1(t, m_i, m_j)$ \citep{Liu:2019rnx}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{\label{method}Inference on PBH mass distribution from GW data}
-Given a general mass function of PBHs $P(m|\vth)$ which satisfy the normalization
-condition of \Eq{norm}, the time (or redshift) dependent merger rate can be
-obtained by \Eq{Rt}, namely
-\e\label{Rt2}
-R(t|\vth) = \int \mR(t, \vla|\vth)\ \rd \vla,
+\section{\label{method}Hierarchical Bayesian Inference}
+To infer the population parameters, we adopt a hierarchical Bayesian approach by marginalizing over the uncertainty in the estimate of individual event parameters.
+In this section, we describe the hierarchical Bayesian inference used in the parameter estimations.
+The merger rate density \eqref{cR} is measured in source frame, and we need to convert it into the detector frame as
+\e\label{Rpop}
+\mR_{\mathrm{pop}}(\theta|\Ld) = \frac{1}{1+z} \frac{dV_\mathrm{c}}{dz} \mR(\theta|\Ld),
 \q
-where $\vla \equiv \{m_1, m_2\}$, and $\vth$ are the parameters that 
-characterize the mass function and will be inferred from GW data. 
-For instance, $\vth=\{\alpha, M\}$ for the power-law PDF (see \Eq{power}) 
-and $\vth=\{m_c, \s\}$ for the log-normal PDF (see \Eq{log}).
-The local merger rate density distribution then reads \cite{Chen:2018rzo}
-\e\label{Rt0} 
-\mR(t_0, \vla|\vth) = R_0\, p(\vla|\vth),
+where $z$ is the cosmological redshift, $\theta\equiv\{z, m_1, m_2\}$, $\Ld$ is a collection of $\fpbh$ and the parameters from mass function $P(m)$, and $dV_\mathrm{c}/dz$ is the differential comoving volume.
+The factor $1/(1 + z)$ converts time increments from the source frame to the detector frame.
+In this work, we take the cosmological parameters from Planck 2018 \citep{Planck:2018vyg}.
+
+Given the data, $\textbf{d} = \{d_1, d_2, \cdots, d_{N_{\mathrm{obs}}}\}$, of $N_{\mathrm{obs}}$ BBH merger events, we model the total number of events as an inhomogeneous Poisson process, yielding the likelihood \citep{Loredo:2004nn,Thrane:2018qnx,Mandel:2018mve}
+\begin{equation}\label{L1}
+	\mathcal{L}(\textbf{d}|\Ld) \propto N_{\mathrm{exp}}^{N_{\mathrm{obs}}} e^{-N_{\mathrm{exp}}} \prod_{i=1}^{N_{\mathrm{obs}}} \frac{\int \mathcal{L} (d_{i}| \theta)\, \cR_{\mathrm{pop}}(\theta|\Ld) d \theta}{\xi(\Ld)},
+\end{equation}
+where $N_{\exp}\equiv N_{\exp}(\Ld)$ is the expected number of detections over the timespan of observation, and $\mathcal{L} (d_{i}|\theta)$ is the individual event likelihood for the $i$th GW event that can be derived from the individual event's posterior by reweighing with the prior on $\theta$.
+Here, $\xi(\Ld)$ quantifies selection biases for a population with parameters $\Ld$ and is defined by
+\e\label{xi}
+\xi(\Ld) = \int P_{\mathrm{det}}(\theta)\, \cR_{\mathrm{pop}}(\theta|\Ld)\, \mathrm{d} \theta,
 \q
-where $R_0 \equiv R(t_0|\vth)$ is the local merger rate, and $p(m_1,m_2|\vth)$ 
-is the population distribution of BBH mergers.
-Note that \Eq{Rt0} guarantees $p(m_1,m_2|\vth)$ is normalized, namely
-\e 
-    \int p(\vla|\vth)\, \rd \vla = 1.
-\q
+where $P_{\text{det}}(\theta)$ is the detection probability that depends on the source parameters $\theta$.
+In practice, we use the simulated injections \citep{ligo_scientific_collaboration_and_virgo_2021_5546676} to estimate $\xi(\Ld)$, and \Eq{xi} can be approximated by a Monte Carlo integral over found injections \citep{LIGOScientific:2021psn}
+\begin{equation}
+	\xi(\Ld) \approx \frac{1}{N_{\mathrm{inj}}} \sum_{j=1}^{N_{\text {found }}} \frac{\cR_{\mathrm{pop}}(\theta_{j} | \Ld)}{p_{\mathrm{draw}}(\theta_j)},
+\end{equation}
+where $N_{\text{inj}}$ is the total number of injections, $N_{\text{found}}$ is the number of successfully detected injections, and $p_{\mathrm{draw}}$ is the probability density function from which the injections are drawn.
+Using the posterior samples from each individual event, the hyper-likelihood \eqref{L1} can be estimated as
+\begin{equation}\label{L2}
+	\mathcal{L}(\textbf{d}|\Ld) \propto N_{\mathrm{exp}}^{N_{\mathrm{obs}}} e^{-N_{\mathrm{exp}}} \prod_{i=1}^{N_{\mathrm{obs}}} \frac{1}{\xi(\Ld)} \left\langle \frac{\cR_{\mathrm{pop}}(\theta|\Ld)}{d_L^2(z)} \right\rangle,
+\end{equation}
+where $\langle\cdots\rangle$ denotes the weighted average over posterior samples of $\theta$.
+The denominator $d_L^2(z)$ is the standard priors used in the LVK analysis of individual events where $d_L$ is the luminosity distance.
 
-Given the GW data, $\vd = (d_1, \dots, d_N)$, which consist of $N$ BBH merger
-events, we aim to extract the population parameters $\{\vth, R_0\}$ from $\vd$.
-In order to do that, it is necessary to perform the hierarchical Bayesian inference
-on the BBHs' mass distribution 
-\cite{Abbott:2016nhf,Abbott:2016drs,TheLIGOScientific:2016pea,
-    Wysocki:2018mpo,Fishbach:2018edt,Mandel:2018mve,Thrane:2018qnx}.
-In this work, we will use the data of ten BBHs
-\cite{TheLIGOScientific:2016pea,LIGOScientific:2018mvr} 
-reported by \lvc\ O1 and O2 observations, and hence $N=10$. 
-The posterior samples of these BBHs are publicly available from \footnote{\url{https://www.gw-openscience.org/}}. 
-Because the standard priors on masses for each event in \lvc\ analysis are 
-taken to be uniform \cite{TheLIGOScientific:2016pea,LIGOScientific:2018mvr},
-the likelihood of an individual event $p(d_i|\vla)$ is
-proportional to the posterior of that event $p(\vla|d_i)$.
-The total likelihood for an inhomogeneous Poisson process can be evaluated as
-\cite{Wysocki:2018mpo,Fishbach:2018edt,Mandel:2018mve,Thrane:2018qnx}
-\e\label{likelihood}
-p(\vd|\vth, R_0) \propto R_0^{N} e^{-R_0\, \beta(\vth)} \prod_i^N 
-\int \rd\vla\ p(d_i|\vla)\ p(\vla|\vth),
-\q 
-where $\beta(\vth)$ is defined as
-\e 
-\beta(\vth) \equiv \int \rd\vla\ VT(\vla)\ p(\vla|\vth),
-\q 
-in which $VT(\vla)$ is the sensitive spacetime volume \cite{Abbott:2016nhf,Abbott:2016drs} of LIGO.
-We adopt the semi-analytical approximation from 
-\cite{Abbott:2016nhf,Abbott:2016drs} to estimate $VT$, 
-where we use the ``IMRPhenomPv2" waveform to simulate the BBH templates
-and neglect the effect of spins for BHs.
-Furthermore, the threshold signal-to-noise ratio (SNR) of detection for a 
-single-detector is set to $8$,
-which corresponds to a network SNR threshold of around $12$.
-
-Assuming the prior distributions $p(\vth, R_0)$ are uniform for $\vth$ parameters
-and log-uniform for local merger rate $R_0$
-\cite{Abbott:2016nhf,Abbott:2017vtc}, namely
-\e 
-p(\vth, R_0) \propto \frac{1}{R_0},
-\q 
-the posterior probability distribution $p(\vth, R_0|\vd)$ 
-can be directly calculated by
-\e\label{post} 
-p(\vth, R_0|\vd) \propto p(\vd |\vth, R_0)\ p(\vth, R_0).
-\q
-The marginalized posterior $p(\vth|\vd)$ can then be readily obtained by
-integrating over $R_0$ in \Eq{post}, namely
-\e\label{post_vth} 
-p(\vth|\vd) \propto \[\beta(\vth)\]^{-N} 
-\prod_i^N \int \rd\vla\ p(d_i|\vla)\ p(\vla|\vth).
-\q 
-This marginalized posterior has been widely used in previous 
-population inferences 
-\cite{Abbott:2016nhf,Abbott:2017vtc,TheLIGOScientific:2016pea,
-    Abbott:2016drs,Fishbach:2017zga,Chen:2018rzo}.
-In the following section, we will utilize the posterior \eqref{post} to infer
-the population parameters $\{\vth, R_0\}$ by considering two concrete mass
-distributions, a power-law PDF and a log-normal PDF, respectively.
+In this work, we incorporate the PBH population distribution \eqref{cR} into the \texttt{ICAROGW} \citep{Mastrogiovanni:2021wsd} package to estimate the likelihood function \eqref{L2}, and use \texttt{dynesty} \citep{Speagle:2019ivv} sampler called from \texttt{Bilby} \citep{Ashton:2018jfp,Romero-Shaw:2020owr} to sample over the parameter space.
+We use the GW events from GWTC-3 by discarding events with false alarm rate larger than 1 yr$^{-1}$ and events with the secondary component mass smaller than $3\Msun$ to avoid contamination from putative events involving neutron stars following \cite{DeLuca:2021wjr}.
+A total of $69$ GW events from GWTC-3 meet this criteria and the posterior samples of these BBHs are publicly available from \cite{ligo_scientific_collaboration_and_virgo_2021_5655785}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Log-normal mass function}
-We now consider a log-normal mass function of PBHs as \cite{Dolgov:1992pu}
-\e\label{log}
-P(m) = \frac{1}{\sqrt{2\pi} \s m} \exp \(-\frac{\ln^2\(m/m_c\)}{2\s^2}\),
-\q
-where $m_c$ presents the peak mass of $m P(m)$, and $\s$ denotes the width of 
-the mass spectrum.
-The log-normal mass function is a good approximation to a large class of extended mass distributions if PBHs are formed from smooth symmetric peaks in the inflationary power spectrum \cite{Carr:2017jsz}, as demonstrated in \cite{Green:2016xgy,Kannike:2017bxn}.
-Note that $\vth=\{m_c, \s\}$, and the free parameters are 
-$\{\vth, R_0\} = \{m_c, \s, R_0\}$ in this case. 
-Using \Eq{mpbh} and \Eq{Fm}, it is easily to get
-\e
-\mpbh = m_c \exp \(-\frac{\s^2}{2}\),
-\q
-\e 
-F(m) = \frac{m_c}{\sqrt{2\pi} \s m^2} \exp \(-\frac{\s^2}{2}-\frac{\ln^2\(m/m_c\)}{2\s^2}\).
-\q
-
-Using data of $10$ BBHs observed by \lvc\ O1 and O2 observations and performing
-the hierarchical Bayesian inference, we obtain $m_c =8.9^{+7.8}_{-7.3} \Msun$,
-$\s = 0.91^{+0.50}_{-0.42}$, and $R_0 = 55^{+42}_{-27} \gpcyr$.
-It is then easy to infer the abundance of PBHs in CDM to be 
-$\fpbh = 2.6^{+6.8}_{-1.4} \times 10^{-3}$ from the posterior distribution of 
-local merger rate $R_0$.
-The results of local merger rate and abundance of PBHs are consistent with
-the previous estimations, confirming that the main components of CDM should
-not be made of stellar mass PBHs.
-The posteriors of parameters $\{\vth, R_0\} = \{m_c, \s, R_0\}$ are shown 
-in \Fig{posterior-log}.
-\begin{figure}[htbp!]
-	\centering
-	\includegraphics[width=0.5\textwidth]{post-log.pdf}
-	\caption{\label{posterior-log}
-		The marginalized one- and two-dimensional posterior distributions for 
-		parameters $\{\vth, R_0\} = \{m_c, \s, R_0\}$ in the log-normal mass function of PBHs, by using $10$ BBH events from \lvc\ O1 and O2 observing runs.
-		The contours are at the $68\%$ and $95\%$ credible levels, respectively. 
-	}
-\end{figure}
-
-\begin{figure}[htbp!]
-	\centering
-	\includegraphics[width=0.5\textwidth]{ratio-log.pdf}
-	\caption{\label{ratio-log}
-		The ratio of merger rate density from second-merger history
-		to that from first-merger history,
-		$\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$. Note that the parameters $\{m_c, \sigma\}$ in \Eq{log} are fixed to their best-fit values.
-	}
-\end{figure}
-
-\Fig{ratio-log} shows the ratio of merger rate density from second-merger history
-to the one from first-merger history, namely 
-$\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing $\{\vth, R_0\}$ to their best-fit values.
-The correction to total merger rate density from 
-second-merger history is larger as component masses are heavier.
-However, the ratio of merger rate from 
-second-merger history to the one from first-merger history is negligible, namely
-$R_2(t_0)/R_1(t_0) = 3.0\%$.
-This is because the major contribution to the merger rate comes from the binaries with masses less than $50\Msun$.
-Therefore the merger history effect can be safely ignored
-when estimating the merger rate of PBHs.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Power-law mass function}
-We now consider a power-law mass function of PBHs as \cite{Carr:1975qj}
-\e\label{power} 
-    P(m) = \frac{\al-1}{M} \(\frac{m}{M}\)^{-\al},
-\q
-where $m>M$, and $\al>1$ is the power-law index.
-The power-law form is a commonly used mass function as it naturally arises if PBHs are formed from primordial energy density fluctuations due to a scale-invariant primordial power spectrum \cite{Carr:2016drx,Carr:2017jsz}.
-Note that $\vth=\{\al, M\}$ and the free parameters are 
-$\{\vth, R_0\} = \{\al, M, R_0\}$ in this case. 
-Using \Eq{mpbh} and \Eq{Fm}, it is easily to get
-\e
-    \mpbh = M \frac{\al}{\al-1},
-\q
-\e 
-    F(m) = \frac{\al}{m} \(\frac{m}{M}\)^{-\al}.
-\q
-
-Using data of $10$ BBHs observed by \lvc\ O1 and O2 observations and performing
-the hierarchical Bayesian inference, we obtain $\al = 2.41^{+1.00}_{-0.87}$,
-$M = 7.4^{+1.4}_{-3.3} \Msun$, and $R_0 = 48^{+37}_{-24} \gpcyr$.
-It is then easy to infer the abundance of PBHs in CDM to be 
-$\fpbh = 2.8^{+1.8}_{-1.2} \times 10^{-3}$ from the posterior distribution of local merger rate $R_0$.
-The results of local merger rate and abundance of PBHs are consistent with
-the previous estimations, confirming that the main components of CDM should
-not be made of stellar mass PBHs.
-The posteriors of parameters $\{\vth, R_0\} = \{\al, M, R_0\}$ are shown 
-in \Fig{posterior-power}.
-
-\begin{figure}[htbp!]
+\begin{table}[tbp!]
 	\centering
-	\includegraphics[width=0.5\textwidth]{post-power.pdf}
-	\caption{\label{posterior-power}
-		The marginalized one- and two-dimensional posterior distributions for 
-    parameters $\{\vth, R_0\} = \{\al, M, R_0\}$ in the power-law mass function 
-    of PBHs, by using $10$ BBH events from \lvc\ O1 and O2 observing runs.
-    The contours are at the $68\%$ and $95\%$ credible levels, respectively. 
-	}
-\end{figure}
-
-\begin{figure}[htbp!]
-	\centering
-	\includegraphics[width=0.5\textwidth]{ratio-power.pdf}
-	\caption{\label{ratio-power}
-		The ratio of merger rate density from second-merger history
-        to that from first-merger history,
-        $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$. Note that the parameters $\{\al, M\}$ in \Eq{power} are fixed to their best-fit values.
-	}
-\end{figure}
-
-\Fig{ratio-power} shows the ratio of merger rate density from second-merger history
-to the one from first-merger history, namely 
-$\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing $\{\vth, R_0\}$ to their best-fit values.
-It is clearly that the correction of total merger rate density from 
-second-merger history is less than $10\%$.
-It is then readily to calculate the ratio of merger rate from 
-second-merger history to the one from first-merger history, 
-$R_2(t_0)/R_1(t_0) = 0.5\%$.
-We therefore conclude that the merger history effect can be safely ignored
-when estimating the merger rate (density) of PBHs.
-
-\subsection{Broken Power-law mass function}
-We now consider a power-law mass function of PBHs as \cite{Carr:1975qj}
-\begin{equation}
-	P(m)= \left(\frac{m_*}{\alpha_1+1}-\frac{m_*}{\alpha_2-1}\right)^{-1} \begin{cases}\left(m / m_*\right)^{\alpha_1}, & m<m_* \\ \left(m / m_*\right)^{-\alpha_2}, & m>m_*\end{cases}
-\end{equation}
-where $m>M$, and $\al>1$ is the power-law index.
-The power-law form is a commonly used mass function as it naturally arises if PBHs are formed from primordial energy density fluctuations due to a scale-invariant primordial power spectrum \cite{Carr:2016drx,Carr:2017jsz}.
-Note that $\vth=\{\al, M\}$ and the free parameters are 
-$\{\vth, R_0\} = \{\al, M, R_0\}$ in this case. 
-Using \Eq{mpbh} and \Eq{Fm}, it is easily to get
-\e
-\mpbh = M \frac{\al}{\al-1},
-\q
-\e 
-F(m) = \frac{\al}{m} \(\frac{m}{M}\)^{-\al}.
-\q
-
-Using data of $10$ BBHs observed by \lvc\ O1 and O2 observations and performing
-the hierarchical Bayesian inference, we obtain $\al = 2.41^{+1.00}_{-0.87}$,
-$M = 7.4^{+1.4}_{-3.3} \Msun$, and $R_0 = 48^{+37}_{-24} \gpcyr$.
-It is then easy to infer the abundance of PBHs in CDM to be 
-$\fpbh = 2.8^{+1.8}_{-1.2} \times 10^{-3}$ from the posterior distribution of local merger rate $R_0$.
-The results of local merger rate and abundance of PBHs are consistent with
-the previous estimations, confirming that the main components of CDM should
-not be made of stellar mass PBHs.
-The posteriors of parameters $\{\vth, R_0\} = \{\al, M, R_0\}$ are shown 
-in \Fig{posterior-power}.
-
-\begin{figure}[htbp!]
-	\centering
-	\includegraphics[width=0.5\textwidth]{post-bpower.pdf}
-	\caption{\label{posterior-bpower}
-		The marginalized one- and two-dimensional posterior distributions for 
-		parameters $\{\vth, R_0\} = \{\al, M, R_0\}$ in the power-law mass function 
-		of PBHs, by using $10$ BBH events from \lvc\ O1 and O2 observing runs.
-		The contours are at the $68\%$ and $95\%$ credible levels, respectively. 
-	}
-\end{figure}
-
-\begin{figure}[htbp!]
-	\centering
-	\includegraphics[width=0.5\textwidth]{ratio-bpower.pdf}
-	\caption{\label{ratio-bpower}
-		The ratio of merger rate density from second-merger history
-		to that from first-merger history,
-		$\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$. Note that the parameters $\{\al, M\}$ in \Eq{power} are fixed to their best-fit values.
-	}
-\end{figure}
-
-\Fig{ratio-power} shows the ratio of merger rate density from second-merger history
-to the one from first-merger history, namely 
-$\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing $\{\vth, R_0\}$ to their best-fit values.
-It is clearly that the correction of total merger rate density from 
-second-merger history is less than $10\%$.
-It is then readily to calculate the ratio of merger rate from 
-second-merger history to the one from first-merger history, 
-$R_2(t_0)/R_1(t_0) = 0.5\%$.
-We therefore conclude that the merger history effect can be safely ignored
-when estimating the merger rate (density) of PBHs.
-
-\subsection{CC mass function}
-We now consider the critical collapse mass function taking the form of \cite{Niemeyer:1997mt,Yokoyama:1998xd,Carr:2016hva,Gow:2020cou}
-\e
-P(m, \alpha, M_{\mathrm{f}})=\frac{\alpha^2\,  m^\alpha}{M_{\mathrm{f}}^{1+\alpha}\, \Gamma(1 / \alpha)} \exp \left(-(m/M_{\mathrm{f}})^{\alpha}\right),
-\q
-where $\alpha$ is a universal exponent which is related to the critical collapse of radiation, and $M_{\mathrm{f}}$ is a mass scale at the order of horizon mass at the collapse epoch \cite{Carr:2016hva}.
-This mass function is supposed to be closely associated with a monochromatic power spectrum of the density fluctuations.
-In this case, there is an exponential upper cut-off at a mass scale of $M_{\mathrm{f}}$, but no lower mass cut-off.
-Here and after, we dub it as CC mass function.
-Note that $\vth=\{\al, M\}$ and the free parameters are 
-$\{\vth, R_0\} = \{\al, M, R_0\}$ in this case. 
-Using \Eq{mpbh} and \Eq{Fm}, it is easily to get
-\e
-\mpbh = M \frac{\al}{\al-1},
-\q
-\e 
-F(m) = \frac{\al}{m} \(\frac{m}{M}\)^{-\al}.
-\q
-
-Using data of $10$ BBHs observed by \lvc\ O1 and O2 observations and performing
-the hierarchical Bayesian inference, we obtain $\al = 2.41^{+1.00}_{-0.87}$,
-$M = 7.4^{+1.4}_{-3.3} \Msun$, and $R_0 = 48^{+37}_{-24} \gpcyr$.
-It is then easy to infer the abundance of PBHs in CDM to be 
-$\fpbh = 2.8^{+1.8}_{-1.2} \times 10^{-3}$ from the posterior distribution of local merger rate $R_0$.
-The results of local merger rate and abundance of PBHs are consistent with
-the previous estimations, confirming that the main components of CDM should
-not be made of stellar mass PBHs.
-The posteriors of parameters $\{\vth, R_0\} = \{\al, M, R_0\}$ are shown 
-in \Fig{posterior-power}.
-
-\begin{figure}[htbp!]
-	\centering
-	\includegraphics[width=0.5\textwidth]{post-CC.pdf}
-	\caption{\label{post-CC}
-		The marginalized one- and two-dimensional posterior distributions for 
-		parameters $\{\vth, R_0\} = \{\al, M, R_0\}$ in the power-law mass function 
-		of PBHs, by using $10$ BBH events from \lvc\ O1 and O2 observing runs.
-		The contours are at the $68\%$ and $95\%$ credible levels, respectively. 
-	}
-\end{figure}
-
-\begin{figure}[htbp!]
-	\centering
-	\includegraphics[width=0.5\textwidth]{ratio-CC.pdf}
-	\caption{\label{ratio-CC}
-		The ratio of merger rate density from second-merger history
-		to that from first-merger history,
-		$\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$. Note that the parameters $\{\al, M\}$ in \Eq{power} are fixed to their best-fit values.
-	}
-\end{figure}
-
-\Fig{ratio-power} shows the ratio of merger rate density from second-merger history
-to the one from first-merger history, namely 
-$\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing $\{\vth, R_0\}$ to their best-fit values.
-It is clearly that the correction of total merger rate density from 
-second-merger history is less than $10\%$.
-It is then readily to calculate the ratio of merger rate from 
-second-merger history to the one from first-merger history, 
-$R_2(t_0)/R_1(t_0) = 0.5\%$.
-We therefore conclude that the merger history effect can be safely ignored
-when estimating the merger rate (density) of PBHs.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[htbp!]
-	\centering
-	%	\scriptsize
 	\begin{tabular}{lll}
@@
 		\hline
+		$\fpbh$ & Abundance of PBH in dark matter & log-$\mU(-4, 0)$\\
+		\hline
 		\multicolumn{3}{c}{Lognormal PBH mass function} \\[1pt]
-		$\Mc$ & Peak mass in $\Msun$. & $\mU(5, 50)$\\
-		$\sigma_\mathrm{c}$ & Mass width. & $\mU(0.1, 2)$\\
+		$\Mc$ & Central mass in $\Msun$. & $\mU(5, 50)$\\
+		$\sigma$ & Mass width. & $\mU(0.1, 2)$\\
 		\hline
@@
 		$\Mmin$ & Lower mass cut-off in $\Msun$. & $\mU(3, 10)$\\
-		$\al$ & power-law index & $\mU(1.05, 4)$\\
+		$\al$ & Power-law index. & $\mU(1.05, 4)$\\
 		\hline
 		\multicolumn{3}{c}{Broken Power-law PBH mass function} \\[1pt]
-		$M_*$ & to be filled & $\mU(3, 15)$\\
-		$\al_1$ & power-law index & $\mU(0, 15)$\\
-		$\al_2$ & power-law index & $\mU(1, 3)$\\
+		$M_*$ & Peak mass in $\Msun$. & $\mU(3, 15)$\\
+		$\al_1$ & First power-law index. & $\mU(0, 15)$\\
+		$\al_2$ & Second power-law index. & $\mU(1, 3)$\\
 		\hline
@@
 	\end{tabular}	
-	\label{tab:priors}
-	\caption{Parameters and their prior distributions used in the Bayesian parameter estimations.}
+	\caption{\label{table:priors}Parameters and their prior distributions used in the Bayesian parameter estimations.
+Here, $\mU$ and log-$\mU$ denote uniform and log-uniform distributions, respectively.}
 \end{table}
+Based on the hierarchical statistical framework, we do the parameter estimations for four different PBH mass functions that are commonly used in the literature.
+These mass functions are the log-normal, power-law, broken power-law, and critical collapse (CC) distributions, respectively.
+We summarize the parameters and their prior distributions in \Table{table:priors}.
+Below we show the results for each of the PBH mass function.
 
+\subsection{Log-normal mass function}
+We first consider a PBH mass function with the log-normal form \citep{Dolgov:1992pu} of
+\e\label{log}
+P(m) = \frac{1}{\sqrt{2\pi} \s m} \exp \(-\frac{\ln^2\(m/M_c\)}{2\s^2}\),
+\q
+where $M_c$ represents the central mass of $m P(m)$, and $\s$ characterizes the width of the mass spectrum.
+A huge class of extended mass distributions can be approximated by the log-normal mass function if PBHs are formed from a smooth symmetric peak in the inflationary power spectrum when the slow-roll approximation holds \citep{Green:2016xgy,Carr:2017jsz,Kannike:2017bxn}.
+The hyper-parameters are $\Ld = \{M_c, \s, \fpbh\}$ in this case. 
+We can then derive the averaged PBH mass and averaged number density from \Eq{mpbh} and \Eq{Fm} as
+\e
+\mpbh = M_c \exp \(-\frac{\s^2}{2}\),
+\q
+\e 
+F(m) = \frac{M_c}{\sqrt{2\pi} \s m^2} \exp \(-\frac{\s^2}{2}-\frac{\ln^2\(m/M_c\)}{2\s^2}\).
+\q
+
+\begin{figure}[tbp!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{post-log.pdf}
+	\caption{\label{posterior-log}The marginalized one- and two-dimensional posterior distributions for hyper-parameters $\{M_c, \s, \fpbh\}$ in the log-normal mass function inferred from GWTC-3.
+The blue color denotes the results from the first merger only, while the orange denotes the results from both the first and second mergers.
+The contours represent the $1\sigma$, $2\sigma$ and $3\sigma$ credible regions, respectively.}
+\end{figure}
+
+\begin{figure}[htbp!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{ratio-log.pdf}
+	\caption{\label{ratio-log}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the log-normal mass function.
+We have fixed the hyper-parameters $\{M_c, \s, \fpbh\}$ to their best-fit values.}
+\end{figure}
+
+Using $69$ BBHs from GWTC-3 and performing the hierarchical Bayesian inference, we obtain $M_c = 17.3^{+2.2}_{-2.0} \Msun$, $\s = 0.71^{+0.10}_{-0.08}$, and $\fpbh = 1.8^{+0.3}_{-0.3} \times 10^{-3}$.
+In this work, we present result with median value and 90\% equal-tailed credible intervals.
+The posteriors for the hyper-parameters $\Ld = \{M_c, \s, \fpbh\}$ are shown in \Fig{posterior-log}.
+Note that we get a larger value of $M_c$ than that inferred from GWTC-1 in \cite{Wu:2020drm} because GWTC-3 contains more heavier BHs than those from GWTC-1.
+From \Eq{Rt}, we also infer the local merger rate as $R(t_0) = 41^{+16}_{-12} \gpcyr$.
+The results of local merger rate and abundance of PBHs are consistent with the previous estimations \citep{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+
+In \Fig{ratio-log}, we show the ratio of merger rate density from second merger to the one from first merger, namely $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing the hyper-parameters $\{M_c, \s, \fpbh\}$ to their best-fit values.
+It can be seen that the second merger provides more contribution to the total merger rate density as component mass increases.
+Even though $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$ can reach as high as $\gtrsim 10\%$, the ratio of merger rate from second merger to that from first merger is $R_2(t_0)/R_1(t_0) = 1.0^{+0.2}_{-0.1}\%$ and is negligible.
+This is because the major contribution to the merger rate is from the masses less than $50\Msun$, and the correction is negligible in this mass range.
+Therefore the effect of merger history can be safely ignored when estimating the merger rate of PBH binaries.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Power-law mass function}
+We next consider a PBH mass function with the power-law form \citep{Carr:1975qj} of
+\e\label{power} 
+    P(m) = \frac{\al-1}{\Mmin} \(\frac{m}{\Mmin}\)^{-\al},
+\q
+where $\Mmin$ is the lower-mass cut-off such that $m>\Mmin$, and $\al>1$ is the power-law index. 
+The power-law mass function can typically result from a broad or flat power spectrum of the curvature perturbations \citep{DeLuca:2020ioi} during radiation dominated era \citep{Carr:2016drx,Carr:2017jsz}.
+The hyper-parameters are $\Ld = \{\Mmin, \al, \fpbh\}$ in this case. 
+We can then derive the averaged PBH mass and averaged number density from \Eq{mpbh} and \Eq{Fm} as
+\e
+    \mpbh = \Mmin \frac{\al}{\al-1},
+\q
+\e 
+    F(m) = \frac{\al}{m} \(\frac{m}{\Mmin}\)^{-\al}.
+\q
+
+Using $69$ BBHs from GWTC-3 and performing the hierarchical Bayesian inference, we obtain $\Mmin = 6.5^{+0.3}_{-0.8} \Msun$, $\al = 1.9^{+0.2}_{-0.2}$, and $\fpbh = 2.3^{+0.3}_{-0.3} \times 10^{-3}$.
+The posteriors for the hyper-parameters $\Ld = \{\Mmin, \al, \fpbh\}$ are shown in \Fig{posterior-power}.
+Note that we get a smaller value of $\al$ than that inferred from GWTC-1 in \cite{Wu:2020drm} because GWTC-3 contains more heavier BHs than those from GWTC-1.
+From \Eq{R0}, we also infer the local merger rate as $R_0 = 48^{+15}_{-12} \gpcyr$.
+The results of local merger rate and abundance of PBHs are consistent with the previous estimations \citep{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+
+\begin{figure}[tbp!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{post-power.pdf}
+	\caption{\label{posterior-power}The marginalized one- and two-dimensional posterior distributions for hyper-parameters $\{\Mmin, \al, \fpbh\}$ in the power-law mass function inferred from GWTC-3.
+The blue color denotes the results from the first merger only, while the orange denotes the results from both the first and second mergers.
+The contours represent the $1\sigma$, $2\sigma$ and $3\sigma$ credible regions, respectively.}
+\end{figure}
+
+\begin{figure}[htbp!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{ratio-power.pdf}
+	\caption{\label{ratio-power}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the power-law mass function.
+We have fixed the hyper-parameters $\{\Mmin, \al, \fpbh\}$ to their best-fit values.}
+\end{figure}
+
+In \Fig{ratio-power}, we show the ratio of merger rate density from second merger to the one from first merger, namely $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing the hyper-parameters $\{\Mmin, \al, \fpbh\}$ to their best-fit values.
+It can be seen that the second merger provides more contribution to the total merger rate density as component mass increases.
+Even though $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$ can reach as high as $\gtrsim 10\%$, the ratio of merger rate from second merger to that from first merger is $R_2(t_0)/R_1(t_0) = 0.9^{+0.1}_{-0.1}\%$ and is negligible.
+This is because the major contribution to the merger rate is from the masses less than $50\Msun$, and the correction is negligible in this mass range.
+Therefore the effect of merger history can be safely ignored when estimating the merger rate of PBH binaries.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Broken power-law mass function}
+We then consider a PBH mass function with the broken power-law form \citep{Deng:2021ezy} of
+\begin{equation}
+	P(m)= \left(\frac{m_*}{\alpha_1+1}-\frac{m_*}{\alpha_2-1}\right)^{-1} \begin{cases} (\frac{m}{m_*})^{\alpha_1}, & m<m_* \\ (\frac{m}{m_*})^{-\alpha_2}, & m>m_*\end{cases},
+\end{equation}
+where $m_*$ is the peak mass of $m P(m)$.
+Here $\al_1>0$ and $\al_2>1$ are two power-law indices.
+The broken power-law mass function is a generalization of the power-law form and can be achieved if PBHs are formed by vacuum bubbles that nucleate during inflation via quantum tunneling \citep{Deng:2021ezy}.
+The hyper-parameters are $\Ld = \{m_*, \al_1, \al_2, \fpbh\}$ in this case. 
+We can then derive the averaged PBH mass and averaged number density from \Eq{mpbh} and \Eq{Fm} as
+\e
+\mpbh = \frac{\al_1 \al_2}{\(\al_1 +1\)\(\al_2 -1\)} m_*,
+\q
+\e 
+F(m) = \frac{\al_1 \al_2}{\al_1 + \al_2} \begin{cases} (\frac{m}{m_*})^{\alpha_1}, & m<m_* \\ (\frac{m}{m_*})^{-\alpha_2}, & m>m_*\end{cases}.
+\q
+
+\begin{figure}[tbp!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{post-bpower.pdf}
+	\caption{\label{posterior-bpower}The marginalized one- and two-dimensional posterior distributions for hyper-parameters $\{m_*, \al_1, \al_2, \fpbh\}$ in the broken power-law mass function inferred from GWTC-3.
+The blue color denotes the results from the first merger only, while the orange denotes the results from both the first and second mergers.
+The contours represent the $1\sigma$, $2\sigma$ and $3\sigma$ credible regions, respectively.}
+\end{figure}
+
+\begin{figure}[tbp!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{ratio-bpower.pdf}
+	\caption{\label{ratio-bpower}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the broken power-law mass function.
+We have fixed the hyper-parameters $\{m_*, \al_1, \al_2, \fpbh\}$ to their best-fit values.}
+\end{figure}
+
+Using $69$ BBHs from GWTC-3 and performing the hierarchical Bayesian inference, we obtain $m_* = 8.6^{+2.1}_{-1.3} \Msun$, $\al_1 = 5.6^{+7.1}_{-3.8}$, $\al_2 = 2.0^{+0.2}_{-0.2}$, and $\fpbh = 2.2^{+0.3}_{-0.4} \times 10^{-3}$.
+The posteriors for the hyper-parameters $\Ld = \{m_*, \al_1, \al_2, \fpbh\}$ are shown in \Fig{posterior-bpower}.
+From \Eq{R0}, we also infer the local merger rate as $R_0 = 46^{+15}_{-11} \gpcyr$.
+The results of local merger rate and abundance of PBHs are consistent with the previous estimations \citep{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+Note that \cite{Deng:2021ezy} obtains quite different results for the broken power-law mass function using GWTC-2 data without accounting for the uncertainties in the measurement of $\vth$.
+\cite{Deng:2021ezy} also deals with the selection effect of the GW detectors in an improper way.
+We emphasize that our results are more robust in the sense that we have a comprehensive treatment of the selection effect and also the measurement uncertainties.
+Nevertheless, our results of the broken power-law mass function are fully consistent with the results of the power-law case as expected.
+
+In \Fig{ratio-bpower}, we show the ratio of merger rate density from second merger to the one from first merger, namely $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing the hyper-parameters $\{m_*, \al_1, \al_2, \fpbh\}$ to their best-fit values.
+It can be seen that the second merger provides more contribution to the total merger rate density as component mass increases.
+Even though $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$ can reach as high as $\gtrsim 10\%$, the ratio of merger rate from second merger to that from first merger is $R_2(t_0)/R_1(t_0) = 0.9^{+0.3}_{-0.1}\%$ and is negligible.
+This is because the major contribution to the merger rate is from the masses less than $50\Msun$, and the correction is negligible in this mass range.
+Therefore the effect of merger history can be safely ignored when estimating the merger rate of PBH binaries.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Critical collapse mass function}
+We last consider a PBH mass function with the critical collapse form \citep{Niemeyer:1997mt,Yokoyama:1998xd,Carr:2016hva,Gow:2020cou} of
+\e
+P(m)=\frac{\alpha^2\,  m^\alpha}{\Mf^{1+\alpha}\, \Gamma(1 / \alpha)} \exp \left(-(m/\Mf)^{\alpha}\right),
+\q
+where $\alpha$ is a universal exponent relating to the critical collapse of radiation, and $M_{\mathrm{f}}$ is the mass scale at the order of horizon mass at the collapse epoch \citep{Carr:2016hva}. 
+For this mass spectrum, there is no lower mass cut-off, but it is exponentially suppressed above the mass scale of $\Mf$.
+The critical collapse mass function is closely associated with a $\delta$-function power spectrum of the density fluctuations \citep{Niemeyer:1997mt,Yokoyama:1998xd,Carr:2016hva,Gow:2020cou}. 
+The hyper-parameters are $\Ld = \{\Mf, \al, \fpbh\}$ in this case. 
+We can then derive the averaged PBH mass and averaged number density from \Eq{mpbh} and \Eq{Fm} as
+\e
+\mpbh = \frac{\Mf \Gamma(1 / \alpha)}{\alpha},
+\q
+\e 
+F(m) = \al \Mf^{-\al} m^{\al -1} \exp\(-(m/\Mf)^{\al}\).
+\q
+
+\begin{figure}[tbp!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{post-CC.pdf}
+	\caption{\label{posterior-CC}The marginalized one- and two-dimensional posterior distributions for hyper-parameters $\{\Mf, \al, \fpbh\}$ in the critical collapse mass function inferred from GWTC-3.
+The blue color denotes the results from the first merger only, while the orange denotes the results from both the first and second mergers.
+The contours represent the $1\sigma$, $2\sigma$ and $3\sigma$ credible regions, respectively.}
+\end{figure}
+
+\begin{figure}[tbp!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{ratio-CC.pdf}
+	\caption{\label{ratio-CC}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the critical collapse mass function.
+We have fixed the hyper-parameters $\{\Mf, \al, \fpbh\}$ to their best-fit values.}
+\end{figure}
+
+Using $69$ BBHs from GWTC-3 and performing the hierarchical Bayesian inference, we obtain $\Mf = 10.8^{+3.7}_{-3.6} \Msun$, $\al = 1.0^{+0.2}_{-0.2}$, and $\fpbh = 1.5^{+0.2}_{-0.2} \times 10^{-3}$.
+The posteriors for the hyper-parameters $\Ld = \{\Mf, \al, \fpbh\}$ are shown in \Fig{posterior-CC}.
+From \Eq{R0}, we also infer the local merger rate as $R_0 = 49^{+26}_{-16} \gpcyr$.
+The results of local merger rate and abundance of PBHs are consistent with the previous estimations \citep{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+
+In \Fig{ratio-CC}, we show the ratio of merger rate density from second merger to the one from first merger, namely $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing the hyper-parameters $\{\Mf, \al, \fpbh\}$ to their best-fit values.
+It can be seen that the second merger provides more contribution to the total merger rate density as component mass increases.
+Even though $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$ can reach as high as $\gtrsim 10\%$, the ratio of merger rate from second merger to that from first merger is $R_2(t_0)/R_1(t_0) = 2.2^{+1.3}_{-0.1}\%$ and is negligible.
+This is because the major contribution to the merger rate is from the masses less than $50\Msun$, and the correction is negligible in this mass range.
+Therefore the effect of merger history can be safely ignored when estimating the merger rate of PBH binaries.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{\label{conclusion}Conclusion}
+
+In this work, we use $69$ BBHs from GWTC-3 to constrain the merger history of PBH binaries by assuming the observed BBHs from LVK are attributed to PBHs.
+We perform comprehensive Bayesian analyses by considering four commonly used PBH mass functions in literature, namely the log-normal, power-law, broken power-law, and critical collapse mass functions.
+
+We summarize the key results in \Table{table:BF}. 
+It can be seen that the contribution of merger rate from second merger to the total merger rate is less than $5\%$.
+Therefore, the merger history of PBH binaries has subdominant effect, and this effect can be neglected  when evaluating the merger rate of PBH binaries.
+It can also be seen that the Bayes factors for the model with second merger vesus the model with only the first merger, $\mathrm{BF}^{\mathrm{2nd}}_{\mathrm{1st}}$, are all smaller than $3$, indicating the evidence for the second merger is ``not worth more than a bare mention" \citep{BF}.
+In this sense, the Bayes factors also imply the effect of merger history can be ignored.
+
+Furthermore, for all the four mass functions, we infer the abundance of PBH in cold dark matter, $\fpbh$, to be at the order of $\mathcal{O}(10^{-3})$.
+The results of local merger rate and abundance of PBHs are consistent with the previous estimations \citep{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{table}[tbp!]
@@
 		\hline\hline
-		& lognormal & power-law & broken power-law & CC \\
+		& LN & PL & BPL & CC \\
 		\hline
@@
 		$\mathrm{BF}_{\mathrm{PL}}$ & $166$ & $1$ & $2$ & $139$ \\
-		$R_2/R_1$ & $0.011$ & $0.0095$ & $0.0098$ & $0.033$ \\
-		$\fpbh$ & $0.0020$ & $0.0026$ & $0.0026$ & $0.0016$ \\
+		$10^{3}\fpbh$ & $1.8^{+0.3}_{-0.3}$ & $2.3^{+0.3}_{-0.3}$ & $2.2^{+0.3}_{-0.4}$ & $1.5^{+0.2}_{-0.2}$ \\
+		$10^{2}R_2/R_1$ & $1.0^{+0.2}_{-0.1}$ & $0.9^{+0.1}_{-0.1}$ & $0.9^{+0.3}_{-0.1}$ & $2.2^{+1.3}_{-0.5}$ \\
 		\hline
 	\end{tabular}
+	\caption{\label{table:BF} Summary of the key results for the log-normal (LN), power-law (PL), broken power-law (BPL), and critical collapse (CC) mass functions.
+The first row, $\mathrm{BF}^{\mathrm{2nd}}_{\mathrm{1st}}$, shows the Bayes factors for the model with 2nd merger versus the model with only 1st merger; the second row, $\mathrm{BF}_{\mathrm{PL}}$, shows the Bayes factors for the model with different PBH mass function versus the model with the power-law PBH mass function by accounting for the second merger effect; the third row, $\fpbh$, shows the abundance of PBH in dark matter inferred from different models by accounting for the second merger effect; the last row, $R_2/R_1$, shows the merger rate ratio between the second merger and the first merger.}
 \end{table}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{\label{conclusion}Conclusion}
-
-In this paper, we use the publicly available GW data of $10$ BBH events from 
-\lvc\ O1 and O2 observing runs to constrain the merger rate distribution 
-of PBHs by taking into account the effect of merger history.
-Considering two concrete mass functions of PBHs, a power-law PDF and 
-a log-normal one, we demonstrate that the contribution of merger rate (density)
-from second-merger history to total merger rate (density) is 
-subdominant, and hence the second-merger history effect can be safely ignored.
-As third-merger (and later merger) history will make even less contribution to 
-the total merger rate (density), we conclude that the effect of merger history
-is subdominant and can be neglected when evaluating the merger rate of PBH
-binaries.
-
-Furthermore, the results of local merger rate and abundance of PBHs inferred from the updated
-analysis are consistent with the previous estimations, 
-confirming that the main components of CDM should not be made of stellar 
-mass PBHs.
+We also compute the Bayes factors between the models with different PBH mass functions.
+The Bayes factors $\mathrm{BF}_{\mathrm{PL}}$ are estimated by taking the model with power-law mass function as the fiducial model.
+We find that $\mathrm{BF}_{\mathrm{PL}}^{\mathrm{LG}}$ has the largest value, indicating that GWTC-3 can be best fitted by the log-normal mass function among the four mass functions considered in this work.
+Our findings contradict with the results from \cite{Deng:2021ezy} claiming that broken power-law mass function can fit better than the log-normal form.
+There are some drawbacks from analyses in \cite{Deng:2021ezy}.
+Firstly, \cite{Deng:2021ezy} neglects the uncertainties in the measurement of each event's masses and completely ignores redshift evolution of the merger rate.
+Secondly, \cite{Deng:2021ezy} deals with the selection effect of GW detectors in an improper way.
+In this sense, we disagree with \cite{Deng:2021ezy} and conclude that the most frequently used log-normal mass function can fit GWTC-3 best among the four mass functions.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% acknowledgments %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section*{acknowledgments}
 \begin{acknowledgments}
@@
 We would also like to thank Xingjiang Zhu, Xiao-Jin Liu, Shen-Shi Du, and Zhu Yi for useful discussions.
-This work is supported by grants from National Natural Science Foundation of China (grant No.11847107). 
-This research has made use of data, software and/or web tools obtained 
-from the Gravitational Wave Open Science Center \cite{Vallisneri:2014vxa}
-(\url{https://www.gw-openscience.org}), a service of LIGO Laboratory, 
-the LIGO Scientific Collaboration and the Virgo Collaboration. 
-LIGO is funded by the U.S. National Science Foundation. 
-Virgo is funded by the French Centre National de Recherche Scientifique (CNRS),
-the Italian Istituto Nazionale della Fisica Nucleare (INFN) and the Dutch Nikhef,
-with contributions by Polish and Hungarian institutes. 
+Z.-C.C. is supported by the China Postdoctoral Science Foundation Fellowship No.~2022M710429.
+This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center (\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the LIGO Scientific Collaboration, the Virgo Collaboration, and the KAGRA Collaboration.
+LIGO Laboratory and Advanced LIGO are funded by the United States National Science Foundation (NSF) as well as the Science and Technology Facilities Council (STFC) of the United Kingdom, the Max-Planck-Society (MPS), and the State of Niedersachsen/Germany for support of the construction of Advanced LIGO and construction and operation of the GEO600 detector.
+Additional support for Advanced LIGO was provided by the Australian Research Council.
+Virgo is funded, through the European Gravitational Observatory (EGO), by the French Centre National de Recherche Scientifique (CNRS), the Italian Istituto Nazionale di Fisica Nucleare (INFN) and the Dutch Nikhef, with contributions by institutions from Belgium, Germany, Greece, Hungary, Ireland, Japan, Monaco, Poland, Portugal, Spain.
+The construction and operation of KAGRA are funded by Ministry of Education, Culture, Sports, Science and Technology (MEXT), and Japan Society for the Promotion of Science (JSPS), National Research Foundation (NRF) and Ministry of Science and ICT (MSIT) in Korea, Academia Sinica (AS) and the Ministry of Science and Technology (MoST) in Taiwan.
 \end{acknowledgments}

### 2022-10-28 latex/paper.tex
update

@@
 \begin{abstract}
-Primordial black holes (PBHs), as dark matter candidates, have attracted 
-more and more attentions as they could be possible progenitors of 
-the heavy binary black holes (BBHs) observed by \lvc.
-Accurately estimating the merger rate of PBH binaries will be crucial to
-reconstruct the mass distribution of PBHs.
-%However there exists some uncertainties in estimating the merger rate.
-It was pointed out the merger history of PBHs may shift the merger rate distribution depending on the mass function of PBHs.
-In this paper, we use BBH events from \lvc\ GWTC-3 data release to
-constrain the merger rate distribution of PBHs by taking into account the effect of merger history.
-It is found that the second merger process makes subdominant contribution to the 
-total merger rate, and hence the merger history effect can be safely neglected.	
-We also confirm that the main components of dark matter should not be made of stellar 
-mass PBHs.
-
-%\keywords{primordial black holes, merger rate, merger history}
+Primordial black holes (PBHs) can be not only cold dark matter candidates but also progenitors of binary black holes (BBHs) observed by LIGO-Virgo-KAGRA (LVK) Collaboration.
+The PBH mass can be shifted to the heavy distribution if multi-merger processes occur.
+In this work, we constrain the merger history of PBH binaries using the gravitational wave (GW) events from the third GW Transient Catalog (GWTC-3).
+Considering four commonly used PBH mass functions,
+namely the log-normal, power-law, broken power-law, and critical collapse forms, we find that the multi-merger processes make a subdominant contribution to the total merger rate.
+Therefore, the effect of merger history can be safely ignored when estimating the merger rate of PBH binaries.
+We also find that GWTC-3 is best fitted by the log-normal form among the four PBH mass functions and confirm that the stellar-mass PBHs cannot dominate cold dark matter.
 \end{abstract}
@@
 \section{Introduction}
-The direct detection of gravitational wave (GW) from a binary black hole (BBH)
-coalescence \cite{Abbott:2016blz} has opened a new window into the universe.
-Over the past few years, ten BBH mergers have been reported by \lvc\ during 
-the O1 and O2 observing runs \cite{Abbott:2016blz,Abbott:2016nmj,%
-TheLIGOScientific:2016pea,Abbott:2017vtc,%
-Abbott:2017gyy,Abbott:2017oio,LIGOScientific:2018mvr}.
-The progenitors of these BBHs are still unknown and under intensively investigation (see \eg \cite{Bird:2016dcv,Sasaki:2016jop,Chen:2018czv,%
-Fishbach:2017dwv,Clesse:2016vqa,Antonini:2016gqe,%
-Inayoshi:2017mrs,Ali-Haimoud:2017rtz,Perna:2019axr,Kavanagh:2018ggo,%
-Rodriguez:2015oxa,Rodriguez:2016kxx,Park:2017zgj,%
-Belczynski:2014iua,Belczynski:2016obo,Woosley:2016nnw,%
-Rodriguez:2018rmd,Choksi:2018jnq,2010AIPC.1314..291D,deMink:2016vkw}).
-These \lvc\ BBHs present a much heavier mass distribution (in particular the 
-source-frame primary mass of GW170729 event can be as heavy as
-$50.2^{+16.2}_{-10.2} \Msun$ \cite{LIGOScientific:2018mvr}) than that 
-inferred from X-ray observations
-\cite{Wiktorowicz:2013dua,Casares:2013tpa,Corral-Santana:2013uua,%
-Corral-Santana:2015fud},
-which would challenge the formation and evolution mechanisms of astrophysical
-black holes. 
-One possible explanation for \lvc\ BBHs is the primordial black holes (PBHs)
-\cite{Bird:2016dcv,Sasaki:2016jop,Chen:2018czv}
-formed through the gravitational collapse of the primordial density
-fluctuations \cite{Hawking:1971ei,Carr:1974nx}, 
-which may accompany the induced GWs
-\cite{Yuan:2019udt,Yuan:2019wwo,Chen:2019xse,Yuan:2019fwv,Cai:2019bmk,Cai:2018dig,Cai:2019elf,DeLuca:2019ufz,Bartolo:2018rku,Bartolo:2018evs}.
-On the other hand, PBHs can also be a candidate of cold dark matter (CDM),
-and the abundance of PBHs in CDM has been constrained by various experiments
-\cite{Carr:2009jm,Barnacka:2012bm,Graham:2015apa,Niikura:2017zjd,%
-Griest:2013esa,Niikura:2019kqi,Tisserand:2006zx,Brandt:2016aco,Gaggero:2016dpq,%
-Ali-Haimoud:2016mbv,Blum:2016cjs,Horowitz:2016lib,Chen:2016pud,%
-Wang:2016ana,Abbott:2018oah,Magee:2018opb,Wang:2019kaf,Chen:2018rzo,Chen:2019irf,%
-Yuan:2019udt,Chen:2019xse,Montero-Camacho:2019jte,Laha:2019ssq,Dasgupta:2019cae,Gow:2019pok}.
 
-In order to account for the \lvc\ BBHs, the merger rate of PBH binaries has
-been estimated to be $17 \sim 288~\gpcyr$ \cite{Chen:2018rzo}.
-One should notice that theoretically there exist some uncertainties in
-estimating the merger rate distribution of PBH binaries, and the accuracy of 
-the estimation has been continuously improved.
-The merger rate of PBH binaries with monochromatic mass function has already
-been given in \cite{Nakamura:1997sm,Sasaki:2016jop} for the case where two 
-neighboring PBHs having sufficiently small separation can form a binary in
-the early Universe due to the torque from the third nearest PBH.
-These binaries would then evolve and coalesce within the age of the Universe 
-and finally explain the merger events observed by \lvc\
-\cite{Sasaki:2016jop}.
-Later, the merger rate estimation is improved in \cite{Ali-Haimoud:2017rtz} 
-by taking into account the torques exerted by all CDM (including all the PBHs
-and linear density perturbations), but it is also assumed that all PBHs have
-the same mass.
-It is also pointed out in \cite{Ali-Haimoud:2017rtz} that the effects such as
-encountering with other PBHs, tidal field from the smooth halo, and
-the baryon accretion are subdominant and can be neglected when estimating
-the merger rate.
+The successful detection of gravitational waves (GWs) from compact binary coalescences \citep{LIGOScientific:2018mvr,LIGOScientific:2020ibl,LIGOScientific:2021djp} has led us into a new era of GW astronomy.
+According to the recently released third GW Transient Catalog (GWTC-3) \citep{LIGOScientific:2021djp} by LIGO-Virgo-KAGRA (LVK) Collaboration, there are $90$ GW events detected during the first three observing runs.
+Most of these events are categorized as binary black hole (BBH) mergers, and the BBHs detected by LVK have a broad mass distribution.
+The heaviest event, GW190521 \citep{LIGOScientific:2020iuh}, has component masses $m_1 = 85^{+21}_{-14}\Msun$ and $m_2 = 66^{+17}_{-18}\Msun$.
+Both masses lie within upper black hole mass gap originated from pulsation pair-instability supernovae \citep{Marchant_2019}, and current modelling places the lower cutoff of the mass gap at $\sim 50\pm 4\Msun$ \citep{Marchant_2019,Farmer_2019,Farmer:2020xne,Marchant:2020haw}.
+Even accounting for the uncertainties in modelling, it still implies at least $m_1$ is well within the mass gap and cannot have originated directly from a stellar progenitor \citep{Anagnostou:2020umw}.
+Therefore, the heavy event GW190521 greatly challenges the stellar evolution scenario of astrophysical black holes.
 
-Various attempts have been made to estimate the merger rate distribution
-of PBH binaries when PBHs have an extended mass function 
-\cite{Chen:2018czv,Chen:2018rzo,Raidal:2018bbj,Raidal:2017mfl,Liu:2018ess,Liu:2020cds,Vaskonen:2019jpv}.
-In particular, a formalism to estimate the effect of merger history of PBHs
-on merger rate distribution has been developed in \cite{Liu:2019rnx},
-and it is argued that the multiple-merger effect may not be ignored if
-PBHs have a power-law or a log-normal mass function by choosing some specific
-parameter values of the mass function.
-An accurate estimation of the merger rate will be crucial to infer the event
-rate of \lvc\ BBHs and constrain the abundance of PBHs in CDM either through
-null detection of sub-solar mass PBH binaries or the null detection
-of stochastic GW background (SGWB) from PBH binaries.
+Besides the astrophysical black holes, another possible explanation for the LVK BBHs is the primordial black holes (PBHs) \citep{Bird:2016dcv,Sasaki:2016jop,Chen:2018czv,Chen:2021nxo}. 
+PBHs are black holes formed in the very early Universe through the gravitational collapse of the primordial density fluctuations \citep{Hawking:1971ei,Carr:1974nx}.
+The formation of PBHs would inevitably accompany the production of scalar-induced GWs \citep{Yuan:2019udt,Yuan:2019wwo,Yuan:2019fwv,Chen:2019xse,DeLuca:2019ufz,Bartolo:2018rku,Bartolo:2018evs}.
+PBHs can also be natural candidates of cold dark matter.
+Recent studies \citep{Chen:2021nxo,Chen:2022fda} show that the BBHs from GWTC-3 are consistent with the PBH scenario, and the abundance of PBH in CDM, $\fpbh$, should be in the order of $\mathcal{O}(10^{-3})$ to explain LVK BBHs.
+In particular, the merger rate for GW190521 derived from the PBH model is consistent with that inferred by LVK, indicating that GW190521 can be a PBH binary \citep{Chen:2021nxo}.
 
-In this paper, we will use the LVK recent released GWTC-3 data to constrain the effect of merger history on the merger rate of PBH binaries assuming all of LVK BBHs are of primordial origin.
+Accurately estimating the merger rate distribution of PBH binaries can be crucial to extract the PBH population parameters from GW data.
+\cite{Liu:2019rnx} study the multi-merger processes of PBH binaries and show that the merger history of PBH binaries may shift the mass distribution from light mass to heavy mass depending on the values of population parameters.
+\cite{Wu:2020drm} then infers the population parameters of PBH binaries by accounting for the merger history effect using $10$ BBHs from GWTC-1, finding that the effect of merger history can be safely ignored when estimating the merger rate of PBH binaries.
+In this work, we use the LVK recent released GWTC-3 data to constrain the effect of merger history on the merger rate of PBH binaries assuming all LVK BBHs are of primordial origin.
+We extend the analyses of \cite{Wu:2020drm} in several aspects.
+Firstly, we use GWTC-3, which expands GWTC-1 with almost six times more BBH events.
+The GWTC-3 events expand the mass and redshift coverage and can alleviate the statistical bias by including significantly more BBHs.
+Secondly, \cite{Wu:2020drm} only consider the PBH mass functions with the log-normal and power-law forms.
+We do more comprehensive analyses by including the broken power-law and critical collapse PBH mass functions that were not considered in \cite{Wu:2020drm}.
+It is claimed by \cite{Deng:2021ezy} that a broken power-law can fit the GW data better than the log-normal form.
+Lastly, we consider the redshift distribution of the merger rate that was ignored in \cite{Wu:2020drm}.
+
 We organize the rest paper as follows.
-In \Sec{merger}, we give a brief review on calculation of merger rate of PBH binaries by accounting for the merger history effect.
+In \Sec{merger}, we briefly review the calculation of the merger rate of PBH binaries by accounting for the merger history effect.
 In \Sec{method}, we describe the hierarchical Bayesian framework used to infer the PBH population parameters from GW data.
@@
 
-In this section, we will outline the calculation of merger rate density when taking into account the PBH merger history effect. We refer to \cite{Liu:2019rnx} for more details.
+In this section, we will outline the calculation of merger rate density when considering the PBH merger history effect. We refer to \cite{Liu:2019rnx} for more details.
 
@@
 \e 
-    0.85 \fpbh\, P(m)\, \rd m,
+0.85 \fpbh\, P(m)\, \rd m.
 \q 
-where the coefficient $0.85$ is roughly the fraction of CDM in non-relativistic matter including both CDM and baryons. Following \cite{Liu:2019rnx}, we may define an average PBH mass, $\mpbh$, as
+The coefficient $0.85$ is roughly the fraction of CDM in the non-relativistic matter, including both CDM and baryons. Following \cite{Liu:2019rnx}, we may define an average PBH mass, $\mpbh$, as
 \e\label{mpbh}
@@
 
-We can now proceed to estimate the merger rate densities of PBH binaries by considering the merger history effect.
+We can now estimate the merger rate densities of PBH binaries by considering the merger history effect.
 We assume that PBHs are randomly distributed in the early Universe when they decouple from the cosmic background evolution \citep{Nakamura:1997sm,Sasaki:2016jop,Ali-Haimoud:2017rtz}.
-Two nearest PBHs would attract each other because of the gravitational interactions.
+The two nearest PBHs would attract each other because of the gravitational interactions.
 These two PBHs would obtain the angular momentum from the torque of other PBHs and form a PBH binary.
@@
 
-We do not intend to give a detailed derivation, but quote the results from \cite{Liu:2019rnx} here.
+We do not intend to give a detailed derivation but quote the results from \cite{Liu:2019rnx} here.
 The merger rate density from first-merger process, $\cR_1(t, m_i, m_j)$, is given by \citep{Liu:2019rnx}
@@
 \q
-We only consider the effect of merger history up to second-merger process.
+We only consider the effect of merger history up to the second-merger process.
 Therefore the total merger rate density, $\cR(t, m_i, m_j)$, of PBH binaries at cosmic time $t$ with masses $m_i$ and $m_j$ is
@@
 \q 
-All the above mentioned merger rate (density) is measured at source frame.
+All the above-mentioned merger rate (density) is measured at the source frame.
 We should emphasize that although $R_2(t)$ should be smaller than $R_1(t)$ as expected, $\cR_2(t, m_i, m_j)$ is not necessarily be smaller than $\cR_1(t, m_i, m_j)$ \citep{Liu:2019rnx}.
@@
 \section{\label{method}Hierarchical Bayesian Inference}
-To infer the population parameters, we adopt a hierarchical Bayesian approach by marginalizing over the uncertainty in the estimate of individual event parameters.
-In this section, we describe the hierarchical Bayesian inference used in the parameter estimations.
-The merger rate density \eqref{cR} is measured in source frame, and we need to convert it into the detector frame as
+We adopt a hierarchical Bayesian approach to infer the population parameters by marginalizing the uncertainty in estimating individual event parameters.
+This section describes the hierarchical Bayesian inference used in the parameter estimations.
+The merger rate density \eqref{cR} is measured in the source frame, and we need to convert it into the detector frame as
 \e\label{Rpop}
@@
 where $z$ is the cosmological redshift, $\theta\equiv\{z, m_1, m_2\}$, $\Ld$ is a collection of $\fpbh$ and the parameters from mass function $P(m)$, and $dV_\mathrm{c}/dz$ is the differential comoving volume.
-The factor $1/(1 + z)$ converts time increments from the source frame to the detector frame.
-In this work, we take the cosmological parameters from Planck 2018 \citep{Planck:2018vyg}.
-
-Given the data, $\textbf{d} = \{d_1, d_2, \cdots, d_{N_{\mathrm{obs}}}\}$, of $N_{\mathrm{obs}}$ BBH merger events, we model the total number of events as an inhomogeneous Poisson process, yielding the likelihood \citep{Loredo:2004nn,Thrane:2018qnx,Mandel:2018mve}
-\begin{equation}\label{L1}
-	\mathcal{L}(\textbf{d}|\Ld) \propto N_{\mathrm{exp}}^{N_{\mathrm{obs}}} e^{-N_{\mathrm{exp}}} \prod_{i=1}^{N_{\mathrm{obs}}} \frac{\int \mathcal{L} (d_{i}| \theta)\, \cR_{\mathrm{pop}}(\theta|\Ld) d \theta}{\xi(\Ld)},
-\end{equation}
-where $N_{\exp}\equiv N_{\exp}(\Ld)$ is the expected number of detections over the timespan of observation, and $\mathcal{L} (d_{i}|\theta)$ is the individual event likelihood for the $i$th GW event that can be derived from the individual event's posterior by reweighing with the prior on $\theta$.
-Here, $\xi(\Ld)$ quantifies selection biases for a population with parameters $\Ld$ and is defined by
-\e\label{xi}
-\xi(\Ld) = \int P_{\mathrm{det}}(\theta)\, \cR_{\mathrm{pop}}(\theta|\Ld)\, \mathrm{d} \theta,
-\q
-where $P_{\text{det}}(\theta)$ is the detection probability that depends on the source parameters $\theta$.
-In practice, we use the simulated injections \citep{ligo_scientific_collaboration_and_virgo_2021_5546676} to estimate $\xi(\Ld)$, and \Eq{xi} can be approximated by a Monte Carlo integral over found injections \citep{LIGOScientific:2021psn}
-\begin{equation}
-	\xi(\Ld) \approx \frac{1}{N_{\mathrm{inj}}} \sum_{j=1}^{N_{\text {found }}} \frac{\cR_{\mathrm{pop}}(\theta_{j} | \Ld)}{p_{\mathrm{draw}}(\theta_j)},
-\end{equation}
-where $N_{\text{inj}}$ is the total number of injections, $N_{\text{found}}$ is the number of successfully detected injections, and $p_{\mathrm{draw}}$ is the probability density function from which the injections are drawn.
-Using the posterior samples from each individual event, the hyper-likelihood \eqref{L1} can be estimated as
-\begin{equation}\label{L2}
-	\mathcal{L}(\textbf{d}|\Ld) \propto N_{\mathrm{exp}}^{N_{\mathrm{obs}}} e^{-N_{\mathrm{exp}}} \prod_{i=1}^{N_{\mathrm{obs}}} \frac{1}{\xi(\Ld)} \left\langle \frac{\cR_{\mathrm{pop}}(\theta|\Ld)}{d_L^2(z)} \right\rangle,
-\end{equation}
-where $\langle\cdots\rangle$ denotes the weighted average over posterior samples of $\theta$.
-The denominator $d_L^2(z)$ is the standard priors used in the LVK analysis of individual events where $d_L$ is the luminosity distance.
-
-In this work, we incorporate the PBH population distribution \eqref{cR} into the \texttt{ICAROGW} \citep{Mastrogiovanni:2021wsd} package to estimate the likelihood function \eqref{L2}, and use \texttt{dynesty} \citep{Speagle:2019ivv} sampler called from \texttt{Bilby} \citep{Ashton:2018jfp,Romero-Shaw:2020owr} to sample over the parameter space.
-We use the GW events from GWTC-3 by discarding events with false alarm rate larger than 1 yr$^{-1}$ and events with the secondary component mass smaller than $3\Msun$ to avoid contamination from putative events involving neutron stars following \cite{DeLuca:2021wjr}.
-A total of $69$ GW events from GWTC-3 meet this criteria and the posterior samples of these BBHs are publicly available from \cite{ligo_scientific_collaboration_and_virgo_2021_5655785}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{\label{result}results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The factor $1/(1 + z)$ converts time increments from the source to the detector frame.
+We take the cosmological parameters from Planck 2018 \citep{Planck:2018vyg}.
 
@@
 \end{table}
-Based on the hierarchical statistical framework, we do the parameter estimations for four different PBH mass functions that are commonly used in the literature.
-These mass functions are the log-normal, power-law, broken power-law, and critical collapse (CC) distributions, respectively.
-We summarize the parameters and their prior distributions in \Table{table:priors}.
-Below we show the results for each of the PBH mass function.
 
-\subsection{Log-normal mass function}
-We first consider a PBH mass function with the log-normal form \citep{Dolgov:1992pu} of
-\e\label{log}
-P(m) = \frac{1}{\sqrt{2\pi} \s m} \exp \(-\frac{\ln^2\(m/M_c\)}{2\s^2}\),
+Given the data, $\textbf{d} = \{d_1, d_2, \cdots, d_{N_{\mathrm{obs}}}\}$, of $N_{\mathrm{obs}}$ BBH merger events, we model the total number of events as an inhomogeneous Poisson process, yielding the likelihood \citep{Loredo:2004nn,Thrane:2018qnx,Mandel:2018mve}
+\begin{equation}\label{L1}
+	\mathcal{L}(\textbf{d}|\Ld) \propto N_{\mathrm{exp}}^{N_{\mathrm{obs}}} e^{-N_{\mathrm{exp}}} \prod_{i=1}^{N_{\mathrm{obs}}} \frac{\int \mathcal{L} (d_{i}| \theta)\, \cR_{\mathrm{pop}}(\theta|\Ld) d \theta}{\xi(\Ld)},
+\end{equation}
+where $N_{\exp}\equiv N_{\exp}(\Ld)$ is the expected number of detections over the timespan of observation.
+Here $\mathcal{L} (d_{i}|\theta)$ is the individual event likelihood for the $i$th GW event that can be derived from the individual event's posterior by reweighing with the prior on $\theta$.
+Here, $\xi(\Ld)$ quantifies selection biases for a population with parameters $\Ld$ and is defined by
+\e\label{xi}
+\xi(\Ld) = \int P_{\mathrm{det}}(\theta)\, \cR_{\mathrm{pop}}(\theta|\Ld)\, \mathrm{d} \theta,
 \q
-where $M_c$ represents the central mass of $m P(m)$, and $\s$ characterizes the width of the mass spectrum.
-A huge class of extended mass distributions can be approximated by the log-normal mass function if PBHs are formed from a smooth symmetric peak in the inflationary power spectrum when the slow-roll approximation holds \citep{Green:2016xgy,Carr:2017jsz,Kannike:2017bxn}.
-The hyper-parameters are $\Ld = \{M_c, \s, \fpbh\}$ in this case. 
-We can then derive the averaged PBH mass and averaged number density from \Eq{mpbh} and \Eq{Fm} as
-\e
-\mpbh = M_c \exp \(-\frac{\s^2}{2}\),
-\q
-\e 
-F(m) = \frac{M_c}{\sqrt{2\pi} \s m^2} \exp \(-\frac{\s^2}{2}-\frac{\ln^2\(m/M_c\)}{2\s^2}\).
-\q
+where $P_{\text{det}}(\theta)$ is the detection probability that depends on the source parameters $\theta$.
+In practice, we use the simulated injections \citep{ligo_scientific_collaboration_and_virgo_2021_5546676} to estimate $\xi(\Ld)$, and \Eq{xi} can be approximated by a Monte Carlo integral over found injections \citep{LIGOScientific:2021psn}
+\begin{equation}
+	\xi(\Ld) \approx \frac{1}{N_{\mathrm{inj}}} \sum_{j=1}^{N_{\text {found }}} \frac{\cR_{\mathrm{pop}}(\theta_{j} | \Ld)}{p_{\mathrm{draw}}(\theta_j)},
+\end{equation}
+where $N_{\text{inj}}$ is the total number of injections, $N_{\text{found}}$ is the number of successfully detected injections, and $p_{\mathrm{draw}}$ is the probability density function from which the injections are drawn.
+Using the posterior samples from each event, we estimate the hyper-likelihood \eqref{L1} as
+\begin{equation}\label{L2}
+	\mathcal{L}(\textbf{d}|\Ld) \propto N_{\mathrm{exp}}^{N_{\mathrm{obs}}} e^{-N_{\mathrm{exp}}} \prod_{i=1}^{N_{\mathrm{obs}}} \frac{1}{\xi(\Ld)} \left\langle \frac{\cR_{\mathrm{pop}}(\theta|\Ld)}{d_L^2(z)} \right\rangle,
+\end{equation}
+where $\langle\cdots\rangle$ denotes the weighted average over posterior samples of $\theta$.
+The denominator $d_L^2(z)$ is the standard priors used in the LVK analysis of individual events where $d_L$ is the luminosity distance.
+
+In this work, we incorporate the PBH population distribution \eqref{cR} into the \texttt{ICAROGW} \citep{Mastrogiovanni:2021wsd} package to estimate the likelihood function \eqref{L2}, and use \texttt{dynesty} \citep{Speagle:2019ivv} sampler called from \texttt{Bilby} \citep{Ashton:2018jfp,Romero-Shaw:2020owr} to sample over the parameter space.
+We use the GW events from GWTC-3 by discarding events with false alarm rate larger than 1 yr$^{-1}$ and events with the secondary component mass smaller than $3\Msun$ to avoid contamination from putative events involving neutron stars following \cite{DeLuca:2021wjr}.
+A total of $69$ GW events from GWTC-3 meet this criteria and the posterior samples of these BBHs are publicly available from \cite{ligo_scientific_collaboration_and_virgo_2021_5655785}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{\label{result}results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+Based on the hierarchical statistical framework, we do the parameter estimations for four different PBH mass functions commonly used in the literature.
+These mass functions are the log-normal, power-law, broken power-law, and critical collapse (CC) distributions, respectively.
+We summarize the parameters and their prior distributions in \Table{table:priors}.
+Below we show the results for each of the PBH mass functions.
+
+\subsection{Log-normal mass function}
+We first consider a PBH mass function with the log-normal form \citep{Dolgov:1992pu} of
+\e\label{log}
+P(m) = \frac{1}{\sqrt{2\pi} \s m} \exp \(-\frac{\ln^2\(m/M_c\)}{2\s^2}\),
+\q
+where $M_c$ represents the central mass of $m P(m)$, and $\s$ characterizes the width of the mass spectrum.
+The log-normal mass function can approximate a huge class of extended mass distributions if PBHs are formed from a smooth, symmetric peak in the inflationary power spectrum when the slow-roll approximation holds \citep{Green:2016xgy,Carr:2017jsz,Kannike:2017bxn}.
+The hyper-parameters are $\Ld = \{M_c, \s, \fpbh\}$ in this case. 
+We can then derive the averaged PBH mass and averaged number density from \Eq{mpbh} and \Eq{Fm} as
+\e
+\mpbh = M_c \exp \(-\frac{\s^2}{2}\),
+\q
+\e 
+F(m) = \frac{M_c}{\sqrt{2\pi} \s m^2} \exp \(-\frac{\s^2}{2}-\frac{\ln^2\(m/M_c\)}{2\s^2}\).
+\q
+
 Using $69$ BBHs from GWTC-3 and performing the hierarchical Bayesian inference, we obtain $M_c = 17.3^{+2.2}_{-2.0} \Msun$, $\s = 0.71^{+0.10}_{-0.08}$, and $\fpbh = 1.8^{+0.3}_{-0.3} \times 10^{-3}$.
-In this work, we present result with median value and 90\% equal-tailed credible intervals.
+In this work, we present results with median value and 90\% equal-tailed credible intervals.
 The posteriors for the hyper-parameters $\Ld = \{M_c, \s, \fpbh\}$ are shown in \Fig{posterior-log}.
-Note that we get a larger value of $M_c$ than that inferred from GWTC-1 in \cite{Wu:2020drm} because GWTC-3 contains more heavier BHs than those from GWTC-1.
+Note that we get a larger value of $M_c$ than that inferred from GWTC-1 in \cite{Wu:2020drm} because GWTC-3 contains heavier BHs than those from GWTC-1.
 From \Eq{Rt}, we also infer the local merger rate as $R(t_0) = 41^{+16}_{-12} \gpcyr$.
 The results of local merger rate and abundance of PBHs are consistent with the previous estimations \citep{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+
+\begin{figure}[tbp!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{post-power.pdf}
+	\caption{\label{posterior-power}The marginalized one- and two-dimensional posterior distributions for hyper-parameters $\{\Mmin, \al, \fpbh\}$ in the power-law mass function inferred from GWTC-3.
+The blue color denotes the results from the first merger only, while the orange denotes the results from both the first and second mergers.
+The contours represent the $1\sigma$, $2\sigma$ and $3\sigma$ credible regions, respectively.}
+\end{figure}
+
+\begin{figure}[htbp!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{ratio-power.pdf}
+	\caption{\label{ratio-power}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the power-law mass function.
+We have fixed the hyper-parameters $\{\Mmin, \al, \fpbh\}$ to their best-fit values.}
+\end{figure}
 
@@
 \subsection{Power-law mass function}
+
 We next consider a PBH mass function with the power-law form \citep{Carr:1975qj} of
@@
 The posteriors for the hyper-parameters $\Ld = \{\Mmin, \al, \fpbh\}$ are shown in \Fig{posterior-power}.
-Note that we get a smaller value of $\al$ than that inferred from GWTC-1 in \cite{Wu:2020drm} because GWTC-3 contains more heavier BHs than those from GWTC-1.
-From \Eq{R0}, we also infer the local merger rate as $R_0 = 48^{+15}_{-12} \gpcyr$.
+Note that we get a smaller value of $\al$ than that inferred from GWTC-1 in \cite{Wu:2020drm} because GWTC-3 contains heavier BHs than those from GWTC-1.
+From \Eq{Rt}, we also infer the local merger rate as $R(t_0) = 48^{+15}_{-12} \gpcyr$.
 The results of local merger rate and abundance of PBHs are consistent with the previous estimations \citep{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{post-power.pdf}
-	\caption{\label{posterior-power}The marginalized one- and two-dimensional posterior distributions for hyper-parameters $\{\Mmin, \al, \fpbh\}$ in the power-law mass function inferred from GWTC-3.
+	\includegraphics[width=0.5\textwidth]{post-bpower.pdf}
+	\caption{\label{posterior-bpower}The marginalized one- and two-dimensional posterior distributions for hyper-parameters $\{m_*, \al_1, \al_2, \fpbh\}$ in the broken power-law mass function inferred from GWTC-3.
 The blue color denotes the results from the first merger only, while the orange denotes the results from both the first and second mergers.
@@
 
-\begin{figure}[htbp!]
+\begin{figure}[tbp!]
 	\centering
-	\includegraphics[width=0.5\textwidth]{ratio-power.pdf}
-	\caption{\label{ratio-power}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the power-law mass function.
-We have fixed the hyper-parameters $\{\Mmin, \al, \fpbh\}$ to their best-fit values.}
+	\includegraphics[width=0.5\textwidth]{ratio-bpower.pdf}
+	\caption{\label{ratio-bpower}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the broken power-law mass function.
+We have fixed the hyper-parameters $\{m_*, \al_1, \al_2, \fpbh\}$ to their best-fit values.}
 \end{figure}
@@
 Here $\al_1>0$ and $\al_2>1$ are two power-law indices.
-The broken power-law mass function is a generalization of the power-law form and can be achieved if PBHs are formed by vacuum bubbles that nucleate during inflation via quantum tunneling \citep{Deng:2021ezy}.
+The broken power-law mass function is a generalization of the power-law form.
+It can be achieved if PBHs are formed by vacuum bubbles that nucleate during inflation via quantum tunneling \citep{Deng:2021ezy}.
 The hyper-parameters are $\Ld = \{m_*, \al_1, \al_2, \fpbh\}$ in this case. 
@@
 
-\begin{figure}[tbp!]
-	\centering
-	\includegraphics[width=0.5\textwidth]{post-bpower.pdf}
-	\caption{\label{posterior-bpower}The marginalized one- and two-dimensional posterior distributions for hyper-parameters $\{m_*, \al_1, \al_2, \fpbh\}$ in the broken power-law mass function inferred from GWTC-3.
-The blue color denotes the results from the first merger only, while the orange denotes the results from both the first and second mergers.
-The contours represent the $1\sigma$, $2\sigma$ and $3\sigma$ credible regions, respectively.}
-\end{figure}
-
-\begin{figure}[tbp!]
-	\centering
-	\includegraphics[width=0.5\textwidth]{ratio-bpower.pdf}
-	\caption{\label{ratio-bpower}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the broken power-law mass function.
-We have fixed the hyper-parameters $\{m_*, \al_1, \al_2, \fpbh\}$ to their best-fit values.}
-\end{figure}
-
 Using $69$ BBHs from GWTC-3 and performing the hierarchical Bayesian inference, we obtain $m_* = 8.6^{+2.1}_{-1.3} \Msun$, $\al_1 = 5.6^{+7.1}_{-3.8}$, $\al_2 = 2.0^{+0.2}_{-0.2}$, and $\fpbh = 2.2^{+0.3}_{-0.4} \times 10^{-3}$.
 The posteriors for the hyper-parameters $\Ld = \{m_*, \al_1, \al_2, \fpbh\}$ are shown in \Fig{posterior-bpower}.
-From \Eq{R0}, we also infer the local merger rate as $R_0 = 46^{+15}_{-11} \gpcyr$.
+From \Eq{Rt}, we also infer the local merger rate as $R(t_0) = 46^{+15}_{-11} \gpcyr$.
 The results of local merger rate and abundance of PBHs are consistent with the previous estimations \citep{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
 Note that \cite{Deng:2021ezy} obtains quite different results for the broken power-law mass function using GWTC-2 data without accounting for the uncertainties in the measurement of $\vth$.
-\cite{Deng:2021ezy} also deals with the selection effect of the GW detectors in an improper way.
-We emphasize that our results are more robust in the sense that we have a comprehensive treatment of the selection effect and also the measurement uncertainties.
-Nevertheless, our results of the broken power-law mass function are fully consistent with the results of the power-law case as expected.
-
-In \Fig{ratio-bpower}, we show the ratio of merger rate density from second merger to the one from first merger, namely $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing the hyper-parameters $\{m_*, \al_1, \al_2, \fpbh\}$ to their best-fit values.
-It can be seen that the second merger provides more contribution to the total merger rate density as component mass increases.
-Even though $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$ can reach as high as $\gtrsim 10\%$, the ratio of merger rate from second merger to that from first merger is $R_2(t_0)/R_1(t_0) = 0.9^{+0.3}_{-0.1}\%$ and is negligible.
-This is because the major contribution to the merger rate is from the masses less than $50\Msun$, and the correction is negligible in this mass range.
-Therefore the effect of merger history can be safely ignored when estimating the merger rate of PBH binaries.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Critical collapse mass function}
-We last consider a PBH mass function with the critical collapse form \citep{Niemeyer:1997mt,Yokoyama:1998xd,Carr:2016hva,Gow:2020cou} of
-\e
-P(m)=\frac{\alpha^2\,  m^\alpha}{\Mf^{1+\alpha}\, \Gamma(1 / \alpha)} \exp \left(-(m/\Mf)^{\alpha}\right),
-\q
-where $\alpha$ is a universal exponent relating to the critical collapse of radiation, and $M_{\mathrm{f}}$ is the mass scale at the order of horizon mass at the collapse epoch \citep{Carr:2016hva}. 
-For this mass spectrum, there is no lower mass cut-off, but it is exponentially suppressed above the mass scale of $\Mf$.
-The critical collapse mass function is closely associated with a $\delta$-function power spectrum of the density fluctuations \citep{Niemeyer:1997mt,Yokoyama:1998xd,Carr:2016hva,Gow:2020cou}. 
-The hyper-parameters are $\Ld = \{\Mf, \al, \fpbh\}$ in this case. 
-We can then derive the averaged PBH mass and averaged number density from \Eq{mpbh} and \Eq{Fm} as
-\e
-\mpbh = \frac{\Mf \Gamma(1 / \alpha)}{\alpha},
-\q
-\e 
-F(m) = \al \Mf^{-\al} m^{\al -1} \exp\(-(m/\Mf)^{\al}\).
-\q
+\cite{Deng:2021ezy} also deals with the selection effect of the GW detectors improperly.
+We emphasize that our results are more robust because we have a comprehensive treatment of the selection effect and measurement uncertainties.
+Nevertheless, as expected, our results of the broken power-law mass function are fully consistent with the results of the power-law case.
 
@@
 
+In \Fig{ratio-bpower}, we show the ratio of merger rate density from second merger to the one from first merger, namely $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing the hyper-parameters $\{m_*, \al_1, \al_2, \fpbh\}$ to their best-fit values.
+It can be seen that the second merger provides more contribution to the total merger rate density as component mass increases.
+Even though $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$ can reach as high as $\gtrsim 10\%$, the ratio of merger rate from second merger to that from first merger is $R_2(t_0)/R_1(t_0) = 0.9^{+0.3}_{-0.1}\%$ and is negligible.
+This is because the major contribution to the merger rate is from the masses less than $50\Msun$, and the correction is negligible in this mass range.
+Therefore the effect of merger history can be safely ignored when estimating the merger rate of PBH binaries.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Critical collapse mass function}
+
+We last consider a PBH mass function with the critical collapse form \citep{Niemeyer:1997mt,Yokoyama:1998xd,Carr:2016hva,Gow:2020cou} of
+\e
+P(m)=\frac{\alpha^2\,  m^\alpha}{\Mf^{1+\alpha}\, \Gamma(1 / \alpha)} \exp \left(-(m/\Mf)^{\alpha}\right),
+\q
+where $\alpha$ is a universal exponent relating to the critical collapse of radiation, and $M_{\mathrm{f}}$ is the mass scale at the order of horizon mass at the collapse epoch \citep{Carr:2016hva}. 
+There is no lower mass cut-off for this mass spectrum, but it is exponentially suppressed above the mass scale of $\Mf$.
+The critical collapse mass function is closely associated with a $\delta$-function power spectrum of the density fluctuations \citep{Niemeyer:1997mt,Yokoyama:1998xd,Carr:2016hva,Gow:2020cou}. 
+The hyper-parameters are $\Ld = \{\Mf, \al, \fpbh\}$ in this case. 
+We can then derive the averaged PBH mass and averaged number density from \Eq{mpbh} and \Eq{Fm} as
+\e
+\mpbh = \frac{\Mf \Gamma(1 / \alpha)}{\alpha},
+\q
+\e 
+F(m) = \al \Mf^{-\al} m^{\al -1} \exp\(-(m/\Mf)^{\al}\).
+\q
+
 Using $69$ BBHs from GWTC-3 and performing the hierarchical Bayesian inference, we obtain $\Mf = 10.8^{+3.7}_{-3.6} \Msun$, $\al = 1.0^{+0.2}_{-0.2}$, and $\fpbh = 1.5^{+0.2}_{-0.2} \times 10^{-3}$.
 The posteriors for the hyper-parameters $\Ld = \{\Mf, \al, \fpbh\}$ are shown in \Fig{posterior-CC}.
-From \Eq{R0}, we also infer the local merger rate as $R_0 = 49^{+26}_{-16} \gpcyr$.
+From \Eq{Rt}, we also infer the local merger rate as $R(t_0) = 49^{+26}_{-16} \gpcyr$.
 The results of local merger rate and abundance of PBHs are consistent with the previous estimations \citep{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
@@
 We summarize the key results in \Table{table:BF}. 
-It can be seen that the contribution of merger rate from second merger to the total merger rate is less than $5\%$.
-Therefore, the merger history of PBH binaries has subdominant effect, and this effect can be neglected  when evaluating the merger rate of PBH binaries.
-It can also be seen that the Bayes factors for the model with second merger vesus the model with only the first merger, $\mathrm{BF}^{\mathrm{2nd}}_{\mathrm{1st}}$, are all smaller than $3$, indicating the evidence for the second merger is ``not worth more than a bare mention" \citep{BF}.
-In this sense, the Bayes factors also imply the effect of merger history can be ignored.
+It can be seen that the contribution of the merger rate from the second merger to the total merger rate is less than $5\%$.
+Therefore, the merger history of PBH binaries has a subdominant effect, and this effect can be neglected when evaluating the merger rate of PBH binaries.
+It can also be seen that the Bayes factors for the model with a second merger versus the model with only the first merger, $\mathrm{BF}^{\mathrm{2nd}}_{\mathrm{1st}}$, are all smaller than $3$, indicating the evidence for the second merger is ``not worth more than a bare mention" \citep{BF}.
+In this sense, the Bayes factors also imply that the effect of merger history can be ignored.
 
-Furthermore, for all the four mass functions, we infer the abundance of PBH in cold dark matter, $\fpbh$, to be at the order of $\mathcal{O}(10^{-3})$.
+Furthermore, for all four mass functions, we infer the abundance of PBH in cold dark matter, $\fpbh$, to be at the order of $\mathcal{O}(10^{-3})$.
 The results of local merger rate and abundance of PBHs are consistent with the previous estimations \citep{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
@@
 	\end{tabular}
-	\caption{\label{table:BF} Summary of the key results for the log-normal (LN), power-law (PL), broken power-law (BPL), and critical collapse (CC) mass functions.
+	\caption{\label{table:BF}Summary of the key results for the log-normal (LN), power-law (PL), broken power-law (BPL), and critical collapse (CC) mass functions.
 The first row, $\mathrm{BF}^{\mathrm{2nd}}_{\mathrm{1st}}$, shows the Bayes factors for the model with 2nd merger versus the model with only 1st merger; the second row, $\mathrm{BF}_{\mathrm{PL}}$, shows the Bayes factors for the model with different PBH mass function versus the model with the power-law PBH mass function by accounting for the second merger effect; the third row, $\fpbh$, shows the abundance of PBH in dark matter inferred from different models by accounting for the second merger effect; the last row, $R_2/R_1$, shows the merger rate ratio between the second merger and the first merger.}
@@
 We also compute the Bayes factors between the models with different PBH mass functions.
-The Bayes factors $\mathrm{BF}_{\mathrm{PL}}$ are estimated by taking the model with power-law mass function as the fiducial model.
-We find that $\mathrm{BF}_{\mathrm{PL}}^{\mathrm{LG}}$ has the largest value, indicating that GWTC-3 can be best fitted by the log-normal mass function among the four mass functions considered in this work.
-Our findings contradict with the results from \cite{Deng:2021ezy} claiming that broken power-law mass function can fit better than the log-normal form.
+The Bayes factors $\mathrm{BF}_{\mathrm{PL}}$ are estimated by taking the model with the power-law mass function as the fiducial model.
+We find that $\mathrm{BF}_{\mathrm{PL}}^{\mathrm{LG}}$ has the largest value, indicating that the log-normal mass function can best fit GWTC-3 among the four mass functions considered in this work.
+Our findings contradict the results from \cite{Deng:2021ezy} claiming that the broken power-law mass function can fit better than the log-normal form.
 There are some drawbacks from analyses in \cite{Deng:2021ezy}.
-Firstly, \cite{Deng:2021ezy} neglects the uncertainties in the measurement of each event's masses and completely ignores redshift evolution of the merger rate.
-Secondly, \cite{Deng:2021ezy} deals with the selection effect of GW detectors in an improper way.
+Firstly, \cite{Deng:2021ezy} neglects the uncertainties in measuring each event's masses and completely ignores the redshift evolution of the merger rate.
+Secondly, \cite{Deng:2021ezy} deals with the selection effect of GW detectors improperly.
 In this sense, we disagree with \cite{Deng:2021ezy} and conclude that the most frequently used log-normal mass function can fit GWTC-3 best among the four mass functions.

### 2022-10-28 latex/paper.tex
Updates from Overleaf

@@
-\documentclass[twocolumn]{aastex631}
-%\documentclass[twocolumn,linenumbers]{aastex631}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[
+%a4paper,       % letterpaper, a4paper, a5paper
+%10pt,              % 10pt, 11pt, 12pt
+reprint,           % journal's actual layout
+%preprint,          % 12pt, single-column
+superscriptaddress,% authors with affiliations via superscripts
+amsmath,           % add AMS-Latex features
+amssymb,           % add extra AMS symbols, including amsfonts
+aps,               % aps or aip
+prd,               % prl, pra, prb, prc, prd, pre, prstab
+%showpacs,          % make PACS codes appear
+notitlepage,       % control appearance of title page
+longbibliography,  % show  article titles in the bibliography
+floatfix,          % process floats as early as possible
+%showkeys,          % option to make keywords appear
+%titlepage,         %
+%eqsecnum,          % number equations by section
+nofootinbib,
+]{revtex4-1}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% load packages %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %\usepackage{ulem}
-%\hypersetup{linkcolor=red,citecolor=blue,filecolor=cyan,urlcolor=magenta}
+\usepackage[
+colorlinks=true,        % color link
+citecolor=blue,         % cite color
+linkcolor=blue,         % link color
+urlcolor=blue           % url color
+]{hyperref}       
 \usepackage{amsmath}
@@
 %\usepackage{tensor}     % manipulate tensors
-%\usepackage{graphicx}   % include figures
+\usepackage{graphicx}   % include figures
 %\usepackage{bm}         % \bm{<text>} Bold math symbols
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%% only used in this paper %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\nc{\mH}{\mathcal{H}}
-\nc{\cs}{c_s^2}
-\nc{\Sij}[1]{S_{ij}^{(#1)}}
-\nc{\vi}[1]{v_i^{(#1)}}
-\nc{\no}{\nonumber}
-\def\<{\left\langle}
-\def\>{\right\rangle}
-\def\ap{\alpha}
-\def\half{{1\over 2}}
-\nc{\bk}{\bm{k}}
-\nc{\bq}{\bm{q}}
-\nc{\bp}{\bm{p}}
-\nc{\bl}{\bm{l}}
-\nc{\bx}{\bm{x}}
-\nc{\be}{\mathbf{e}}
-\nc{\mS}{\mathcal{S}}
-\nc{\te}{\tilde{\eta}}
-\nc{\tp}{\tilde{p}}
-\nc{\tk}{\tilde{k}}
-\nc{\tx}{\tilde{x}}
-\nc{\tF}{\tilde{F}}
-\nc{\tA}{\tilde{A}}
-\nc{\mkpq}{|\bk-\bp-\bq|}
-\nc{\mpq}{|\bp-\bq|}
-\nc{\mkp}{|\bk-\bp|}
-\nc{\mSi}[1]{\mS^{(#1)}({\bk, \eta})}
-\nc{\vk}{\vec{k}}
-\nc{\kstar}{k_*}
-\nc{\xstar}{x_*}
+% \nc{\mH}{\mathcal{H}}
+% \nc{\cs}{c_s^2}
+% \nc{\Sij}[1]{S_{ij}^{(#1)}}
+% \nc{\vi}[1]{v_i^{(#1)}}
+% \nc{\no}{\nonumber}
+% \def\<{\left\langle}
+% \def\>{\right\rangle}
+% \def\ap{\alpha}
+% \def\half{{1\over 2}}
+% \nc{\bk}{\bm{k}}
+% \nc{\bq}{\bm{q}}
+% \nc{\bp}{\bm{p}}
+% \nc{\bl}{\bm{l}}
+% \nc{\bx}{\bm{x}}
+% \nc{\be}{\mathbf{e}}
+% \nc{\mS}{\mathcal{S}}
+% \nc{\te}{\tilde{\eta}}
+% \nc{\tp}{\tilde{p}}
+% \nc{\tk}{\tilde{k}}
+% \nc{\tx}{\tilde{x}}
+% \nc{\tF}{\tilde{F}}
+% \nc{\tA}{\tilde{A}}
+% \nc{\mkpq}{|\bk-\bp-\bq|}
+% \nc{\mpq}{|\bp-\bq|}
+% \nc{\mkp}{|\bk-\bp|}
+% \nc{\mSi}[1]{\mS^{(#1)}({\bk, \eta})}
+% \nc{\vk}{\vec{k}}
+% \nc{\kstar}{k_*}
+% \nc{\xstar}{x_*}
 \nc{\mpbh}{m_{\rm{pbh}}}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author[0000-0002-0297-9633]{Lang~Liu}
+% \author[0000-0002-0297-9633]{Lang~Liu}
+\author{Lang~Liu}
 \email{liulang@bnu.edu.cn}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author[0000-0002-3309-415X]{Zhi-Qiang~You}
+% \author[0000-0002-3309-415X]{Zhi-Qiang~You}
+\author{Zhi-Qiang~You}
 \email{zhiqiang.you@bnu.edu.cn}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author[0000-0002-9610-2284]{You~Wu}
+% \author[0000-0002-9610-2284]{You~Wu}
+\author{You~Wu}
 \email{youwuphy@gmail.com}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author[0000-0001-7016-9934]{Zu-Cheng~Chen}
+% \author[0000-0001-7016-9934]{Zu-Cheng~Chen}
+\author{Zu-Cheng~Chen}
 \email{Corresponding author: zucheng.chen@bnu.edu.cn}
@@
 \begin{abstract}
-Primordial black holes (PBHs) can be not only cold dark matter candidates but also progenitors of binary black holes (BBHs) observed by LIGO-Virgo-KAGRA (LVK) Collaboration.
+Primordial black holes (PBHs) can be not only cold dark matter candidates but also progenitors of binary black holes observed by LIGO-Virgo-KAGRA (LVK) Collaboration.
 The PBH mass can be shifted to the heavy distribution if multi-merger processes occur.
-In this work, we constrain the merger history of PBH binaries using the gravitational wave (GW) events from the third GW Transient Catalog (GWTC-3).
+In this work, we constrain the merger history of PBH binaries using the gravitational wave events from the third Gravitational-Wave Transient Catalog (GWTC-3).
 Considering four commonly used PBH mass functions,
@@
 
-%\maketitle
+\maketitle
 
@@
 
-The successful detection of gravitational waves (GWs) from compact binary coalescences \citep{LIGOScientific:2018mvr,LIGOScientific:2020ibl,LIGOScientific:2021djp} has led us into a new era of GW astronomy.
-According to the recently released third GW Transient Catalog (GWTC-3) \citep{LIGOScientific:2021djp} by LIGO-Virgo-KAGRA (LVK) Collaboration, there are $90$ GW events detected during the first three observing runs.
+The successful detection of gravitational waves (GWs) from compact binary coalescences \cite{LIGOScientific:2018mvr,LIGOScientific:2020ibl,LIGOScientific:2021djp} has led us into a new era of GW astronomy.
+According to the recently released third GW Transient Catalog (GWTC-3) \cite{LIGOScientific:2021djp} by LIGO-Virgo-KAGRA (LVK) Collaboration, there are $90$ GW events detected during the first three observing runs.
 Most of these events are categorized as binary black hole (BBH) mergers, and the BBHs detected by LVK have a broad mass distribution.
-The heaviest event, GW190521 \citep{LIGOScientific:2020iuh}, has component masses $m_1 = 85^{+21}_{-14}\Msun$ and $m_2 = 66^{+17}_{-18}\Msun$.
-Both masses lie within upper black hole mass gap originated from pulsation pair-instability supernovae \citep{Marchant_2019}, and current modelling places the lower cutoff of the mass gap at $\sim 50\pm 4\Msun$ \citep{Marchant_2019,Farmer_2019,Farmer:2020xne,Marchant:2020haw}.
-Even accounting for the uncertainties in modelling, it still implies at least $m_1$ is well within the mass gap and cannot have originated directly from a stellar progenitor \citep{Anagnostou:2020umw}.
+The heaviest event, GW190521 \cite{LIGOScientific:2020iuh}, has component masses $m_1 = 85^{+21}_{-14}\Msun$ and $m_2 = 66^{+17}_{-18}\Msun$.
+Both masses lie within upper black hole mass gap originated from pulsation pair-instability supernovae \cite{Marchant_2019}, and current modelling places the lower cutoff of the mass gap at $\sim 50\pm 4\Msun$ \cite{belczynski2016effect,Marchant_2019,Farmer_2019,Farmer:2020xne,Marchant:2020haw}.
+Even accounting for the uncertainties in modelling, it still implies at least $m_1$ is well within the mass gap and cannot originate directly from a stellar progenitor \cite{Anagnostou:2020umw}.
 Therefore, the heavy event GW190521 greatly challenges the stellar evolution scenario of astrophysical black holes.
 
-Besides the astrophysical black holes, another possible explanation for the LVK BBHs is the primordial black holes (PBHs) \citep{Bird:2016dcv,Sasaki:2016jop,Chen:2018czv,Chen:2021nxo}. 
-PBHs are black holes formed in the very early Universe through the gravitational collapse of the primordial density fluctuations \citep{Hawking:1971ei,Carr:1974nx}.
-The formation of PBHs would inevitably accompany the production of scalar-induced GWs \citep{Yuan:2019udt,Yuan:2019wwo,Yuan:2019fwv,Chen:2019xse,DeLuca:2019ufz,Bartolo:2018rku,Bartolo:2018evs}.
+Besides the astrophysical black holes, another possible explanation for the LVK BBHs is the primordial black holes (PBHs) \cite{Bird:2016dcv,Sasaki:2016jop,Chen:2018czv,Liu:2018ess,Chen:2021nxo}. 
+PBHs are black holes formed in the very early Universe through the gravitational collapse of the primordial density fluctuations \cite{Hawking:1971ei,Carr:1974nx}.
+The formation of PBHs would inevitably accompany the production of scalar-induced GWs \cite{Saito:2008jc,Yuan:2019udt,Yuan:2019wwo,Yuan:2019fwv,Chen:2019xse,DeLuca:2019ufz,Bartolo:2018rku,Bartolo:2018evs}.
 PBHs can also be natural candidates of cold dark matter.
-Recent studies \citep{Chen:2021nxo,Chen:2022fda} show that the BBHs from GWTC-3 are consistent with the PBH scenario, and the abundance of PBH in CDM, $\fpbh$, should be in the order of $\mathcal{O}(10^{-3})$ to explain LVK BBHs.
-In particular, the merger rate for GW190521 derived from the PBH model is consistent with that inferred by LVK, indicating that GW190521 can be a PBH binary \citep{Chen:2021nxo}.
+Recent studies \cite{Chen:2021nxo,Chen:2022fda} show that the BBHs from GWTC-3 are consistent with the PBH scenario, and the abundance of PBH in CDM, $\fpbh$, should be in the order of $\mathcal{O}(10^{-3})$ to explain LVK BBHs.
+In particular, the merger rate for GW190521 derived from the PBH model is consistent with that inferred by LVK, indicating that GW190521 can be a PBH binary \cite{DeLuca:2020sae,Chen:2021nxo}.
 
 Accurately estimating the merger rate distribution of PBH binaries can be crucial to extract the PBH population parameters from GW data.
-\cite{Liu:2019rnx} study the multi-merger processes of PBH binaries and show that the merger history of PBH binaries may shift the mass distribution from light mass to heavy mass depending on the values of population parameters.
-\cite{Wu:2020drm} then infers the population parameters of PBH binaries by accounting for the merger history effect using $10$ BBHs from GWTC-1, finding that the effect of merger history can be safely ignored when estimating the merger rate of PBH binaries.
+Ref.~\cite{Liu:2019rnx} studies the multi-merger processes of PBH binaries and show that the merger history of PBH binaries may shift the mass distribution from light mass to heavy mass depending on the values of population parameters.
+Ref.~\cite{Wu:2020drm} then infers the population parameters of PBH binaries by accounting for the merger history effect using $10$ BBHs from GWTC-1, finding that the effect of merger history can be safely ignored when estimating the merger rate of PBH binaries.
 In this work, we use the LVK recent released GWTC-3 data to constrain the effect of merger history on the merger rate of PBH binaries assuming all LVK BBHs are of primordial origin.
-We extend the analyses of \cite{Wu:2020drm} in several aspects.
+We extend the analyses of Ref.~\cite{Wu:2020drm} in several aspects.
 Firstly, we use GWTC-3, which expands GWTC-1 with almost six times more BBH events.
 The GWTC-3 events expand the mass and redshift coverage and can alleviate the statistical bias by including significantly more BBHs.
-Secondly, \cite{Wu:2020drm} only consider the PBH mass functions with the log-normal and power-law forms.
-We do more comprehensive analyses by including the broken power-law and critical collapse PBH mass functions that were not considered in \cite{Wu:2020drm}.
-It is claimed by \cite{Deng:2021ezy} that a broken power-law can fit the GW data better than the log-normal form.
-Lastly, we consider the redshift distribution of the merger rate that was ignored in \cite{Wu:2020drm}.
+Secondly, Ref.~\cite{Wu:2020drm} only considers the PBH mass functions with the log-normal and power-law forms.
+We do more comprehensive analyses by including the broken power-law and critical collapse PBH mass functions that were not considered in Ref.~\cite{Wu:2020drm}.
+It is claimed by Ref.~\cite{Deng:2021ezy} that a broken power-law can fit the GW data better than the log-normal form.
+Lastly, we consider the redshift distribution of the merger rate that is ignored in Ref.~\cite{Wu:2020drm}.
 
@@
 
-In this section, we will outline the calculation of merger rate density when considering the PBH merger history effect. We refer to \cite{Liu:2019rnx} for more details.
+In this section, we will outline the calculation of merger rate density when considering the PBH merger history effect. We refer to Ref.~\cite{Liu:2019rnx} for more details.
 
@@
 \q 
-Assuming the fraction of PBHs in CDM is $\fpbh$, we can estimate the abundance of PBHs in the mass interval $(m, m+\rd m)$ as \citep{Chen:2018rzo}
+Assuming the fraction of PBHs in CDM is $\fpbh$, we can estimate the abundance of PBHs in the mass interval $(m, m+\rd m)$ as \cite{Chen:2018rzo}
 \e 
@@
 \q 
-The coefficient $0.85$ is roughly the fraction of CDM in the non-relativistic matter, including both CDM and baryons. Following \cite{Liu:2019rnx}, we may define an average PBH mass, $\mpbh$, as
+The coefficient $0.85$ is roughly the fraction of CDM in the non-relativistic matter, including both CDM and baryons. Following Ref.~\cite{Liu:2019rnx}, we may define an average PBH mass, $\mpbh$, as
 \e\label{mpbh}
@@
 Then, we can obtain the average number density of PBHs with mass $m$ in the 
-total number density of PBHs, $F(m)$, by \citep{Liu:2019rnx}
+total number density of PBHs, $F(m)$, by \cite{Liu:2019rnx}
 \e\label{Fm} 
@@
 We can now estimate the merger rate densities of PBH binaries by considering the merger history effect.
-We assume that PBHs are randomly distributed in the early Universe when they decouple from the cosmic background evolution \citep{Nakamura:1997sm,Sasaki:2016jop,Ali-Haimoud:2017rtz}.
+We assume that PBHs are randomly distributed in the early Universe when they decouple from the cosmic background evolution \cite{Nakamura:1997sm,Sasaki:2016jop,Ali-Haimoud:2017rtz}.
 The two nearest PBHs would attract each other because of the gravitational interactions.
@@
 
-We do not intend to give a detailed derivation but quote the results from \cite{Liu:2019rnx} here.
-The merger rate density from first-merger process, $\cR_1(t, m_i, m_j)$, is given by \citep{Liu:2019rnx}
+We do not intend to give a detailed derivation but quote the results from Ref.~\cite{Liu:2019rnx} here.
+The merger rate density from first-merger process, $\cR_1(t, m_i, m_j)$, is given by \cite{Liu:2019rnx}
 \e 
@@
 \q
-Similarly, the merger rate density from second-merger process, $\cR_2(t, m_i, m_j)$, is given by \citep{Liu:2019rnx}
+Similarly, the merger rate density from second-merger process, $\cR_2(t, m_i, m_j)$, is given by \cite{Liu:2019rnx}
 \e 
@@
 All the above-mentioned merger rate (density) is measured at the source frame.
-We should emphasize that although $R_2(t)$ should be smaller than $R_1(t)$ as expected, $\cR_2(t, m_i, m_j)$ is not necessarily be smaller than $\cR_1(t, m_i, m_j)$ \citep{Liu:2019rnx}.
+We should emphasize that although $R_2(t)$ should be smaller than $R_1(t)$ as expected, $\cR_2(t, m_i, m_j)$ is not necessarily be smaller than $\cR_1(t, m_i, m_j)$ \cite{Liu:2019rnx}.
 
@@
 The factor $1/(1 + z)$ converts time increments from the source to the detector frame.
-We take the cosmological parameters from Planck 2018 \citep{Planck:2018vyg}.
+We take the cosmological parameters from Planck 2018 \cite{Planck:2018vyg}.
 
@@
 
-Given the data, $\textbf{d} = \{d_1, d_2, \cdots, d_{N_{\mathrm{obs}}}\}$, of $N_{\mathrm{obs}}$ BBH merger events, we model the total number of events as an inhomogeneous Poisson process, yielding the likelihood \citep{Loredo:2004nn,Thrane:2018qnx,Mandel:2018mve}
+Given the data, $\textbf{d} = \{d_1, d_2, \cdots, d_{N_{\mathrm{obs}}}\}$, of $N_{\mathrm{obs}}$ BBH merger events, we model the total number of events as an inhomogeneous Poisson process, yielding the likelihood \cite{Loredo:2004nn,Thrane:2018qnx,Mandel:2018mve}
 \begin{equation}\label{L1}
@@
 where $P_{\text{det}}(\theta)$ is the detection probability that depends on the source parameters $\theta$.
-In practice, we use the simulated injections \citep{ligo_scientific_collaboration_and_virgo_2021_5546676} to estimate $\xi(\Ld)$, and \Eq{xi} can be approximated by a Monte Carlo integral over found injections \citep{LIGOScientific:2021psn}
+In practice, we use the simulated injections \cite{ligo_scientific_collaboration_and_virgo_2021_5546676} to estimate $\xi(\Ld)$, and \Eq{xi} can be approximated by a Monte Carlo integral over found injections \cite{LIGOScientific:2021psn}
 \begin{equation}
@@
 
-In this work, we incorporate the PBH population distribution \eqref{cR} into the \texttt{ICAROGW} \citep{Mastrogiovanni:2021wsd} package to estimate the likelihood function \eqref{L2}, and use \texttt{dynesty} \citep{Speagle:2019ivv} sampler called from \texttt{Bilby} \citep{Ashton:2018jfp,Romero-Shaw:2020owr} to sample over the parameter space.
-We use the GW events from GWTC-3 by discarding events with false alarm rate larger than 1 yr$^{-1}$ and events with the secondary component mass smaller than $3\Msun$ to avoid contamination from putative events involving neutron stars following \cite{DeLuca:2021wjr}.
-A total of $69$ GW events from GWTC-3 meet this criteria and the posterior samples of these BBHs are publicly available from \cite{ligo_scientific_collaboration_and_virgo_2021_5655785}.
+In this work, we incorporate the PBH population distribution \eqref{cR} into the \texttt{ICAROGW} \cite{Mastrogiovanni:2021wsd} package to estimate the likelihood function \eqref{L2}, and use \texttt{dynesty} \cite{Speagle:2019ivv} sampler called from \texttt{Bilby} \cite{Ashton:2018jfp,Romero-Shaw:2020owr} to sample over the parameter space.
+We use the GW events from GWTC-3 by discarding events with false alarm rate larger than 1 yr$^{-1}$ and events with the secondary component mass smaller than $3\Msun$ to avoid contamination from putative events involving neutron stars following Ref.~\cite{DeLuca:2021wjr}.
+A total of $69$ GW events from GWTC-3 meet this criteria and the posterior samples of these BBHs are publicly available from Ref.~\cite{ligo_scientific_collaboration_and_virgo_2021_5655785}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}[tbp!]
-	\centering
-	\includegraphics[width=0.5\textwidth]{post-log.pdf}
-	\caption{\label{posterior-log}The marginalized one- and two-dimensional posterior distributions for hyper-parameters $\{M_c, \s, \fpbh\}$ in the log-normal mass function inferred from GWTC-3.
-The blue color denotes the results from the first merger only, while the orange denotes the results from both the first and second mergers.
-The contours represent the $1\sigma$, $2\sigma$ and $3\sigma$ credible regions, respectively.}
-\end{figure}
-
-\begin{figure}[htbp!]
-	\centering
-	\includegraphics[width=0.5\textwidth]{ratio-log.pdf}
-	\caption{\label{ratio-log}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the log-normal mass function.
-We have fixed the hyper-parameters $\{M_c, \s, \fpbh\}$ to their best-fit values.}
-\end{figure}
 
@@
 \subsection{Log-normal mass function}
-We first consider a PBH mass function with the log-normal form \citep{Dolgov:1992pu} of
+
+\begin{figure}[tbp!]
+	\centering
+	\includegraphics[width=\linewidth]{post-log.pdf}
+	\caption{\label{posterior-log}The marginalized one- and two-dimensional posterior distributions for hyper-parameters $\{M_c, \s, \fpbh\}$ in the log-normal mass function inferred from GWTC-3.
+The blue color denotes the results from the first merger only, while the orange denotes the results from both the first and second mergers.
+The contours represent the $1\sigma$, $2\sigma$ and $3\sigma$ credible regions, respectively.}
+\end{figure}
+
+We first consider a PBH mass function with the log-normal form \cite{Dolgov:1992pu} of
 \e\label{log}
@@
 where $M_c$ represents the central mass of $m P(m)$, and $\s$ characterizes the width of the mass spectrum.
-The log-normal mass function can approximate a huge class of extended mass distributions if PBHs are formed from a smooth, symmetric peak in the inflationary power spectrum when the slow-roll approximation holds \citep{Green:2016xgy,Carr:2017jsz,Kannike:2017bxn}.
+The log-normal mass function can approximate a huge class of extended mass distributions if PBHs are formed from a smooth, symmetric peak in the inflationary power spectrum when the slow-roll approximation holds \cite{Green:2016xgy,Carr:2017jsz,Kannike:2017bxn}.
 The hyper-parameters are $\Ld = \{M_c, \s, \fpbh\}$ in this case. 
@@
 From \Eq{Rt}, we also infer the local merger rate as $R(t_0) = 41^{+16}_{-12} \gpcyr$.
-The results of local merger rate and abundance of PBHs are consistent with the previous estimations \citep{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{post-power.pdf}
-	\caption{\label{posterior-power}The marginalized one- and two-dimensional posterior distributions for hyper-parameters $\{\Mmin, \al, \fpbh\}$ in the power-law mass function inferred from GWTC-3.
-The blue color denotes the results from the first merger only, while the orange denotes the results from both the first and second mergers.
-The contours represent the $1\sigma$, $2\sigma$ and $3\sigma$ credible regions, respectively.}
-\end{figure}
-
-\begin{figure}[htbp!]
-	\centering
-	\includegraphics[width=0.5\textwidth]{ratio-power.pdf}
-	\caption{\label{ratio-power}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the power-law mass function.
-We have fixed the hyper-parameters $\{\Mmin, \al, \fpbh\}$ to their best-fit values.}
+	\includegraphics[width=\linewidth]{ratio-log.pdf}
+	\caption{\label{ratio-log}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the log-normal mass function.
+We have fixed the hyper-parameters $\{M_c, \s, \fpbh\}$ to their best-fit values.}
 \end{figure}
@@
 
-We next consider a PBH mass function with the power-law form \citep{Carr:1975qj} of
+We next consider a PBH mass function with the power-law form \cite{Carr:1975qj} of
 \e\label{power} 
@@
 where $\Mmin$ is the lower-mass cut-off such that $m>\Mmin$, and $\al>1$ is the power-law index. 
-The power-law mass function can typically result from a broad or flat power spectrum of the curvature perturbations \citep{DeLuca:2020ioi} during radiation dominated era \citep{Carr:2016drx,Carr:2017jsz}.
+The power-law mass function can typically result from a broad or flat power spectrum of the curvature perturbations \cite{DeLuca:2020ioi} during radiation dominated era \cite{Carr:2016drx,Carr:2017jsz}.
 The hyper-parameters are $\Ld = \{\Mmin, \al, \fpbh\}$ in this case. 
@@
 
+\begin{figure}[tbp!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{post-power.pdf}
+	\caption{\label{posterior-power}The marginalized one- and two-dimensional posterior distributions for hyper-parameters $\{\Mmin, \al, \fpbh\}$ in the power-law mass function inferred from GWTC-3.
+The blue color denotes the results from the first merger only, while the orange denotes the results from both the first and second mergers.
+The contours represent the $1\sigma$, $2\sigma$ and $3\sigma$ credible regions, respectively.}
+\end{figure}
+
 Using $69$ BBHs from GWTC-3 and performing the hierarchical Bayesian inference, we obtain $\Mmin = 6.5^{+0.3}_{-0.8} \Msun$, $\al = 1.9^{+0.2}_{-0.2}$, and $\fpbh = 2.3^{+0.3}_{-0.3} \times 10^{-3}$.
@@
 From \Eq{Rt}, we also infer the local merger rate as $R(t_0) = 48^{+15}_{-12} \gpcyr$.
-The results of local merger rate and abundance of PBHs are consistent with the previous estimations \citep{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
 
-\begin{figure}[tbp!]
+\begin{figure}[htbp!]
 	\centering
-	\includegraphics[width=0.5\textwidth]{post-bpower.pdf}
-	\caption{\label{posterior-bpower}The marginalized one- and two-dimensional posterior distributions for hyper-parameters $\{m_*, \al_1, \al_2, \fpbh\}$ in the broken power-law mass function inferred from GWTC-3.
-The blue color denotes the results from the first merger only, while the orange denotes the results from both the first and second mergers.
-The contours represent the $1\sigma$, $2\sigma$ and $3\sigma$ credible regions, respectively.}
-\end{figure}
-
-\begin{figure}[tbp!]
-	\centering
-	\includegraphics[width=0.5\textwidth]{ratio-bpower.pdf}
-	\caption{\label{ratio-bpower}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the broken power-law mass function.
-We have fixed the hyper-parameters $\{m_*, \al_1, \al_2, \fpbh\}$ to their best-fit values.}
+	\includegraphics[width=0.5\textwidth]{ratio-power.pdf}
+	\caption{\label{ratio-power}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the power-law mass function.
+We have fixed the hyper-parameters $\{\Mmin, \al, \fpbh\}$ to their best-fit values.}
 \end{figure}
@@
 \subsection{Broken power-law mass function}
-We then consider a PBH mass function with the broken power-law form \citep{Deng:2021ezy} of
+We then consider a PBH mass function with the broken power-law form \cite{Deng:2021ezy} of
 \begin{equation}
@@
 The broken power-law mass function is a generalization of the power-law form.
-It can be achieved if PBHs are formed by vacuum bubbles that nucleate during inflation via quantum tunneling \citep{Deng:2021ezy}.
+It can be achieved if PBHs are formed by vacuum bubbles that nucleate during inflation via quantum tunneling \cite{Deng:2021ezy}.
 The hyper-parameters are $\Ld = \{m_*, \al_1, \al_2, \fpbh\}$ in this case. 
@@
 
+\begin{figure}[tbp!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{post-bpower.pdf}
+	\caption{\label{posterior-bpower}The marginalized one- and two-dimensional posterior distributions for hyper-parameters $\{m_*, \al_1, \al_2, \fpbh\}$ in the broken power-law mass function inferred from GWTC-3.
+The blue color denotes the results from the first merger only, while the orange denotes the results from both the first and second mergers.
+The contours represent the $1\sigma$, $2\sigma$ and $3\sigma$ credible regions, respectively.}
+\end{figure}
+
 Using $69$ BBHs from GWTC-3 and performing the hierarchical Bayesian inference, we obtain $m_* = 8.6^{+2.1}_{-1.3} \Msun$, $\al_1 = 5.6^{+7.1}_{-3.8}$, $\al_2 = 2.0^{+0.2}_{-0.2}$, and $\fpbh = 2.2^{+0.3}_{-0.4} \times 10^{-3}$.
@@
 From \Eq{Rt}, we also infer the local merger rate as $R(t_0) = 46^{+15}_{-11} \gpcyr$.
-The results of local merger rate and abundance of PBHs are consistent with the previous estimations \citep{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
 Note that \cite{Deng:2021ezy} obtains quite different results for the broken power-law mass function using GWTC-2 data without accounting for the uncertainties in the measurement of $\vth$.
-\cite{Deng:2021ezy} also deals with the selection effect of the GW detectors improperly.
+Moreover, \cite{Deng:2021ezy} deals with the selection effect of the GW detectors improperly.
 We emphasize that our results are more robust because we have a comprehensive treatment of the selection effect and measurement uncertainties.
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{post-CC.pdf}
-	\caption{\label{posterior-CC}The marginalized one- and two-dimensional posterior distributions for hyper-parameters $\{\Mf, \al, \fpbh\}$ in the critical collapse mass function inferred from GWTC-3.
-The blue color denotes the results from the first merger only, while the orange denotes the results from both the first and second mergers.
-The contours represent the $1\sigma$, $2\sigma$ and $3\sigma$ credible regions, respectively.}
-\end{figure}
-
-\begin{figure}[tbp!]
-	\centering
-	\includegraphics[width=0.5\textwidth]{ratio-CC.pdf}
-	\caption{\label{ratio-CC}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the critical collapse mass function.
-We have fixed the hyper-parameters $\{\Mf, \al, \fpbh\}$ to their best-fit values.}
+	\includegraphics[width=0.5\textwidth]{ratio-bpower.pdf}
+	\caption{\label{ratio-bpower}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the broken power-law mass function.
+We have fixed the hyper-parameters $\{m_*, \al_1, \al_2, \fpbh\}$ to their best-fit values.}
 \end{figure}
@@
 
-We last consider a PBH mass function with the critical collapse form \citep{Niemeyer:1997mt,Yokoyama:1998xd,Carr:2016hva,Gow:2020cou} of
+We last consider a PBH mass function with the critical collapse form \cite{Niemeyer:1997mt,Yokoyama:1998xd,Carr:2016hva,Gow:2020cou} of
 \e
@@
 \q
-where $\alpha$ is a universal exponent relating to the critical collapse of radiation, and $M_{\mathrm{f}}$ is the mass scale at the order of horizon mass at the collapse epoch \citep{Carr:2016hva}. 
+where $\alpha$ is a universal exponent relating to the critical collapse of radiation, and $M_{\mathrm{f}}$ is the mass scale at the order of horizon mass at the collapse epoch \cite{Carr:2016hva}. 
 There is no lower mass cut-off for this mass spectrum, but it is exponentially suppressed above the mass scale of $\Mf$.
-The critical collapse mass function is closely associated with a $\delta$-function power spectrum of the density fluctuations \citep{Niemeyer:1997mt,Yokoyama:1998xd,Carr:2016hva,Gow:2020cou}. 
+The critical collapse mass function is closely associated with a $\delta$-function power spectrum of the density fluctuations \cite{Niemeyer:1997mt,Yokoyama:1998xd,Carr:2016hva,Gow:2020cou}. 
 The hyper-parameters are $\Ld = \{\Mf, \al, \fpbh\}$ in this case. 
@@
 
+\begin{figure}[tbp!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{post-CC.pdf}
+	\caption{\label{posterior-CC}The marginalized one- and two-dimensional posterior distributions for hyper-parameters $\{\Mf, \al, \fpbh\}$ in the critical collapse mass function inferred from GWTC-3.
+The blue color denotes the results from the first merger only, while the orange denotes the results from both the first and second mergers.
+The contours represent the $1\sigma$, $2\sigma$ and $3\sigma$ credible regions, respectively.}
+\end{figure}
+
 Using $69$ BBHs from GWTC-3 and performing the hierarchical Bayesian inference, we obtain $\Mf = 10.8^{+3.7}_{-3.6} \Msun$, $\al = 1.0^{+0.2}_{-0.2}$, and $\fpbh = 1.5^{+0.2}_{-0.2} \times 10^{-3}$.
@@
 From \Eq{Rt}, we also infer the local merger rate as $R(t_0) = 49^{+26}_{-16} \gpcyr$.
-The results of local merger rate and abundance of PBHs are consistent with the previous estimations \citep{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+
+\begin{figure}[tbp!]
+	\centering
+	\includegraphics[width=0.5\textwidth]{ratio-CC.pdf}
+	\caption{\label{ratio-CC}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the critical collapse mass function.
+We have fixed the hyper-parameters $\{\Mf, \al, \fpbh\}$ to their best-fit values.}
+\end{figure}
 
@@
 Therefore, the merger history of PBH binaries has a subdominant effect, and this effect can be neglected when evaluating the merger rate of PBH binaries.
-It can also be seen that the Bayes factors for the model with a second merger versus the model with only the first merger, $\mathrm{BF}^{\mathrm{2nd}}_{\mathrm{1st}}$, are all smaller than $3$, indicating the evidence for the second merger is ``not worth more than a bare mention" \citep{BF}.
+It can also be seen that the Bayes factors for the model with a second merger versus the model with only the first merger, $\mathrm{BF}^{\mathrm{2nd}}_{\mathrm{1st}}$, are all smaller than $3$, indicating the evidence for the second merger is ``not worth more than a bare mention" \cite{BF}.
 In this sense, the Bayes factors also imply that the effect of merger history can be ignored.
@@
 Furthermore, for all four mass functions, we infer the abundance of PBH in cold dark matter, $\fpbh$, to be at the order of $\mathcal{O}(10^{-3})$.
-The results of local merger rate and abundance of PBHs are consistent with the previous estimations \citep{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Sasaki:2016jop,Ali-Haimoud:2017rtz,Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
 

### 2022-10-28 latex/paper.tex
update

@@
 The heaviest event, GW190521 \cite{LIGOScientific:2020iuh}, has component masses $m_1 = 85^{+21}_{-14}\Msun$ and $m_2 = 66^{+17}_{-18}\Msun$.
-Both masses lie within upper black hole mass gap originated from pulsation pair-instability supernovae \cite{Marchant_2019}, and current modelling places the lower cutoff of the mass gap at $\sim 50\pm 4\Msun$ \cite{belczynski2016effect,Marchant_2019,Farmer_2019,Farmer:2020xne,Marchant:2020haw}.
+Both masses lie within upper black hole mass gap originated from pulsation pair-instability supernovae \cite{Marchant_2019}, and current modelling places the lower cutoff of the mass gap at $\sim 50\pm 4\Msun$ \cite{Belczynski:2016jno,Marchant_2019,Farmer_2019,Farmer:2020xne,Marchant:2020haw}.
 Even accounting for the uncertainties in modelling, it still implies at least $m_1$ is well within the mass gap and cannot originate directly from a stellar progenitor \cite{Anagnostou:2020umw}.
@@
 
-We first consider a PBH mass function with the log-normal form \cite{Dolgov:1992pu} of
+We first consider a PBH mass function with the log-normal form of \cite{Dolgov:1992pu}
 \e\label{log}
@@
 The posteriors for the hyper-parameters $\Ld = \{M_c, \s, \fpbh\}$ are shown in \Fig{posterior-log}.
-Note that we get a larger value of $M_c$ than that inferred from GWTC-1 in \cite{Wu:2020drm} because GWTC-3 contains heavier BHs than those from GWTC-1.
+Note that we get a larger value of $M_c$ than that inferred from GWTC-1 in Ref.~\cite{Wu:2020drm} because GWTC-3 contains heavier BHs than those from GWTC-1.
 From \Eq{Rt}, we also infer the local merger rate as $R(t_0) = 41^{+16}_{-12} \gpcyr$.
@@
 
-We next consider a PBH mass function with the power-law form \cite{Carr:1975qj} of
+We next consider a PBH mass function with the power-law form of \cite{Carr:1975qj}
 \e\label{power} 
@@
 The posteriors for the hyper-parameters $\Ld = \{\Mmin, \al, \fpbh\}$ are shown in \Fig{posterior-power}.
-Note that we get a smaller value of $\al$ than that inferred from GWTC-1 in \cite{Wu:2020drm} because GWTC-3 contains heavier BHs than those from GWTC-1.
+Note that we get a smaller value of $\al$ than that inferred from GWTC-1 in Ref.~\cite{Wu:2020drm} because GWTC-3 contains heavier BHs than those from GWTC-1.
 From \Eq{Rt}, we also infer the local merger rate as $R(t_0) = 48^{+15}_{-12} \gpcyr$.
@@
 \subsection{Broken power-law mass function}
-We then consider a PBH mass function with the broken power-law form \cite{Deng:2021ezy} of
+We then consider a PBH mass function with the broken power-law form of \cite{Deng:2021ezy}
 \begin{equation}
@@
 The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
-Note that \cite{Deng:2021ezy} obtains quite different results for the broken power-law mass function using GWTC-2 data without accounting for the uncertainties in the measurement of $\vth$.
-Moreover, \cite{Deng:2021ezy} deals with the selection effect of the GW detectors improperly.
+Note that Ref.~\cite{Deng:2021ezy} obtains quite different results for the broken power-law mass function using GWTC-2 data without accounting for the uncertainties in the measurement of $\vth$.
+Moreover, Ref.~\cite{Deng:2021ezy} deals with the selection effect of the GW detectors improperly.
 We emphasize that our results are more robust because we have a comprehensive treatment of the selection effect and measurement uncertainties.
@@
 
-We last consider a PBH mass function with the critical collapse form \cite{Niemeyer:1997mt,Yokoyama:1998xd,Carr:2016hva,Gow:2020cou} of
+We last consider a PBH mass function with the critical collapse form of \cite{Niemeyer:1997mt,Yokoyama:1998xd,Carr:2016hva,Gow:2020cou}
 \e
@@
 We find that $\mathrm{BF}_{\mathrm{PL}}^{\mathrm{LG}}$ has the largest value, indicating that the log-normal mass function can best fit GWTC-3 among the four mass functions considered in this work.
-Our findings contradict the results from \cite{Deng:2021ezy} claiming that the broken power-law mass function can fit better than the log-normal form.
-There are some drawbacks from analyses in \cite{Deng:2021ezy}.
-Firstly, \cite{Deng:2021ezy} neglects the uncertainties in measuring each event's masses and completely ignores the redshift evolution of the merger rate.
-Secondly, \cite{Deng:2021ezy} deals with the selection effect of GW detectors improperly.
-In this sense, we disagree with \cite{Deng:2021ezy} and conclude that the most frequently used log-normal mass function can fit GWTC-3 best among the four mass functions.
+Our findings contradict the results from Ref.~\cite{Deng:2021ezy} claiming that the broken power-law mass function can fit better than the log-normal form.
+There are some drawbacks from analyses in Ref.~\cite{Deng:2021ezy}.
+Firstly, Ref.~\cite{Deng:2021ezy} neglects the uncertainties in measuring each event's masses and completely ignores the redshift evolution of the merger rate.
+Secondly, Ref.~\cite{Deng:2021ezy} deals with the selection effect of GW detectors improperly.
+In this sense, we disagree with Ref.~\cite{Deng:2021ezy} and conclude that the most frequently used log-normal mass function can fit GWTC-3 best among the four mass functions.
 

### 2022-10-28 latex/paper.tex
Updates from Overleaf

@@
 \nc{\discuss}{\textcolor{red}{Add discussion here!}}
-\nc{\red}[1]{\textcolor{red}{#1}}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%% only used in this paper %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \nc{\mH}{\mathcal{H}}
-% \nc{\cs}{c_s^2}
-% \nc{\Sij}[1]{S_{ij}^{(#1)}}
-% \nc{\vi}[1]{v_i^{(#1)}}
-% \nc{\no}{\nonumber}
-% \def\<{\left\langle}
-% \def\>{\right\rangle}
-% \def\ap{\alpha}
-% \def\half{{1\over 2}}
-% \nc{\bk}{\bm{k}}
-% \nc{\bq}{\bm{q}}
-% \nc{\bp}{\bm{p}}
-% \nc{\bl}{\bm{l}}
-% \nc{\bx}{\bm{x}}
-% \nc{\be}{\mathbf{e}}
-% \nc{\mS}{\mathcal{S}}
-% \nc{\te}{\tilde{\eta}}
-% \nc{\tp}{\tilde{p}}
-% \nc{\tk}{\tilde{k}}
-% \nc{\tx}{\tilde{x}}
-% \nc{\tF}{\tilde{F}}
-% \nc{\tA}{\tilde{A}}
-% \nc{\mkpq}{|\bk-\bp-\bq|}
-% \nc{\mpq}{|\bp-\bq|}
-% \nc{\mkp}{|\bk-\bp|}
-% \nc{\mSi}[1]{\mS^{(#1)}({\bk, \eta})}
-% \nc{\vk}{\vec{k}}
-% \nc{\kstar}{k_*}
-% \nc{\xstar}{x_*}
 \nc{\mpbh}{m_{\rm{pbh}}}
@@
 \nc{\Mf}{{M_\mathrm{f}}}
+\nc{\red}[1]{\textcolor{red}{#1}}
+\nc{\yellow}[1]{\textcolor{yellow}{#1}}
+\nc{\green}[1]{\textcolor{green}{#1}}
+\nc{\blue}[1]{\textcolor{blue}{#1}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 PBHs are black holes formed in the very early Universe through the gravitational collapse of the primordial density fluctuations \cite{Hawking:1971ei,Carr:1974nx}.
+Recently, PBHs have attracted considerable attention \cite{Garcia-Bellido:2017mdw,Carr:2017jsz,Germani:2017bcs,Liu:2019rnx,Cai:2019elf,Cai:2019bmk,DeLuca:2020sae,Vaskonen:2020lbd,DeLuca:2020agl,Hutsi:2020sol,Sasaki:2018dmp,Carr:2020gox,Carr:2020xqk,Liu:2021jnw} because they can be not only the sources of LVK detections~\cite{Bird:2016dcv,Sasaki:2016jop}, but also candidates of cold dark matter (CDM) \cite{Carr:2016drx} and the seeds for galaxy formation~\cite{Bean:2002kx,Kawasaki:2012kn}.
 The formation of PBHs would inevitably accompany the production of scalar-induced GWs \cite{Saito:2008jc,Yuan:2019udt,Yuan:2019wwo,Yuan:2019fwv,Chen:2019xse,DeLuca:2019ufz,Bartolo:2018rku,Bartolo:2018evs}.
-PBHs can also be natural candidates of cold dark matter.
+%PBHs can also be natural candidates of cold dark matter (CDM). 
 Recent studies \cite{Chen:2021nxo,Chen:2022fda} show that the BBHs from GWTC-3 are consistent with the PBH scenario, and the abundance of PBH in CDM, $\fpbh$, should be in the order of $\mathcal{O}(10^{-3})$ to explain LVK BBHs.
@@
 		\hline
-		$\fpbh$ & Abundance of PBH in dark matter & log-$\mU(-4, 0)$\\
+		$\fpbh$ & Abundance of PBH in CDM & log-$\mU(-4, 0)$\\
 		\hline
@@
 From \Eq{Rt}, we also infer the local merger rate as $R(t_0) = 41^{+16}_{-12} \gpcyr$.
-The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Sasaki:2016jop,Ali-Haimoud:2017rtz,Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
 
@@
 From \Eq{Rt}, we also infer the local merger rate as $R(t_0) = 48^{+15}_{-12} \gpcyr$.
-The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Sasaki:2016jop,Ali-Haimoud:2017rtz,Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
 
@@
 From \Eq{Rt}, we also infer the local merger rate as $R(t_0) = 46^{+15}_{-11} \gpcyr$.
-The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Sasaki:2016jop,Ali-Haimoud:2017rtz,Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
 Note that Ref.~\cite{Deng:2021ezy} obtains quite different results for the broken power-law mass function using GWTC-2 data without accounting for the uncertainties in the measurement of $\vth$.
@@
 From \Eq{Rt}, we also infer the local merger rate as $R(t_0) = 49^{+26}_{-16} \gpcyr$.
-The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Sasaki:2016jop,Ali-Haimoud:2017rtz,Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
 
@@
 
-Furthermore, for all four mass functions, we infer the abundance of PBH in cold dark matter, $\fpbh$, to be at the order of $\mathcal{O}(10^{-3})$.
+Furthermore, for all four mass functions, we infer the abundance of PBH in CDM, $\fpbh$, to be at the order of $\mathcal{O}(10^{-3})$.
 The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Sasaki:2016jop,Ali-Haimoud:2017rtz,Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
@@
 	\caption{\label{table:BF}Summary of the key results for the log-normal (LN), power-law (PL), broken power-law (BPL), and critical collapse (CC) mass functions.
-The first row, $\mathrm{BF}^{\mathrm{2nd}}_{\mathrm{1st}}$, shows the Bayes factors for the model with 2nd merger versus the model with only 1st merger; the second row, $\mathrm{BF}_{\mathrm{PL}}$, shows the Bayes factors for the model with different PBH mass function versus the model with the power-law PBH mass function by accounting for the second merger effect; the third row, $\fpbh$, shows the abundance of PBH in dark matter inferred from different models by accounting for the second merger effect; the last row, $R_2/R_1$, shows the merger rate ratio between the second merger and the first merger.}
+The first row, $\mathrm{BF}^{\mathrm{2nd}}_{\mathrm{1st}}$, shows the Bayes factors for the model with 2nd merger versus the model with only 1st merger; the second row, $\mathrm{BF}_{\mathrm{PL}}$, shows the Bayes factors for the model with different PBH mass function versus the model with the power-law PBH mass function by accounting for the second merger effect; the third row, $\fpbh$, shows the abundance of PBH in CDM inferred from different models by accounting for the second merger effect; the last row, $R_2/R_1$, shows the merger rate ratio between the second merger and the first merger.}
 \end{table}

### 2022-10-31 latex/paper.tex
update
Updates from Overleaf

@@
 In this work, we constrain the merger history of PBH binaries using the gravitational wave events from the third Gravitational-Wave Transient Catalog (GWTC-3).
-Considering four commonly used PBH mass functions,
-namely the log-normal, power-law, broken power-law, and critical collapse forms, we find that the multi-merger processes make a subdominant contribution to the total merger rate.
+Considering four commonly used PBH mass functions, namely the log-normal, power-law, broken power-law, and critical collapse forms, we find that the multi-merger processes make a subdominant contribution to the total merger rate.
 Therefore, the effect of merger history can be safely ignored when estimating the merger rate of PBH binaries.
@@
 PBHs are black holes formed in the very early Universe through the gravitational collapse of the primordial density fluctuations \cite{Hawking:1971ei,Carr:1974nx}.
-Recently, PBHs have attracted considerable attention \cite{Garcia-Bellido:2017mdw,Carr:2017jsz,Germani:2017bcs,Liu:2019rnx,Cai:2019elf,Cai:2019bmk,DeLuca:2020sae,Vaskonen:2020lbd,DeLuca:2020agl,Hutsi:2020sol,Sasaki:2018dmp,Carr:2020gox,Carr:2020xqk,Liu:2021jnw} because they can be not only the sources of LVK detections~\cite{Bird:2016dcv,Sasaki:2016jop}, but also candidates of cold dark matter (CDM) \cite{Carr:2016drx} and the seeds for galaxy formation~\cite{Bean:2002kx,Kawasaki:2012kn}.
+Recently, PBHs have attracted considerable attention \cite{Garcia-Bellido:2017mdw,Carr:2017jsz,Germani:2017bcs,Liu:2019rnx,Cai:2019elf,Cai:2019bmk,DeLuca:2020sae,Vaskonen:2020lbd,DeLuca:2020agl,Hutsi:2020sol,Sasaki:2018dmp,Carr:2020gox,Carr:2020xqk,Liu:2021jnw,Wang:2022nml} because they can be not only the sources of LVK detections~\cite{Bird:2016dcv,Sasaki:2016jop}, but also candidates of cold dark matter (CDM) \cite{Carr:2016drx} and the seeds for galaxy formation~\cite{Bean:2002kx,Kawasaki:2012kn}.
 The formation of PBHs would inevitably accompany the production of scalar-induced GWs \cite{Saito:2008jc,Yuan:2019udt,Yuan:2019wwo,Yuan:2019fwv,Chen:2019xse,DeLuca:2019ufz,Bartolo:2018rku,Bartolo:2018evs}.

### 2022-11-03 latex/paper.tex
update

--- 2022-10-28 latex/paper.tex
@@
 PBHs are black holes formed in the very early Universe through the gravitational collapse of the primordial density fluctuations \cite{Hawking:1971ei,Carr:1974nx}.
-Recently, PBHs have attracted considerable attention \cite{Garcia-Bellido:2017mdw,Carr:2017jsz,Germani:2017bcs,Liu:2019rnx,Cai:2019elf,Cai:2019bmk,DeLuca:2020sae,Vaskonen:2020lbd,DeLuca:2020agl,Hutsi:2020sol,Sasaki:2018dmp,Carr:2020gox,Carr:2020xqk,Liu:2021jnw} because they can be not only the sources of LVK detections~\cite{Bird:2016dcv,Sasaki:2016jop}, but also candidates of cold dark matter (CDM) \cite{Carr:2016drx} and the seeds for galaxy formation~\cite{Bean:2002kx,Kawasaki:2012kn}.
+Recently, PBHs have attracted considerable attention \cite{Garcia-Bellido:2017mdw,Carr:2017jsz,Germani:2017bcs,Liu:2019rnx,Cai:2019elf,Cai:2019bmk,DeLuca:2020sae,Vaskonen:2020lbd,DeLuca:2020agl,Hutsi:2020sol,Sasaki:2018dmp,Carr:2020gox,Carr:2020xqk,Liu:2021jnw,Franciolini:2022tfm} because they can be not only the sources of LVK detections~\cite{Bird:2016dcv,Sasaki:2016jop}, but also candidates of cold dark matter (CDM) \cite{Carr:2016drx} and the seeds for galaxy formation~\cite{Bean:2002kx,Kawasaki:2012kn}.
 The formation of PBHs would inevitably accompany the production of scalar-induced GWs \cite{Saito:2008jc,Yuan:2019udt,Yuan:2019wwo,Yuan:2019fwv,Chen:2019xse,DeLuca:2019ufz,Bartolo:2018rku,Bartolo:2018evs}.

### 2022-11-03 latex/paper.tex

--- 2022-10-28 latex/paper.tex
@@
 PBHs are black holes formed in the very early Universe through the gravitational collapse of the primordial density fluctuations \cite{Hawking:1971ei,Carr:1974nx}.
-Recently, PBHs have attracted considerable attention \cite{Garcia-Bellido:2017mdw,Carr:2017jsz,Germani:2017bcs,Liu:2019rnx,Cai:2019elf,Cai:2019bmk,DeLuca:2020sae,Vaskonen:2020lbd,DeLuca:2020agl,Hutsi:2020sol,Sasaki:2018dmp,Carr:2020gox,Carr:2020xqk,Liu:2021jnw} because they can be not only the sources of LVK detections~\cite{Bird:2016dcv,Sasaki:2016jop}, but also candidates of cold dark matter (CDM) \cite{Carr:2016drx} and the seeds for galaxy formation~\cite{Bean:2002kx,Kawasaki:2012kn}.
+Recently, PBHs have attracted considerable attention \cite{Garcia-Bellido:2017mdw,Carr:2017jsz,Germani:2017bcs,Liu:2019rnx,Cai:2019elf,Cai:2019bmk,DeLuca:2020sae,Vaskonen:2020lbd,DeLuca:2020agl,Hutsi:2020sol,Sasaki:2018dmp,Carr:2020gox,Carr:2020xqk,Liu:2021jnw,Wang:2022nml,Franciolini:2022tfm} because they can be not only the sources of LVK detections~\cite{Bird:2016dcv,Sasaki:2016jop}, but also candidates of cold dark matter (CDM) \cite{Carr:2016drx} and the seeds for galaxy formation~\cite{Bean:2002kx,Kawasaki:2012kn}.
 The formation of PBHs would inevitably accompany the production of scalar-induced GWs \cite{Saito:2008jc,Yuan:2019udt,Yuan:2019wwo,Yuan:2019fwv,Chen:2019xse,DeLuca:2019ufz,Bartolo:2018rku,Bartolo:2018evs}.
-%PBHs can also be natural candidates of cold dark matter (CDM). 
 Recent studies \cite{Chen:2021nxo,Chen:2022fda} show that the BBHs from GWTC-3 are consistent with the PBH scenario, and the abundance of PBH in CDM, $\fpbh$, should be in the order of $\mathcal{O}(10^{-3})$ to explain LVK BBHs.

### 2022-12-12 code/merger_rate.jl
update

@@ -1,12 +1,7 @@
-using Trapz, MathLink, SpecialFunctions
+using Trapz, SpecialFunctions
 
 const m_min = 1e-1
 const m_max = 1e3
-
-# # using beta function from mathematica
-# beta0 = W"Beta"(W"z", W"a", W"b")
-# beta(z, a, b) = weval(beta0; z=z, a=a, b=b)
-
 
 # log-normal mass function 
 function mergerRateDensity1st0_log(mc, σc, log_fpbh, i, j)
@@ -80,7 +75,6 @@ mergerRateDensity2nd_power(α, M, log_fpbh, i, j) = mergerRateDensity2nd0_power.
 
 
 # critical collapse
-
 function mergerRateDensity1st0_CC(α, Mf, log_fpbh, i, j)
     fpbh = 10^log_fpbh
     t1 = (i * j)^(-34 / 37) * 1.32e6 * exp(-(i / Mf)^α - (j / Mf)^α) * i^α * j^α * (i + j)^(36 / 37) * Mf^(-(21 / 37) - 2 * α) * α^2

### 2023-04-02 latex/paper.tex
update

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Reintroduced the \received and \accepted commands from AASTeX v5.2
-%\received{}
-%\revised{}
-%\accepted{}
-%\published{}
-%% Command to document which AAS Journal the manuscript was submitted to.
-%% Adds "Submitted to " the arguement.
-%\submitjournal{ApJ}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
-\title{Constrain the Merger History of Primordial-Black-Hole Binaries from GWTC-3}
+\title{Constraining the Merger History of Primordial-Black-Hole Binaries from GWTC-3}
 
@@
 \author{Zhi-Qiang~You}
-\email{zhiqiang.you@bnu.edu.cn}
+\email{Corresponding author: zhiqiang.you@bnu.edu.cn}
 \affiliation{Department of Astronomy, Beijing Normal University, Beijing 100875, China}
@@
 Both masses lie within upper black hole mass gap originated from pulsation pair-instability supernovae \cite{Marchant_2019}, and current modelling places the lower cutoff of the mass gap at $\sim 50\pm 4\Msun$ \cite{Belczynski:2016jno,Marchant_2019,Farmer_2019,Farmer:2020xne,Marchant:2020haw}.
-Even accounting for the uncertainties in modelling, it still implies at least $m_1$ is well within the mass gap and cannot originate directly from a stellar progenitor \cite{Anagnostou:2020umw}.
+Even accounting for the statistical uncertainties, it still implies at least $m_1$ is well within the mass gap and cannot originate directly from a stellar progenitor \cite{Anagnostou:2020tta}.
 Therefore, the heavy event GW190521 greatly challenges the stellar evolution scenario of astrophysical black holes.
@@
 Recently, PBHs have attracted considerable attention \cite{Garcia-Bellido:2017mdw,Carr:2017jsz,Germani:2017bcs,Liu:2019rnx,Cai:2019elf,Cai:2019bmk,DeLuca:2020sae,Vaskonen:2020lbd,DeLuca:2020agl,Hutsi:2020sol,Sasaki:2018dmp,Carr:2020gox,Carr:2020xqk,Liu:2021jnw,Wang:2022nml,Franciolini:2022tfm} because they can be not only the sources of LVK detections~\cite{Bird:2016dcv,Sasaki:2016jop}, but also candidates of cold dark matter (CDM) \cite{Carr:2016drx} and the seeds for galaxy formation~\cite{Bean:2002kx,Kawasaki:2012kn}.
-The formation of PBHs would inevitably accompany the production of scalar-induced GWs \cite{Saito:2008jc,Yuan:2019udt,Yuan:2019wwo,Yuan:2019fwv,Chen:2019xse,DeLuca:2019ufz,Bartolo:2018rku,Bartolo:2018evs}.
+The formation of PBHs would inevitably accompany the production of scalar-induced GWs \cite{Saito:2008jc,Cai:2018dig,Yuan:2019udt,Yuan:2019wwo,Yuan:2019fwv,Chen:2019xse,DeLuca:2019ufz,Bartolo:2018rku,Bartolo:2018evs}.
 Recent studies \cite{Chen:2021nxo,Chen:2022fda} show that the BBHs from GWTC-3 are consistent with the PBH scenario, and the abundance of PBH in CDM, $\fpbh$, should be in the order of $\mathcal{O}(10^{-3})$ to explain LVK BBHs.
@@
 We extend the analyses of Ref.~\cite{Wu:2020drm} in several aspects.
-Firstly, we use GWTC-3, which expands GWTC-1 with almost six times more BBH events.
+Firstly, we use a purified subset of GWTC-3, which expands GWTC-1 with almost six times more BBH events.
 The GWTC-3 events expand the mass and redshift coverage and can alleviate the statistical bias by including significantly more BBHs.
@@
 Lastly, we consider the redshift distribution of the merger rate that is ignored in Ref.~\cite{Wu:2020drm}.
+The aforementioned reasons have inspired us to explore the possibility that the heavy black holes detected by LVK have been formed, at least in part, through second-generation mergers.
+This is because the second-merger process has the potential to increase the mass distribution to a higher value.
+A precise assessment of the influence of second-generation mergers on mass distribution demands a meticulous analysis of the data, as has been conducted in this study.
 
@@
 We can now estimate the merger rate densities of PBH binaries by considering the merger history effect.
-We assume that PBHs are randomly distributed in the early Universe when they decouple from the cosmic background evolution \cite{Nakamura:1997sm,Sasaki:2016jop,Ali-Haimoud:2017rtz}.
+We assume that PBHs are randomly distributed following a spatial Poisson distribution in the early Universe when they decouple from the cosmic background evolution \cite{Nakamura:1997sm,Sasaki:2016jop,Ali-Haimoud:2017rtz}.
 The two nearest PBHs would attract each other because of the gravitational interactions.
-These two PBHs would obtain the angular momentum from the torque of other PBHs and form a PBH binary.
+These two PBHs would obtain the angular momentum from the torque of other PBHs and form a PBH binary after decoupling from the cosmic expansion.
 The binary would emit gravitational radiations and eventually merge.
@@
 \q 
-where
+where $m_i$ and $m_j$ are the masses of the merging binary, $m_l$ is the mass of the third black hole that is closest to the merging binary, and
 \e 
@@
 \q
+Here, $t$ is the cosmic time, and $t_0$ is the present cosmic time.
 Similarly, the merger rate density from second-merger process, $\cR_2(t, m_i, m_j)$, is given by \cite{Liu:2019rnx}
@@
 \q 
-where
+where $m_e$ is the mass of the fourth black hole that is closest to the merging binary, and
 \e 
@@
 \q
-We only consider the effect of merger history up to the second-merger process.
+We only consider the effect of merger history up to the second-merger process. We have verified that the fraction of the third merger rate over the second merger rate is less than $0.005$.
 Therefore the total merger rate density, $\cR(t, m_i, m_j)$, of PBH binaries at cosmic time $t$ with masses $m_i$ and $m_j$ is
@@
 		\multicolumn{3}{c}{Broken Power-law PBH mass function} \\[1pt]
-		$M_*$ & Peak mass in $\Msun$. & $\mU(3, 15)$\\
-		$\al_1$ & First power-law index. & $\mU(0, 15)$\\
-		$\al_2$ & Second power-law index. & $\mU(1, 3)$\\
+		$m_*$ & Peak mass in $\Msun$. & $\mU(5, 50)$\\
+		$\al_1$ & First power-law index. & $\mU(0, 3)$\\
+		$\al_2$ & Second power-law index. & $\mU(1, 10)$\\
 		\hline
@@
 where $P_{\text{det}}(\theta)$ is the detection probability that depends on the source parameters $\theta$.
-In practice, we use the simulated injections \cite{ligo_scientific_collaboration_and_virgo_2021_5546676} to estimate $\xi(\Ld)$, and \Eq{xi} can be approximated by a Monte Carlo integral over found injections \cite{LIGOScientific:2021psn}
+In practice, we use the simulated injections \cite{ligo_scientific_collaboration_and_virgo_2021_5546676} to estimate $\xi(\Ld)$, and \Eq{xi} can be approximated by a Monte Carlo integral over found injections \cite{KAGRA:2021duu}
 \begin{equation}
@@
 We use the GW events from GWTC-3 by discarding events with false alarm rate larger than 1 yr$^{-1}$ and events with the secondary component mass smaller than $3\Msun$ to avoid contamination from putative events involving neutron stars following Ref.~\cite{DeLuca:2021wjr}.
-A total of $69$ GW events from GWTC-3 meet this criteria and the posterior samples of these BBHs are publicly available from Ref.~\cite{ligo_scientific_collaboration_and_virgo_2021_5655785}.
+A total of $69$ GW events from GWTC-3 meet these criteria and the posterior samples of these BBHs are publicly available from Ref.~\cite{ligo_scientific_collaboration_and_virgo_2021_5655785}.
 
@@
 The blue color denotes the results from the first merger only, while the orange denotes the results from both the first and second mergers.
-The contours represent the $1\sigma$, $2\sigma$ and $3\sigma$ credible regions, respectively.}
+The contours represent the $1\sigma$, $2\sigma$, and $3\sigma$ credible regions, respectively.}
 \end{figure}
@@
 From \Eq{Rt}, we also infer the local merger rate as $R(t_0) = 41^{+16}_{-12} \gpcyr$.
-The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Sasaki:2016jop,Ali-Haimoud:2017rtz,Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Sasaki:2016jop,Ali-Haimoud:2017rtz,Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda,Zheng:2022wqo}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
 
@@
 	\includegraphics[width=\linewidth]{ratio-log.pdf}
-	\caption{\label{ratio-log}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the log-normal mass function.
+	\caption{\label{ratio-log}The ratio of merger rate density from the second merger to that from the first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the log-normal mass function.
 We have fixed the hyper-parameters $\{M_c, \s, \fpbh\}$ to their best-fit values.}
@@
 
-In \Fig{ratio-log}, we show the ratio of merger rate density from second merger to the one from first merger, namely $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing the hyper-parameters $\{M_c, \s, \fpbh\}$ to their best-fit values.
+In \Fig{ratio-log}, we show the ratio of merger rate density from the second merger to the one from the first merger, namely $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing the hyper-parameters $\{M_c, \s, \fpbh\}$ to their best-fit values.
 It can be seen that the second merger provides more contribution to the total merger rate density as component mass increases.
-Even though $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$ can reach as high as $\gtrsim 10\%$, the ratio of merger rate from second merger to that from first merger is $R_2(t_0)/R_1(t_0) = 1.0^{+0.2}_{-0.1}\%$ and is negligible.
+Even though $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$ can reach as high as $\gtrsim 10\%$, the ratio of merger rate from second merger to that from the first merger is $R_2(t_0)/R_1(t_0) = 1.0^{+0.2}_{-0.1}\%$ and is negligible.
 This is because the major contribution to the merger rate is from the masses less than $50\Msun$, and the correction is negligible in this mass range.
@@
 where $\Mmin$ is the lower-mass cut-off such that $m>\Mmin$, and $\al>1$ is the power-law index. 
-The power-law mass function can typically result from a broad or flat power spectrum of the curvature perturbations \cite{DeLuca:2020ioi} during radiation dominated era \cite{Carr:2016drx,Carr:2017jsz}.
+The power-law mass function can typically result from a broad or flat power spectrum of the curvature perturbations \cite{DeLuca:2020ioi} during radiation-dominated era \cite{Carr:2016drx,Carr:2017jsz}.
 The hyper-parameters are $\Ld = \{\Mmin, \al, \fpbh\}$ in this case. 
@@
 From \Eq{Rt}, we also infer the local merger rate as $R(t_0) = 48^{+15}_{-12} \gpcyr$.
-The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Sasaki:2016jop,Ali-Haimoud:2017rtz,Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+The results of the local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Sasaki:2016jop,Ali-Haimoud:2017rtz,Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda,Zheng:2022wqo}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
 
@@
 	\includegraphics[width=0.5\textwidth]{ratio-power.pdf}
-	\caption{\label{ratio-power}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the power-law mass function.
+	\caption{\label{ratio-power}The ratio of merger rate density from the second merger to that from the first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the power-law mass function.
 We have fixed the hyper-parameters $\{\Mmin, \al, \fpbh\}$ to their best-fit values.}
@@
 
-In \Fig{ratio-power}, we show the ratio of merger rate density from second merger to the one from first merger, namely $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing the hyper-parameters $\{\Mmin, \al, \fpbh\}$ to their best-fit values.
+In \Fig{ratio-power}, we show the ratio of merger rate density from the second merger to the one from the first merger, namely $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing the hyper-parameters $\{\Mmin, \al, \fpbh\}$ to their best-fit values.
 It can be seen that the second merger provides more contribution to the total merger rate density as component mass increases.
-Even though $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$ can reach as high as $\gtrsim 10\%$, the ratio of merger rate from second merger to that from first merger is $R_2(t_0)/R_1(t_0) = 0.9^{+0.1}_{-0.1}\%$ and is negligible.
+Even though $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$ can reach as high as $\gtrsim 10\%$, the ratio of merger rate from second merger to that from the first merger is $R_2(t_0)/R_1(t_0) = 0.9^{+0.1}_{-0.1}\%$ and is negligible.
 This is because the major contribution to the merger rate is from the masses less than $50\Msun$, and the correction is negligible in this mass range.
@@
 \begin{equation}
-	P(m)= \left(\frac{m_*}{\alpha_1+1}-\frac{m_*}{\alpha_2-1}\right)^{-1} \begin{cases} (\frac{m}{m_*})^{\alpha_1}, & m<m_* \\ (\frac{m}{m_*})^{-\alpha_2}, & m>m_*\end{cases},
+	P(m)= \left(\frac{m_*}{\alpha_1+1} + \frac{m_*}{\alpha_2-1}\right)^{-1} \begin{cases} (\frac{m}{m_*})^{\alpha_1}, & m<m_* \\ (\frac{m}{m_*})^{-\alpha_2}, & m>m_*\end{cases},
 \end{equation}
@@
 The blue color denotes the results from the first merger only, while the orange denotes the results from both the first and second mergers.
-The contours represent the $1\sigma$, $2\sigma$ and $3\sigma$ credible regions, respectively.}
+The contours represent the $1\sigma$, $2\sigma$, and $3\sigma$ credible regions, respectively.}
 \end{figure}
 
-Using $69$ BBHs from GWTC-3 and performing the hierarchical Bayesian inference, we obtain $m_* = 8.6^{+2.1}_{-1.3} \Msun$, $\al_1 = 5.6^{+7.1}_{-3.8}$, $\al_2 = 2.0^{+0.2}_{-0.2}$, and $\fpbh = 2.2^{+0.3}_{-0.4} \times 10^{-3}$.
+Using $69$ BBHs from GWTC-3 and performing the hierarchical Bayesian inference, we obtain $m_* = 31.1^{+1.8}_{-2.1} \Msun$, $\al_1 = 0.54^{+0.08}_{-0.06}$, $\al_2 = 5.6^{+0.9}_{-0.8}$, and $\fpbh = 0.9^{+0.1}_{-0.1} \times 10^{-3}$.
 The posteriors for the hyper-parameters $\Ld = \{m_*, \al_1, \al_2, \fpbh\}$ are shown in \Fig{posterior-bpower}.
 From \Eq{Rt}, we also infer the local merger rate as $R(t_0) = 46^{+15}_{-11} \gpcyr$.
-The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Sasaki:2016jop,Ali-Haimoud:2017rtz,Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
-Note that Ref.~\cite{Deng:2021ezy} obtains quite different results for the broken power-law mass function using GWTC-2 data without accounting for the uncertainties in the measurement of $\vth$.
+The results of the local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Sasaki:2016jop,Ali-Haimoud:2017rtz,Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda,Zheng:2022wqo}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+We also confirm that there is a mass peak at $m_* \sim 34 \Msun$ as was found in  Ref.~\cite{Deng:2021ezy}.
+
+% obtains quite different results for the broken power-law mass function using GWTC-2 data without accounting for the uncertainties in the measurement of $\vth$.
 Moreover, Ref.~\cite{Deng:2021ezy} deals with the selection effect of the GW detectors improperly.
 We emphasize that our results are more robust because we have a comprehensive treatment of the selection effect and measurement uncertainties.
-Nevertheless, as expected, our results of the broken power-law mass function are fully consistent with the results of the power-law case.
 
@@
 	\includegraphics[width=0.5\textwidth]{ratio-bpower.pdf}
-	\caption{\label{ratio-bpower}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the broken power-law mass function.
+	\caption{\label{ratio-bpower}The ratio of merger rate density from the second merger to that from the first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the broken power-law mass function.
 We have fixed the hyper-parameters $\{m_*, \al_1, \al_2, \fpbh\}$ to their best-fit values.}
@@
 
-In \Fig{ratio-bpower}, we show the ratio of merger rate density from second merger to the one from first merger, namely $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing the hyper-parameters $\{m_*, \al_1, \al_2, \fpbh\}$ to their best-fit values.
+In \Fig{ratio-bpower}, we show the ratio of merger rate density from the second merger to the one from the first merger, namely $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing the hyper-parameters $\{m_*, \al_1, \al_2, \fpbh\}$ to their best-fit values.
 It can be seen that the second merger provides more contribution to the total merger rate density as component mass increases.
-Even though $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$ can reach as high as $\gtrsim 10\%$, the ratio of merger rate from second merger to that from first merger is $R_2(t_0)/R_1(t_0) = 0.9^{+0.3}_{-0.1}\%$ and is negligible.
+Even though $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$ can reach as high as $\gtrsim 10\%$, the ratio of merger rate from second merger to that from the first merger is $R_2(t_0)/R_1(t_0) = 0.9^{+0.3}_{-0.1}\%$ and is negligible.
 This is because the major contribution to the merger rate is from the masses less than $50\Msun$, and the correction is negligible in this mass range.
@@
 From \Eq{Rt}, we also infer the local merger rate as $R(t_0) = 49^{+26}_{-16} \gpcyr$.
-The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Sasaki:2016jop,Ali-Haimoud:2017rtz,Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+The results of the local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Sasaki:2016jop,Ali-Haimoud:2017rtz,Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda,Zheng:2022wqo}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
 
@@
 	\includegraphics[width=0.5\textwidth]{ratio-CC.pdf}
-	\caption{\label{ratio-CC}The ratio of merger rate density from second merger to that from first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the critical collapse mass function.
+	\caption{\label{ratio-CC}The ratio of merger rate density from the second merger to that from the first merger, $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, as a function of component masses for the critical collapse mass function.
 We have fixed the hyper-parameters $\{\Mf, \al, \fpbh\}$ to their best-fit values.}
@@
 
-In \Fig{ratio-CC}, we show the ratio of merger rate density from second merger to the one from first merger, namely $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing the hyper-parameters $\{\Mf, \al, \fpbh\}$ to their best-fit values.
+In \Fig{ratio-CC}, we show the ratio of merger rate density from the second merger to the one from the first merger, namely $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$, by fixing the hyper-parameters $\{\Mf, \al, \fpbh\}$ to their best-fit values.
 It can be seen that the second merger provides more contribution to the total merger rate density as component mass increases.
-Even though $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$ can reach as high as $\gtrsim 10\%$, the ratio of merger rate from second merger to that from first merger is $R_2(t_0)/R_1(t_0) = 2.2^{+1.3}_{-0.1}\%$ and is negligible.
+Even though $\cR_2(t_0, m_1, m_2)/\cR_1(t_0, m_1, m_2)$ can reach as high as $\gtrsim 10\%$, the ratio of merger rate from second merger to that from the first merger is $R_2(t_0)/R_1(t_0) = 2.2^{+1.3}_{-0.1}\%$ and is negligible.
 This is because the major contribution to the merger rate is from the masses less than $50\Msun$, and the correction is negligible in this mass range.
@@
 It can be seen that the contribution of the merger rate from the second merger to the total merger rate is less than $5\%$.
-Therefore, the merger history of PBH binaries has a subdominant effect, and this effect can be neglected when evaluating the merger rate of PBH binaries.
+Therefore, the higher-order hierarchical merger after the first one has a subdominant effect, and this effect can be neglected when evaluating the merger rate of PBH binaries.
 It can also be seen that the Bayes factors for the model with a second merger versus the model with only the first merger, $\mathrm{BF}^{\mathrm{2nd}}_{\mathrm{1st}}$, are all smaller than $3$, indicating the evidence for the second merger is ``not worth more than a bare mention" \cite{BF}.
@@
 Furthermore, for all four mass functions, we infer the abundance of PBH in CDM, $\fpbh$, to be at the order of $\mathcal{O}(10^{-3})$.
-The results of local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Sasaki:2016jop,Ali-Haimoud:2017rtz,Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+The results of the local merger rate and abundance of PBHs are consistent with the previous estimations \cite{Sasaki:2016jop,Ali-Haimoud:2017rtz,Chen:2018czv,Chen:2018rzo,Chen:2019irf,Wu:2020drm,Chen:2021nxo,Chen:2022fda,Zheng:2022wqo}, confirming that CDM cannot be dominated by the stellar-mass PBHs.
+PBHs cluster at the late time of the Universe may play an important role in the merger rate.
+For all of the four PBH mass functions, we always have $f_{\mathrm{pbh}} \lesssim 3\times10^{-3}$.
+Therefore, according to Ref.~\cite{Hutsi:2020sol}, this effect can be safely ignored.
 
@@
 		\hline
-		$\mathrm{BF}^{\mathrm{2nd}}_{\mathrm{1st}}$ & $0.9$ & $0.4$ & $0.69$ & $1.2$ \\
-		$\mathrm{BF}_{\mathrm{PL}}$ & $166$ & $1$ & $2$ & $139$ \\
-		$10^{3}\fpbh$ & $1.8^{+0.3}_{-0.3}$ & $2.3^{+0.3}_{-0.3}$ & $2.2^{+0.3}_{-0.4}$ & $1.5^{+0.2}_{-0.2}$ \\
-		$10^{2}R_2/R_1$ & $1.0^{+0.2}_{-0.1}$ & $0.9^{+0.1}_{-0.1}$ & $0.9^{+0.3}_{-0.1}$ & $2.2^{+1.3}_{-0.5}$ \\
+		$\mathrm{BF}^{\mathrm{2nd}}_{\mathrm{1st}}$ & $0.9$ & $0.4$ & $0.89$ & $1.2$ \\
+		$\mathrm{BF}_{\mathrm{PL}}$ & $166$ & $1$ & $49$ & $139$ \\
+		$10^{3}\fpbh$ & $1.8^{+0.3}_{-0.3}$ & $2.3^{+0.3}_{-0.3}$ & $0.9^{+0.1}_{-0.1}$ & $1.5^{+0.2}_{-0.2}$ \\
+		$10^{2}R_2/R_1$ & $1.0^{+0.2}_{-0.1}$ & $0.9^{+0.1}_{-0.1}$ & $1.3^{+0.3}_{-0.1}$ & $2.2^{+1.3}_{-0.5}$ \\
 		\hline
@@
 \begin{acknowledgments}
-% We thank the referee for providing constructive comments and suggestions to improve the quality of this paper. 
-We would also like to thank Xingjiang Zhu, Xiao-Jin Liu, Shen-Shi Du, and Zhu Yi for useful discussions.
-Z.-C.C. is supported by the China Postdoctoral Science Foundation Fellowship No.~2022M710429.
+We thank the referee for providing constructive comments and suggestions to improve the quality of this paper. 
+We would also like to thank Xingjiang Zhu, Xiao-Jin Liu, Shen-Shi Du, and Zhu Yi for the useful discussions.
+ZCC is supported by the National Natural Science Foundation of China (Grant No.~12247176 and No.~12247112) and the China Postdoctoral Science Foundation Fellowship No.~2022M710429.
+ZQY is supported by the China Postdoctoral Science Foundation Fellowship No.~2022M720482.
+LL is supported by the National Natural Science Foundation of China (Grant No.~12247112 and No.~12247176).
+
 This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center (\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the LIGO Scientific Collaboration, the Virgo Collaboration, and the KAGRA Collaboration.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %%% references %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \bibliographystyle{apsrev4-2}
 \bibliography{ref}

### 2023-04-02 latex/reply.tex
update

@@
 \documentclass[
-%a4paper,       % letterpaper, a4paper, a5paper
-%10pt,              % 10pt, 11pt, 12pt
-%reprint,           % journal's actual layout
 preprint,          % 12pt, single-column
@@
 prl,               % prl, pra, prb, prc, prd, pre, prstab
-%showpacs,          % make PACS codes appear
 notitlepage,       % control appearance of title page
@@
 floatfix,          % process floats as early as possible
-%showkeys,          % option to make keywords appear
-%titlepage,         %
-%eqsecnum,          % number equations by section
 nofootinbib,
@@
 
+\usepackage{bm}         % \bm{<text>} Bold math symbols
 \usepackage{amsmath}
@@
 ]{hyperref}             % create hyperlinks
+\usepackage{color}    
+\newcommand{\nc}{\newcommand*} 
+\nc{\fpbh}{f_{\mathrm{pbh}}}    % f_pbh
+\nc{\Mmin}{{M_{\mathrm{min}}}}
+\nc{\Mf}{{M_\mathrm{f}}}
+\nc{\al}{\alpha}
+\newcommand{\red}[1]{\textcolor{red}{#1}}
+
+\newcommand{\cR}{\mathcal{R}}
 
@@
 
-Dear Editor and Referee, \\
+\noindent Response to Report of the Referee -- DY12741/Liu\\
 
-We thank the referee for careful reading of our manuscript and for his/her insightful suggestions and comments. 
-We enclose our reply to comments in the following part of our reply. 
+We would like to thank the referee for the valuable comments and suggestions. We have considered all of them and revised the manuscript accordingly.
+Our responses to the comments are given below.
+
 \begin{enumerate}
-	\item The power-law and log-normal mass functions are commonly used in literature and are worthwhile to investigate because they are well motivated by the formation mechanisms of primordial black holes (PBHs).
-The mass function of PBHs is closely related to shape of primordial power spectrum when PBHs are formed.
-It is believed that power-law and log-normal mass functions can be representatives of quite a large class of mass distributions.
-We added corresponding explanations after Eq.(23) and Eq.(26), respectively, to address the motivations of using these two mass functions.
 
-    \item The text after Eq.~(4) to the end of Section 2 was completely rewritten as suggested by the referee.
-We added some necessary intermediate steps and explanations to make the derivations much more readable.
+\item \red{\it My first general question is whether it is really necessary to perform a detailed analysis to know that the second-generation merger can be neglected?
+To me the neglected contribution is definite from a back-of-the-envelope calculation, given the current knowledge that the fraction of PBH in dark matter $f_{pbh}$ is O($10^{-3}$).
+I read with interest the authors' previous event rate modeling paper ref.
+21 that the current manuscript heavily relies on.
+Using the binary formation criteria Eq.
+1 of ref.
+21, that $x^3$ $n_{pbh}$ should $<$ $f_{pbh}$ (I reckon $x^3$ the occupation volume of a PBH and $1/n_{pbh}$ is the average volume occupied by a PBH), I estimate a fraction of $O(f_{pbh})$ formed binaries.
+The reasoning is that I made the (crude) assumption that $x^3$ is uniformly distributed within $[0, 1/n_{pbh}]$, thus only a fraction $f_{pbh}$ satisfies the condition.
+A more practical distribution for x was also given by ref.
+21 and should give a more precise estimation.
+This work concluded the second-generation merger contributes $10^{-2}$ to the first-generation, not $10^{-3}$, but the crude estimation for x and assuming a single-mass may cause the difference.
+Anyway, my point is that the authors may be able to estimate the order of magnitude of second-generation mergers, given a nice analytical model of merger rate and knowledge about $f_{pbh}$.
+Does this make sense?
+Putting it in another way, in the section of the assessment, I was asked to evaluate whether this paper yields significant new physics results to warrant publication, so I'm trying to understand how innovative this manuscript's result is.
+If the numerical analysis performed by this manuscript can offer more insights about the second-generation merger (not just confirming what was expected with more precise digits), I would consider the results more innovative.}
 
-    \item We added units to the labels of figures and enlarge labels' font size. Furthermore, more explanations were added to the captions.
+First of all, we respectfully disagree with some points of the referee as we believe there may be some misunderstandings.
+Eq.~1 of ref.~21 is the condition for black holes to form binaries, but not the condition to form second-generation binaries.
+The fraction of the second-generation merger rate over the first-generation merger rate should be given by Eq.~(7) over Eq.~(5).
+We note that the fraction depends not only on $f_{pbh}$ and the mass function, but also on the cosmic time (or redshift); and the fraction will increase as cosmic time increases.
 
-    \item We corrected the grammatical errors as pointed out by the referee.
+Secondly, compared to GWTC-1, GWTC-3 has greatly enlarged the number of BBH events.
+Most importantly, GWTC-3 contains much more heavy black holes and shifts the mass distribution of black holes to a larger value.
+This motivates us to investigate whether these heavy black holes are (partly) formed from second-generation mergers or not, since the second-merger process will shift the mass distribution to a larger value.
+Although we agree that the merger rate from second-merger process cannot make significant contribution even from a crude estimation, an accurate estimation of the impact of the second-merger process on the mass distribution should come from careful data analyses as done in this work.
+In fact, as can be seen Fig.~(8), the second-merger process can significantly shift the mass distribution to heavy mass as $\cR_2/\cR_1$ can be $\geq 50\%$.
+
+In summary, we believe our work has considerable signiﬁcance and novelty. Moreover, in the revised version of the manuscript, we have added some sentences to explain our novelty in the Introduction.
+
+\item \red{\it My second question concerns the fact that this manuscript didn't consider the PBH cluster at the late time of the universe, rather it still reckons the second-generation merger from spatially uniformly distributed PBHs.
+At late times the dark matter forms halo structures, thus causing the PBH to cluster, and thus maybe boosting the merger rate.
+This was considered e.g.
+by 2012.02786 (see their $S_2$ term).
+Can this effect be safely ignored by the current work?}
+
+We would like to thank the referee for pointing out this effect as well as the reference 2012.02786.
+Yes, this effect can be safely ignored.
+According to Ref.~\cite{Hutsi:2020sol}, the suppression factor $S_2(z,f_{\mathrm{pbh}})$ can be approximated as
+\begin{equation}
+    S_2(z,f_{\mathrm{pbh}}) \approx \mathrm{min}[1,\Tilde{S_2}(z,f_{\mathrm{pbh}})], 
+\end{equation}
+where 
+\begin{equation}
+\Tilde{S_2}(z,f_{\mathrm{pbh}})=9.6 \times 10^{-3} {\left(\left(t[z]/t_0\right)^{0.44}f_{\mathrm{pbh}}\right)}^{-0.65} e^{0.03 \ln ^2 \left(\left(t[z]/t_0\right)^{0.44}f_{\mathrm{pbh}}\right)},
+\end{equation}
+which decrease as $f_{\mathrm{pbh}}$ increase and increase as $z$ increase.
+For all of the four PBH mass functions, we always have $f_{\mathrm{pbh}} \lesssim 3\times10^{-3}$.
+Therefore, we always have $\Tilde{S_2}(z,f_{\mathrm{pbh}})\geq \Tilde{S_2}(0,3\times 10^{-3}) \approx 1.15$ and $S_2(z,f_{\mathrm{pbh}})\approx 1$.
+As a result, this effect can be safely ignored.
+In the revised version, we have cited this reference and added the following discussion in the Conclusion section:
+
+\textit{``PBHs cluster at the late time of the Universe may play an important role in the merger rate.
+For all of the four PBH mass functions, we always have $f_{\mathrm{pbh}} \lesssim 3\times10^{-3}$.
+Therefore, according to Ref.~\cite{Hutsi:2020sol}, this effect can be safely ignored."}
+
+%Yes, this effect can be safely ignored.
+For all of the four PBH mass functions, we always have $f_{\mathrm{pbh}} \in [10^{-3},3\times10^{-3}]$, and therefore $S_2[z]\approx 1$ as shown in the following figure.
+I would like to thank the referee for pointing out this effect as well as the reference 2012.02786.
+In the revised version, we have cited this reference and added the following discussion in the Conclusion section:
+
+\item \red{\it The title remains ``Constrain ..." in the manuscript, but in the PRD submission system it has been changed to ``Constraining ...". Keep the latter.}
+
+We thank the referee for pointing out this inconsistency. We have changed the title to ``Constraining ..." in the revised version.
+
+\item \red{\it Section 1: The first paragraph, the second last sentence ``even accounting for the uncertainties in modelling...", I think the authors meant ``statistical uncertainties" (i.e., the uncertainty of parameter estimation).
+Other models exist for GW190521, such as eccentric orbits, hyperbolic encounters models, or even proca star head-on collisions.
+In those models, especially the proca star, the mass in the gap may not be the case.}
+
+Yes, we meant ``statistical uncertainties", and we have rephrased the sentence as ``even accounting for the statistical uncertainties, it ...".
+
+\item \red{\it Section 1: paragraph 3, in the middle, ``we use GWTC-3, which expands GWTC-1 with almost six times", add that the GWTC-3 is purified by using a subset.
+I was confused at the first pass why it was not nine times more.}
+
+We have rephrased it as ``we use a purified subset of GWTC-3, which expands GWTC-1 with almost six times".
+
+\item \red{\it Although the authors recommended the readers to ref 21 for details, this manuscript should add more descriptions to at least explain all terms.
+For example, I couldn't find the meaning of $m_i$, $m_j$ and $m_l$, $m_e$, etc.}
+
+In the revised version, we have added more descriptions to explain all terms, including $m_i$, $m_j$, $m_l$, and $m_e$, etc., as suggested by the referee.
+
+\item \red{\it Under equation 4, ``the PBHs are randomly distributed", add ``following a spatial Poisson distribution" otherwise it's not clear what is the random distribution.
+Also, ``These two PBH would ...
+and form a PBH binary", add the condition to form a binary, i.e., decouple from the cosmic expansion.}
+
+As suggested by the referee, we have rephrased these two sentences as 1) ``the PBHs are randomly distributed following a spatial Poisson distribution ..."; 2) ``These two PBH would ...
+and form a PBH binary after decoupling from the cosmic expansion".
+
+\item \red{\it Under equation 8 the authors only considered the merger history up to the second, is it because the authors have estimated the third merger and know it can be safely neglected?
+To echo my first question, can the authors also estimate the contribution from the second merger along the same line?}
+
+Yes, we have estimated the effect of the third-merger process.
+Based on best-fit parameter values inferred from both the first- and second-merger, we found the contribution from the third merger can be negligible as can be seen from the following figure.
+In fact, we have $\cR_3/\cR_2 \leq 0.005$ for the critical collapse mass function.
+
+\begin{figure}[hp!]
+	\centering
+	\includegraphics[width=0.6\textwidth]{ratio-CC-32.pdf}
+	\caption{\label{ratio-power}The ratio of merger rate density from the third merger to that from the second merger, $\cR_3(t_0, m_1, m_2)/\cR_2(t_0, m_1, m_2)$, as a function of component masses for the critical collapse mass function.
+We have fixed the hyper-parameters $\{\Mf, \al, \fpbh\}$ to their best-fit values.}
+\end{figure}
+
+However, the second-merger process can significantly shift the mass distribution to heavy mass as $\cR_2/\cR_1$ can be $\geq 50\%$ for the critical collapse mass function as can be seen from Fig.~(8) in the manuscript.
+
+\item \red{\it Conclusion: The second paragraph said ``Therefore the merger history of PBH binaries has a sub-dominant effect...", I suggest making it clear that by ``merger history" the authors really meant the higher-order hierarchical merger after the first one.
+My reasoning is that the term "merger history" may be confused by the PBH merger rate as a function of different cosmic time.}
+
+As suggested by the referee, we have rephrased the sentence as ``Therefore the higher-order hierarchical merger after the first one has a sub-dominant effect...".
 
@@
 
-Please reconsider our paper for publication in PRD. \\
+We have highlighted the changes in the bold font in the manuscript. We hope these changes will address the referee's concerns. Please reconsider our paper for publication in PRD. \\
 
-Best wishes,
+\noindent Sincerely,\\
+Lang~Liu, Zhi-Qiang~You, You~Wu, Zu-Cheng~Chen
 
-You Wu
-
-\newpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %%% references %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliography{ref}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\end{document}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\end{document}
